### 2024-10-21 paper/paper.qmd
Paper writing.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Yongqi Liu
  - Third author
thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-10-21 paper/paper.qmd
Update Pollster Methodology Overview and Evaluation in Appendix

@@
   - First author
-  - Yongqi Liu
-  - Third author
-thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
+  - Another author
+thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
 date: today
@@
 library(tidyverse)
+library(palmerpenguins)
 ```
@@
 
+ggplot(penguins, aes(x = island, fill = species)) +
+  geom_bar(alpha = 0.8) +
+  scale_fill_manual(values = c("darkorange","purple","cyan4"),
+                    guide = "none") +
+  theme_minimal() +
+  facet_wrap(~species, ncol = 1) +
+  coord_flip()
 ```
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
 ```
@@
 
+# Pollster Methodology Overview and Evaluation
+
+## Overview of SurveyUSA\
+SurveyUSA is a privately held opinion research company that operates nationwide, across all 50 U.S.
+states.
+Since its founding, the company has conducted over 40,000 research projects, serving a client base of 400 organizations, including media outlets, corporations, non-profits, government agencies, and academic institutions.
+Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels.
+The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms.
+
+## Population, Frame, and Sample\
+
+* Target Population: U.S. citizens eligible to vote in the 2024 presidential election.\
+* Sample Frame:  U.S. households with either home telephones or access to devices such as phones or tablets. \
+* Sample Size: Sample sizes vary across different polls.
+For the 2024 U.S.
+presidential election cycle, SurveyUSA conducted 49 polls, with sample sizes ranging from 507 to 2,330 for registered voters or likely voters.
+The average sample size for these polls is approximately 1,045 households.\
+
+## Recruitment\
+SurveyUSA employs a mixed-method approach to recruitment, including online panels, telephone calls, and a text-to-web method.
+Some respondents are recruited through Random Digit Dialing (RDD) using telephone samples purchased from Aristotle, while others, who do not use home telephones, are invited to complete the survey on an electronic device such as a phone or tablet.
+Respondents from non-probability online panels are selected randomly by Cint/Lucid Holdings LLC.\
+
+## Sampling approach and Trade-offs\
+SurveyUSA uses a blend of probability and non-probability sampling methods.
+Some respondents are drawn from non-probability online panels, while others are recruited using probability-based telephone sampling.
+Responses are weighted based on the latest U.S.
+Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population.
+Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects.\
+
+* **Advantages:**\
+The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population.
+Furthermore, reweighting the data according to U.S.
+Census demographics strengthens the credibility of the results by ensuring demographic accuracy.
+Additionally, rotating questions and answer choices helps mitigate bias, further improving the reliability of the data.
+Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
+* **Disadvantages:**\
+Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
+Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.\
+
+## Non-response Handling\
+In cases of non-response, SurveyUSA attempts follow-up calls if interviews are interrupted by answering machines or busy signals.
+Weighting is applied to adjust for non-response bias, although this doesn't completely eliminate challenges posed by unreachable or unwilling participants.\
+
+## Questionnaire Evaluation\
+
+* **Positive Aspects:**
+A logical flow between questions facilitates easy navigation for respondents throughout the survey, while simple wording promotes inclusivity by enabling individuals from diverse backgrounds to comprehend the questions.
+Furthermore, all questions are directly relevant to analyzing the 2024 U.S.
+presidential election, and providing predefined response options simplifies the choices for participants.\
+* **Negative Aspects:**
+Static options for party affiliation and ideology may fail to capture the nuances of respondents’ political beliefs. These rigid categories could oversimplify complex political identities.\
+
+## Summary Evaluation\
+SurveyUSA’s methodology reflects a balanced approach, leveraging various sampling approach and method to reach a representative sample.
+While its blend of probability and non-probability methods has strengths, such as cost-effectiveness and broad reach, it faces challenges related to telephone interview logistics, potential interviewer bias, and the limitations of fixed questionnaire options.
+Nevertheless, the inclusion of data weighting and question rotation adds credibility to its results, making SurveyUSA a reliable pollster for localized opinion research.
+
 # Additional data details
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
 ```

### 2024-10-21 scripts/03-clean_data.R
Delete useless code.

@@ -14,21 +14,15 @@ raw_data <- read_csv("data/01-raw_data/US_voting.csv")
 colnames(raw_data)
 
 #### Clean the poll data
-# Filter for likely voters (lv)
-#likely_voters_data <- raw_data %>% filter(population == "lv")
-
 # Now we decide to use pollster with grade >2.5 as 'high quality' pollster
 cleaned_data <- raw_data %>% filter(numeric_grade > 2.5)
 cleaned_data$mdy <- mdy(cleaned_data$end_date)
-cleaned_data <- cleaned_data %>%
-  filter(candidate_name== "Donald Trump")
+cleaned_data <- cleaned_data %>% filter(candidate_name== "Donald Trump")
 
 # Clean raw dataset, remove columns with many missing values and keep the columns we want to make analysis on
 cleaned_data <- cleaned_data %>% dplyr::select(pollster_rating_name, methodology, numeric_grade, start_date,
                                                end_date, sample_size, population, state, 
-                                               candidate_name, pct)
-
-#filter(!is.na(population) & !is.na(state) & !is.na(candidate_name) & !is.na(pct) & !is.na(numeric_grade& )
+                                           candidate_name, pct) 
 
 # Change name for different types of voters in population column
 cleaned_data <- cleaned_data %>%
@@ -45,19 +39,18 @@ cleaned_data <- cleaned_data %>% select(-population)
 cleaned_data <- cleaned_data %>%
   filter(end_date >= start_date)
 
-# convert the format of the start date and end date
+# Convert the format of the start date and end date
 cleaned_data <- cleaned_data %>%
   mutate(
-    start_date = mdy(start_date),  # or dmy(), ymd() depending on the format
-    end_date = mdy(end_date)       # same as above
-  )
+    start_date = mdy(start_date), 
+    end_date = mdy(end_date))
 
 # Revise the state name
 cleaned_data <- cleaned_data %>%
   mutate(state = ifelse(is.na(state), "National",
                         ifelse(state == "Nebraska CD-2", "Nebraska",
                                ifelse(state %in% c("Maine CD-1", "Maine CD-2"), "Maine", state))))
-# revise the name of column 
+# Revise the name of column 
 cleaned_data <- cleaned_data %>%
   rename(percent = pct)
 

### 2024-10-21 paper/paper.qmd

@@
   - First author
-  - Another author
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+  - Yongqi Liu
+  - Third author
+thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
 date: today
@@
 library(tidyverse)
-library(palmerpenguins)
 ```
@@
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
 ```

### 2024-10-22 paper/paper.qmd
Modify Appendix B

@@
   - Yongqi Liu
-  - Third author
+  - Yuxuan Wei
 thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
@@
 
+# Appendix B: Idealized Methodology and Survey
+
+## **Objective and Overview**
+The goal of this survey methodology is to accurately forecast the outcome of the U.S.
+presidential election by collecting high-quality, representative data from a diverse set of respondents across the country.
+With a budget of $100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols.
+The approach is designed to maximize accuracy, reduce bias, and account for various demographic, geographic, and political factors that influence voting behavior.
+
+### **Core Objectives**:
+1. Obtain a representative sample of the U.S. electorate.
+2. Ensure data quality through rigorous validation.
+3. Leverage statistical modeling and poll aggregation for an accurate prediction.
+
+## **1. Sampling Strategy**
+
+The sampling strategy is designed to ensure that the survey reaches a broad, representative section of the voting population.
+To achieve this, we will use **stratified random sampling** combined with **quota sampling** for key demographics.
+This ensures that each important subgroup within the population is adequately represented.
+
+### **Stratification Variables**:
+- **Age Groups**: 18-29, 30-44, 45-64, 65+  
+- **Gender**: Male, Female, Non-binary/Other  
+- **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other  
+- **Education Level**: No high school, High school graduate, College graduate, Post-graduate  
+- **Income Bracket**: <$30,000, $30,000-$60,000, $60,000-$100,000, >$100,000  
+- **Geographic Region**: Northeast, Midwest, South, West
+
+**Sample Size**:  
+A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1% at a 95% confidence level.
+This sample size will allow for detailed subgroup analysis (e.g., by state, demographic group), yielding statistically robust predictions.
+
+**Weighting**:  
+We will apply post-stratification weights to adjust for any oversampling or undersampling of specific demographic groups.
+For example, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.
+
+## **2. Recruitment Strategy**
+
+### **Recruitment Channels**:
+To maximize respondent diversity and ensure accurate sampling, the survey will employ **multi-channel recruitment**:
+
+- **Digital Advertisements**: Targeted ads on platforms like Facebook, Instagram, and Google will be used to recruit respondents based on their demographic profiles (age, gender, location, political interest).
+Custom audience features will be utilized to reach specific demographic and geographic groups.
+- **Email Outreach**: If permissible, we will access voter registration databases and send email invitations to registered voters.
+This will allow us to target specific voter demographics that are harder to reach via digital ads.
+- **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities (e.g., minority voter outreach programs) will further boost respondent diversity.
+- **Incentives**: To increase response rates, each participant will be entered into a lottery with a chance to win a $100 gift card, encouraging broader participation.
+
+## **3. Data Validation and Quality Assurance**
+
+Maintaining data integrity and ensuring high-quality responses are critical to the accuracy of the election forecast.
+Therefore, several measures will be put in place to validate responses and reduce noise in the dataset.
+
+### **Data Validation Protocols**:
+1. **Real-time Captcha Verification**: This will prevent automated bots from submitting responses.
+2. **Email/Phone Verification**: Respondents will verify their email or phone number to ensure authenticity. This ensures that each respondent only participates once.
+3.
+**Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question.
+Responses completed suspiciously quickly (e.g., below 30% of the average completion time) will be flagged for review or exclusion.
+4. **Voter Registration Cross-Check**: If feasible, respondents will be cross-referenced with voter registration records to ensure they are eligible to vote in the upcoming election.
+5. **Response Audits**: Randomly selected respondents will be contacted to verify the accuracy of their responses, ensuring integrity in the dataset.
+
+## **4. Poll Aggregation and Data Analysis**
+
+### **Poll Aggregation**:
+This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen our forecast through a **poll-of-polls** approach.
+
+- **Weighting by Methodology and Recency**: Poll results will be weighted based on the rigor of their methodology (e.g., online vs.
+phone surveys, sample size) and the recency of the poll.
+Recent, methodologically sound polls will receive more weight in the aggregation process.
+- **Handling Bias and Variability**: Aggregated results will adjust for pollster house effects (biases in methodology) and variability between polls, ensuring that no single poll dominates the prediction.
+
+### **Modeling Approach**:
+We will implement **Bayesian hierarchical models** to account for variability across different states, demographics, and regions.
+This will allow us to model the popular vote and potentially translate it into **Electoral College predictions**.
+
+## **5. Budget Allocation**
+
+- **Respondent Recruitment (Targeted ads, outreach)**: $70,000  
+- **Incentives (e.g., lottery prizes)**: $10,000  
+- **Survey Platform (Google Forms, Qualtrics subscription)**: $5,000  
+- **Data Validation Tools**: $5,000  
+- **Poll Aggregation & Analysis Software**: $10,000
+
+---
+
+## **6. Survey Implementation**
+
+The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection.
+The link to the live survey can be found here: [Google Form Survey](https://forms.gle/RC1464SvLvtoAYdv6).
+A copy of the questions is provided below.
+
+### **Survey Structure**:
+
+1. **Introduction**:
+Thank you for taking part in this survey aimed at predicting the outcome of the 2024 US Presidential election. Your insights are valuable to our research.
+
+Please note:
+- **All responses will be kept strictly confidential.**
+- **Your participation is entirely voluntary.**
+- **We kindly request that you answer all questions honestly and to the best of your knowledge.**
+- **The survey is estimated to take approximately 10 minutes to complete.**
+If you have any inquiries or concerns regarding this survey, please don't hesitate to contact the research team at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca).
+
+Your contribution to this study is greatly appreciated! Each participant will be entered into a lottery with a chance to win a $100 gift card!
+
+2. **Section 1: Eligibility Screening**:
+Are you a U.S. citizen?
+- Yes
+- No [If No, end survey]
+
+Will you be 18 or older by Election Day (November 5, 2024)?
+- Yes
+- No [If No, end survey]
+
+Are you registered to vote in the United States?
+- Yes
+- No
+- Not sure
+- Plan to register before the election
+
+3. **Section 2: Demographic Information**:
+What is your age group?
+- 18-29
+- 30-44
+- 45-64
+- 65 or older
+- Prefer not to say
+
+What is your gender?
+- Male
+- Female
+- Non-binary/Other
+- Prefer not to say
+
+What is your race/ethnicity? (Select all that apply)
+- White
+- Black or African American
+- Hispanic or Latino
+- Asian
+- American Indian or Alaska Native
+- Native Hawaiian or Pacific Islander
+- Prefer not to say
+- Other: [Short text answer]
+
+What is your highest level of education completed?
+- No high school
+- High school graduate or equivalent
+- Some college, no degree
+- Bachelor's degree
+- Graduate or professional degree
+- Prefer not to say
+
+What was your total household income in 2023?
+- Less than $30,000
+- $30,000 - $59,999
+- $60,000 - $99,999
+- $100,000 - $149,999
+- $150,000 or more
+- Prefer not to say
+
+In which region of the United States do you currently reside?
+- Northeast (ME, NH, VT, MA, RI, CT, NY, NJ, PA)
+- Midwest (OH, IN, IL, MI, WI, MN, IA, MO, ND, SD, NE, KS)
+- South (DE, MD, DC, VA, WV, NC, SC, GA, FL, KY, TN, AL, MS, AR, LA, OK, TX)
+- West (MT, ID, WY, CO, NM, AZ, UT, NV, WA, OR, CA, AK, HI)
+
+4. **Section 3: Political Views and Voting Intentions**:
+How likely are you to vote in the 2024 Presidential election?
+- Definitely will vote
+- Probably will vote
+- Might or might not vote
+- Probably will not vote
+- Definitely will not vote
+
+Generally speaking, do you usually think of yourself as a:
+- Democrat
+- Republican
+- Independent
+- Prefer not to say
+- Other: [Short text answer]
+
+If the 2024 Presidential election were held today, who would you vote for?
+- Kamala Harris (Democrat)
+- Donald Trump (Republican)
+- Undecided
+- Prefer not to say
+- Other: [Short text answer]
+
+How certain are you about your choice?
+- Very certain
+- Somewhat certain
+- Not very certain
+- Not at all certain
+- Prefer not to say
+
+Which THREE issues are most important to you in deciding your vote? (Select exactly three)
+- Economy and jobs
+- Healthcare
+- Immigration
+- Climate change
+- National security
+- Education
+- Gun policy
+- Social justice/racial equality
+- Taxes
+- Crime and public safety
+- Foreign policy
+- Other: [Short text answer]
+
+5. **Section 4: Information Sources and Engagement**:
+
+What is your primary source of political news? (Select all that apply)
+- Network TV news (ABC, CBS, NBC)
+- Cable TV news (CNN, Fox News, MSNBC)
+- News websites
+- Social media
+- Radio
+- Print newspapers
+- Friends and family
+- Other: [Short text answer]
+
+How closely have you been following news about the 2024 Presidential election?
+- Very closely
+- Somewhat closely
+- Not too closely
+- Not at all
+- Not sure
+
+6. **Section 5: Validation and Consent**:
+Please verify that you are a human by selecting "Blue" from the following options:
+- Red
+- Green
+- Blue
+- Yellow
+
+Consent Statement:
+"I understand that my participation in this survey is voluntary and that my responses will be kept confidential. I agree that my responses may be used for research purposes."
+- Yes, I agree
+- No, I do not agree
+
+Email Address: [Email field]
+
+7. **End Message**:
+"Thank you for completing this survey. Your response has been recorded.
+If you have any questions about this survey or would like to be informed about the results, please contact [Your Contact Information]."
+
+---
+
+### **7. Survey Design Considerations**
+
+- **Question Wording**: All questions are carefully designed to avoid bias or leading responses.
+- **Neutrality**: Political questions are framed neutrally to avoid pushing respondents toward specific answers.
+- **Pilot Testing**: Before full deployment, the survey will undergo a pilot test to identify and resolve any issues.
+
+---
+
+This methodology, combining rigorous sampling, data validation, and aggregation, ensures that the election forecast is as accurate and representative as possible.
+
 # Additional data details

### 2024-10-22 scripts/05-exploratory_data_analysis.R
Update the EDA about starter model part.

@@ -12,107 +12,99 @@ library(tidyverse)
 #install.packages("rstanarm")
 library(rstanarm)
 library(dplyr)
+library(ggplot2)
+library(modelsummary)
 
 #### Read data ####
 analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
 colnames(analysis_data)
 
 #### Summary the numeric variables ####
-summary(cleaned_data)
+summary(analysis_data)
 summary(analysis_data$sample_size)
-summary(analysis_data$pct)
+summary(analysis_data$percent)
 summary(analysis_data$numeric_grade)
 
-# Histogram of support percentages (pct) for Trump
-ggplot(cleaned_data, aes(x = percent)) +
+### See the distribution for some useful variables ###
+# Histogram of support percentages for Trump
+ggplot(analysis_data, aes(x = percent)) +
   geom_histogram(binwidth = 2, fill = "blue", color = "black", alpha = 0.7) +
-  labs(title = "Distribution of Support (pct) for Donald Trump", x = "Support Percentage (pct)", y = "Count") +
+  labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
   theme_minimal()
 
 # Histogram of sample size to see its distribution
-ggplot(cleaned_data, aes(x = sample_size)) +
+ggplot(analysis_data, aes(x = sample_size)) +
   geom_histogram(binwidth = 100, fill = "green", color = "black", alpha = 0.7) +
   labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
   theme_minimal()
 
-# Line plot of candidate support over time
-ggplot(candidates, aes(x = as.Date(start_date, format = "%m/%d/%y"), y = pct, color = candidate_name)) +
+# Line plot of Trump's support over time by end data
+ggplot(analysis_data, aes(x = as.Date(end_date, format = "%y/%m/%d"), y = percent, color = candidate_name)) +
   geom_line() +
-  labs(title = "Candidate Support Over Time", x = "Date", y = "Support Percentage (pct)") +
+  labs(title = "Candidate Support Over Time", x = "Date", y = "Support Percentage (percent)") +
   theme_minimal()
 
-# Boxplot to compare support percentages across candidates
-ggplot(candidates, aes(x = candidate_name, y = pct, fill = candidate_name)) +
[…]

### 2024-10-22 paper/paper.qmd
Update the paper.

--- 2024-10-21 paper/paper.qmd
@@
 library(tidyverse)
+analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
 ```
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
+analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
 
+analysis_data |> 
+  ggplot(aes(x = width, y = length)) +
+  geom_point(alpha = 0.8) +
+  theme_minimal() +
+  labs(x = "Wing width (mm)",
+       y = "Wing length (mm)")
 ```
@@
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+```{r}
+trump_model <- readRDS(here::here(("models/trump_model.rds")))
+```
+
+# Diagnostic plots for the MLR model
+par(mfrow = c(2, 2))
+plot(mlr_harris_model)
+par(mfrow = c(1, 1))  # Reset plot layout
 
@@
 
-# Pollster Methodology Overview and Evaluation
-
-## Overview of SurveyUSA\
-SurveyUSA is a privately held opinion research company that operates nationwide, across all 50 U.S.
-states.
-Since its founding, the company has conducted over 40,000 research projects, serving a client base of 400 organizations, including media outlets, corporations, non-profits, government agencies, and academic institutions.
-Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels.
-The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms.
-
-## Population, Frame, and Sample\
-
-* Target Population: U.S. citizens eligible to vote in the 2024 presidential election.\
-* Sample Frame:  U.S. households with either home telephones or access to devices such as phones or tablets. \
-* Sample Size: Sample sizes vary across different polls.
-For the 2024 U.S.
-presidential election cycle, SurveyUSA conducted 49 polls, with sample sizes ranging from 507 to 2,330 for registered voters or likely voters.
-The average sample size for these polls is approximately 1,045 households.\
-
-## Recruitment\
-SurveyUSA employs a mixed-method approach to recruitment, including online panels, telephone calls, and a text-to-web method.
-Some respondents are recruited through Random Digit Dialing (RDD) using telephone samples purchased from Aristotle, while others, who do not use home telephones, are invited to complete the survey on an electronic device such as a phone or tablet.
-Respondents from non-probability online panels are selected randomly by Cint/Lucid Holdings LLC.\
-
-## Sampling approach and Trade-offs\
-SurveyUSA uses a blend of probability and non-probability sampling methods.
-Some respondents are drawn from non-probability online panels, while others are recruited using probability-based telephone sampling.
-Responses are weighted based on the latest U.S.
-Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population.
-Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects.\
-
-* **Advantages:**\
-The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population.
-Furthermore, reweighting the data according to U.S.
-Census demographics strengthens the credibility of the results by ensuring demographic accuracy.
-Additionally, rotating questions and answer choices helps mitigate bias, further improving the reliability of the data.
-Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
-* **Disadvantages:**\
-Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
-Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.\
-
-## Non-response Handling\
-In cases of non-response, SurveyUSA attempts follow-up calls if interviews are interrupted by answering machines or busy signals.
-Weighting is applied to adjust for non-response bias, although this doesn't completely eliminate challenges posed by unreachable or unwilling participants.\
-
-## Questionnaire Evaluation\
-
-* **Positive Aspects:**
-A logical flow between questions facilitates easy navigation for respondents throughout the survey, while simple wording promotes inclusivity by enabling individuals from diverse backgrounds to comprehend the questions.
-Furthermore, all questions are directly relevant to analyzing the 2024 U.S.
-presidential election, and providing predefined response options simplifies the choices for participants.\
-* **Negative Aspects:**
-Static options for party affiliation and ideology may fail to capture the nuances of respondents’ political beliefs. These rigid categories could oversimplify complex political identities.\
-
-## Summary Evaluation\
-SurveyUSA’s methodology reflects a balanced approach, leveraging various sampling approach and method to reach a representative sample.
-While its blend of probability and non-probability methods has strengths, such as cost-effectiveness and broad reach, it faces challenges related to telephone interview logistics, potential interviewer bias, and the limitations of fixed questionnaire options.
-Nevertheless, the inclusion of data weighting and question rotation adds credibility to its results, making SurveyUSA a reliable pollster for localized opinion research.
-
 # Additional data details
@@
 
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+
+posterior_vs_prior(first_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
+plot(trump_model, "trace")
 
 plot(first_model, "rhat")
+
 ```
@@
 
+# Acknowledgements
+@citeR
+
 # References

### 2024-10-22 scripts/06-model_data.R
Model build up used for paper writing.

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Model for the Trump's election
 # Author: Xuanle Zhou, Yongqi Liu, Yuxuan Wei
-# Date: October 19 2024
+# Date: October 22, 2024
 # Contact: cassieliu.liu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Need the US election poll data
@@ -14,13 +14,18 @@ library(tidyverse)
 library(dplyr)
 library(splines)
 library(rstanarm)
+library(bayesplot)
+library(rstanarm)
+library(ggplot2)
+
 
 #### Read data ####
 analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
 
 ### Model data ####
+# 1. Bayesian Model
 # Convert end_date to a numeric
-analysis_data <- analysis_data %>%
+analysis_data %>%
   mutate(end_date_num = as.numeric(end_date - min(end_date)))
 
 # Fit Bayesian model with spline and pollster as fixed effect
@@ -90,36 +95,43 @@ ggplot(analysis_data, aes(x = end_date_num, y = percent, color = pollster_rating
   labs(x = "Days since earliest poll", y = "Trump Percentage", title = "Trump Polling Percentage over Time with Spline Fit") +
   theme_minimal()
 
-#---------------------------------------logistic regression----------------
-# Convert end_date to a numeric counter and create a binary outcome for winning
+#2. Logistic Regression Model
+analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
+# Create a binary outcome variable for Trump's win (1 if percent > 50%, 0 otherwise)
 analysis_data <- analysis_data %>%
   mutate(
-    end_date_num = as.numeric(end_date - min(end_date, na.rm = TRUE)),  # Convert end_date to a numeric counter
-    win_prob = ifelse(percent > 50, 1, 0)  # Create a binary outcome for winning
-  )
+    win_trump = ifelse(percent > 50, 1, 0))
 
-# Make pollster_rating_name a factor
-analysis_data$pollster_rating_name <- factor(analysis_data$pollster_rating_name)
+# Convert necessary variables to factors
+analysis_data %>%
+  mutate(
+    state = factor(state), 
+    pollster_rating_name = factor(pollster_rating_name), 
+    methodology = factor(methodology))
 
-# Check the structure to confirm
+
[…]

### 2024-10-23 scripts/06-model_data.R
Logistic model build up.

@@ -17,6 +17,9 @@ library(rstanarm)
 library(bayesplot)
 library(rstanarm)
 library(ggplot2)
+#install.packages("caret")
+library(caret)
+library(modelsummary)
 
 
 #### Read data ####
@@ -24,41 +27,59 @@ analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
 
 ### Model data ####
 # 1. Bayesian Model
-# Convert end_date to a numeric
-analysis_data %>%
-  mutate(end_date_num = as.numeric(end_date - min(end_date)))
+# Change 'end_date' and 'state' to factor variables
+analysis_data <- analysis_data |>
+  mutate( end_date = as.numeric(end_date), state = factor(state))
 
-# Fit Bayesian model with spline and pollster as fixed effect
-spline_model <- stan_glm(
-  percent ~ ns(end_date_num, df = 9) + pollster_rating_name, 
+# Bayesian Regression Model (Without State Effect):
+bayesian_model <- stan_glm(
+  percent ~ ns(end_date, df = 9) + pollster_rating_name, 
   data = analysis_data,
   family = gaussian(),
-  prior = normal(0, 5),
-  prior_intercept = normal(50, 10),
+  prior = normal(0, 2.5),  # Weakened prior to allow more spread
+  prior_intercept = normal(50, 20),  # Slightly wider prior for intercept
   seed = 1234,
-  iter = 2000,
+  iter = 3000,  # Increase iterations for better convergence
   chains = 4,
   refresh = 0)
 
-# Adding random effects for pollster
-spline_model_random <- stan_glmer(
-  percent ~ ns(end_date_num, df = 9) + (1 | pollster_rating_name)+ (1 | state),
+# Bayesian Mixed-Effects Model (With Random Effects for State and Pollster):
+bayesian_model_state <- stan_glmer(
+  percent ~ ns(end_date, df = 9) + (1 | pollster_rating_name) + (1 | state),
   data = analysis_data,
   family = gaussian(),
-  prior = normal(0, 5),
-  prior_intercept = normal(50, 10),
+  prior = normal(0, 5),  # Moderate prior for the coefficients
+  prior_intercept = normal(50, 20),  # Adjusted prior intercept
   seed = 1234,
-  iter = 2000,
+  adapt_delta = 0.99,  # Increased adapt_delta to improve convergence
+  iter = 3000,  # Increased iterations for better convergence
   chains = 4,
[…]

### 2024-10-23 scripts/03-clean_data.R
Update cleaned data set and EDA to include 2 candidates.

@@ -17,7 +17,14 @@ colnames(raw_data)
 # Now we decide to use pollster with grade >2.5 as 'high quality' pollster
 cleaned_data <- raw_data %>% filter(numeric_grade > 2.5)
 cleaned_data$mdy <- mdy(cleaned_data$end_date)
-cleaned_data <- cleaned_data %>% filter(candidate_name== "Donald Trump")
+
+# Define the cutoff date (July 21, 2024)
+cutoff_date <- as.Date("2024-07-21")
+
+# Fitler trump and Harris
+cleaned_data <- cleaned_data %>%
+  filter((candidate_name == "Donald Trump") | 
+           (candidate_name == "Kamala Harris" & mdy > cutoff_date))
 
 # Clean raw dataset, remove columns with many missing values and keep the columns we want to make analysis on
 cleaned_data <- cleaned_data %>% dplyr::select(pollster_rating_name, methodology, numeric_grade, start_date,

### 2024-10-23 scripts/05-exploratory_data_analysis.R

@@ -38,7 +38,7 @@ ggplot(analysis_data, aes(x = sample_size)) +
   labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
   theme_minimal()
 
-# Line plot of Trump's support over time by end data
+# Line plot of Trump and Harris's support over time by end data
 ggplot(analysis_data, aes(x = as.Date(end_date, format = "%y/%m/%d"), y = percent, color = candidate_name)) +
   geom_line() +
   labs(title = "Candidate Support Over Time", x = "Date", y = "Support Percentage (percent)") +

### 2024-10-23 paper/paper.qmd
Paper writing.

--- 2024-10-22 paper/paper.qmd
@@
 ```{r}
-#| include: false
-#| warning: false
-#| message: false
-
 library(tidyverse)
+library(ggplot2)
+analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
 ```
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
-
 ```
@@
 
-## Model set-up
+## Logistic Regression Model Build up
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+To predict whether Donald Trump would win over Kamala Harris based on polling data, we constructed a logistic regression model using a subset of 1,000 randomly sampled observations from our cleaned dataset.
+The dependent variable, trump_win, is a binary outcome representing whether Trump was predicted to win in a given state (1 for Trump win, 0 for Harris win).
+The independent variables included in the model are pollster_rating_name, state, population_group, numeric_grade, sample_size, and methodology.
+
+We used the logit link function given that our outcome variable is binary.
+The logistic regression model estimates the log odds of Trump winning as a linear function of these predictors.
+Each predictor variable was selected based on its relevance to polling outcomes:
+
+	•	pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
+	•	state accounts for geographic variations in voter preferences.
+	•	population_group represents different demographic categories.
+	•	numeric_grade reflects the poll’s quality rating.
+	•	sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
+	•	methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
+
+We applied a Bayesian approach to estimate the logistic regression model using Stan, with weakly informative priors (Normal distribution with mean 0 and standard deviation 2.5) for both the coefficients and the intercept.
+These priors reflect our assumption that the effect of each predictor is centered around 0, with a moderate level of uncertainty.
+By incorporating state and demographic information along with pollster quality and methodology, we aim to capture the variability in polling predictions across different regions and polling practices.
+The use of Bayesian inference allows us to quantify uncertainty in our predictions more effectively.
+
+We use weakly informative Normal priors for the intercept ( \alpha ) and coefficients ( \beta_i ), centered around zero with a standard deviation of 2.5.
+These priors were chosen to allow the data to influence the predictions while still reflecting reasonable uncertainty.
+Specifically:
 
@@
 \alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
 \end{align}
@@
 We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+
+```{r}
+logistic_model <- readRDS(here::here(("models/logistic_model.rds")))
+```
+
+# Diagnostic plots for the MLR model
+par(mfrow = c(2, 2))
+plot(mlr_harris_model)
+par(mfrow = c(1, 1))  # Reset plot layout
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our results are summarized in ...
 
 ```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
 
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
+  readRDS(file = (here::here("models/logistic_model.rds")))
 ```
@@
 # Appendix {-}
-
+=======
 # Pollster Methodology Overview and Evaluation
@@
 
+>>>>>>> 7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4
+
 # Additional data details
@@
 
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
 ```

### 2024-10-23 paper/paper.tex
Paper writing.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={First author; Yongqi Liu; Yuxuan Wei},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
{[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Yongqi Liu \and Yuxuan Wei}
\date{October 22, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
-- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
v dplyr     1.1.4     v readr     2.1.5
v forcats   1.0.0     v stringr   1.5.1
v ggplot2   3.5.1     v tibble    3.2.1
v lubridate 1.9.3     v tidyr     1.3.1
v purrr     1.0.2     
-- Conflicts ------------------------------------------ tidyverse_conflicts() --
x dplyr::filter() masks stats::filter()
x dplyr::lag()    masks stats::lag()
i Use the conflicted package (<http://conflicted.r-lib.org/>) to force all conflicts to become errors
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(ggplot2)}
\NormalTok{analysis\_data }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data/02{-}analysis\_data/cleaned\_US\_voting.csv"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Rows: 1951 Columns: 10
-- Column specification --------------------------------------------------------
Delimiter: ","
chr  (5): pollster_rating_name, methodology, state, candidate_name, populati...
dbl  (3): numeric_grade, sample_size, percent
date (2): start_date, end_date

i Use `spec()` to retrieve the full column specification for this data.
i Specify the column types or set `show_col_types = FALSE` to quiet this message.
\end{verbatim}

\section{Introduction}\label{introduction}

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as
follows. Section~\ref{sec-data}\ldots.

\section{Data}\label{sec-data}

\subsection{Overview}\label{overview}

We use the statistical programming language R (R Core Team 2023)\ldots.
Our data (Toronto Shelter \& Support Services 2024)\ldots. Following
Alexander (2023), we consider\ldots{}

Overview text

\subsection{Measurement}\label{measurement}

Some paragraphs about how we go from a phenomena in the world to an
entry in the dataset.

\subsection{Outcome variables}\label{outcome-variables}

Add graphs, tables and text. Use sub-sub-headings for each outcome
variable or update the subheading to be singular.

Some of our data is of penguins (\textbf{?@fig-bills}), from Horst,
Hill, and Gorman (2020).

Talk more about it.

And also planes (\textbf{?@fig-planes}). (You can change the height and
width, but don't worry about doing that until you have finished every
other aspect of the paper - Quarto will try to make it look nice and the
defaults usually work well once you have enough text.)

Talk way more about it.

\subsection{Predictor variables}\label{predictor-variables}

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine
a few into one if they go together naturally.

\section{Model}\label{model}

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\subsection{Logistic Regression Model Build
up}\label{logistic-regression-model-build-up}

To predict whether Donald Trump would win over Kamala Harris based on
polling data, we constructed a logistic regression model using a subset
of 1,000 randomly sampled observations from our cleaned dataset. The
dependent variable, trump\_win, is a binary outcome representing whether
Trump was predicted to win in a given state (1 for Trump win, 0 for
Harris win). The independent variables included in the model are
pollster\_rating\_name, state, population\_group, numeric\_grade,
sample\_size, and methodology.

We used the logit link function given that our outcome variable is
binary. The logistic regression model estimates the log odds of Trump
winning as a linear function of these predictors. Each predictor
variable was selected based on its relevance to polling outcomes:

\begin{verbatim}
•   pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
•   state accounts for geographic variations in voter preferences.
•   population_group represents different demographic categories.
•   numeric_grade reflects the poll’s quality rating.
•   sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
•   methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
\end{verbatim}

We applied a Bayesian approach to estimate the logistic regression model
using Stan, with weakly informative priors (Normal distribution with
mean 0 and standard deviation 2.5) for both the coefficients and the
intercept. These priors reflect our assumption that the effect of each
predictor is centered around 0, with a moderate level of uncertainty. By
incorporating state and demographic information along with pollster
quality and methodology, we aim to capture the variability in polling
predictions across different regions and polling practices. The use of
Bayesian inference allows us to quantify uncertainty in our predictions
more effectively.

We use weakly informative Normal priors for the intercept ( \alpha ) and
coefficients ( \beta\_i ), centered around zero with a standard
deviation of 2.5. These priors were chosen to allow the data to
influence the predictions while still reflecting reasonable uncertainty.
Specifically:

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{logistic\_model }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{((}\StringTok{"models/logistic\_model.rds"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\section{Diagnostic plots for the MLR
model}\label{diagnostic-plots-for-the-mlr-model}

par(mfrow = c(2, 2)) plot(mlr\_harris\_model) par(mfrow = c(1, 1)) \#
Reset plot layout

\subsubsection{Model justification}\label{model-justification}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\section{Results}\label{results}

Our results are summarized in \ldots{}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(rstanarm)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Loading required package: Rcpp
\end{verbatim}

\begin{verbatim}
This is rstanarm version 2.32.1
\end{verbatim}

\begin{verbatim}
- See https://mc-stan.org/rstanarm/articles/priors for changes to default priors!
\end{verbatim}

\begin{verbatim}
- Default priors may change, so it's safest to specify priors, even if equivalent to the defaults.
\end{verbatim}

\begin{verbatim}
- For execution on a local, multicore CPU with excess RAM we recommend calling
\end{verbatim}

\begin{verbatim}
  options(mc.cores = parallel::detectCores())
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{first\_model }\OtherTok{\textless{}{-}}
  \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =}\NormalTok{ (here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"models/logistic\_model.rds"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

Please don't use these as sub-heading labels - change them to be what
your point actually is.

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{\# Appendix}\label{appendix}
\addcontentsline{toc}{section}{\# Appendix}

\section{Pollster Methodology Overview and
Evaluation}\label{pollster-methodology-overview-and-evaluation}

\subsection{\texorpdfstring{Overview of SurveyUSA\\
}{Overview of SurveyUSA }}\label{overview-of-surveyusa}

SurveyUSA is a privately held opinion research company that operates
nationwide, across all 50 U.S. states. Since its founding, the company
has conducted over 40,000 research projects, serving a client base of
400 organizations, including media outlets, corporations, non-profits,
government agencies, and academic institutions. Known for its expertise
in localized opinion research, SurveyUSA focuses on gathering data at
the city, county, and regional levels. The company offers timely,
cost-effective surveys tailored to meet specific client needs,
distinguishing itself from larger global firms.

\subsection{\texorpdfstring{Population, Frame, and Sample\\
}{Population, Frame, and Sample }}\label{population-frame-and-sample}

\begin{itemize}
\tightlist
\item
  Target Population: U.S. citizens eligible to vote in the 2024
  presidential election.\\
\item
  Sample Frame: U.S. households with either home telephones or access to
  devices such as phones or tablets.\\
\item
  Sample Size: Sample sizes vary across different polls. For the 2024
  U.S. presidential election cycle, SurveyUSA conducted 49 polls, with
  sample sizes ranging from 507 to 2,330 for registered voters or likely
  voters. The average sample size for these polls is approximately 1,045
  households.\\
\end{itemize}

\subsection{\texorpdfstring{Recruitment\\
}{Recruitment }}\label{recruitment}

SurveyUSA employs a mixed-method approach to recruitment, including
online panels, telephone calls, and a text-to-web method. Some
respondents are recruited through Random Digit Dialing (RDD) using
telephone samples purchased from Aristotle, while others, who do not use
home telephones, are invited to complete the survey on an electronic
device such as a phone or tablet. Respondents from non-probability
online panels are selected randomly by Cint/Lucid Holdings LLC.\\

\subsection{\texorpdfstring{Sampling approach and Trade-offs\\
}{Sampling approach and Trade-offs }}\label{sampling-approach-and-trade-offs}

SurveyUSA uses a blend of probability and non-probability sampling
methods. Some respondents are drawn from non-probability online panels,
while others are recruited using probability-based telephone sampling.
Responses are weighted based on the latest U.S. Census estimates for
age, gender, ethnicity, and region, ensuring alignment with the target
population. Questions and answer choices are rotated to reduce order
bias, recency effects, and latency effects.\\

\begin{itemize}
\tightlist
\item
  \textbf{Advantages:}\\
  The diverse sampling approach not only ensures a broad range of
  opinions is captured but also complements probability-based sampling,
  which accurately reflects the overall population. Furthermore,
  reweighting the data according to U.S. Census demographics strengthens
  the credibility of the results by ensuring demographic accuracy.
  Additionally, rotating questions and answer choices helps mitigate
  bias, further improving the reliability of the data. Finally, the use
  of online surveys offers a cost-effective solution for efficient data
  collection.\\
\item
  \textbf{Disadvantages:}\\
  Phone-based data collection tends to be time-consuming and can be
  affected by interviewer effects during telephone interviews.
  Additionally, challenges like non-response issues, such as busy
  signals or refusals to participate, can hinder the effectiveness of
  the data collection process.\\
\end{itemize}

\subsection{\texorpdfstring{Non-response Handling\\
}{Non-response Handling }}\label{non-response-handling}

In cases of non-response, SurveyUSA attempts follow-up calls if
interviews are interrupted by answering machines or busy signals.
Weighting is applied to adjust for non-response bias, although this
doesn't completely eliminate challenges posed by unreachable or
unwilling participants.\\

\subsection{\texorpdfstring{Questionnaire Evaluation\\
}{Questionnaire Evaluation }}\label{questionnaire-evaluation}

\begin{itemize}
\tightlist
\item
  \textbf{Positive Aspects:} A logical flow between questions
  facilitates easy navigation for respondents throughout the survey,
  while simple wording promotes inclusivity by enabling individuals from
  diverse backgrounds to comprehend the questions. Furthermore, all
  questions are directly relevant to analyzing the 2024 U.S.
  presidential election, and providing predefined response options
  simplifies the choices for participants.\\
\item
  \textbf{Negative Aspects:} Static options for party affiliation and
  ideology may fail to capture the nuances of respondents' political
  beliefs. These rigid categories could oversimplify complex political
  identities.\\
\end{itemize}

\subsection{\texorpdfstring{Summary Evaluation\\
}{Summary Evaluation }}\label{summary-evaluation}

SurveyUSA's methodology reflects a balanced approach, leveraging various
sampling approach and method to reach a representative sample. While its
blend of probability and non-probability methods has strengths, such as
cost-effectiveness and broad reach, it faces challenges related to
telephone interview logistics, potential interviewer bias, and the
limitations of fixed questionnaire options. Nevertheless, the inclusion
of data weighting and question rotation adds credibility to its results,
making SurveyUSA a reliable pollster for localized opinion research.

\section{Appendix B: Idealized Methodology and
Survey}\label{appendix-b-idealized-methodology-and-survey}

\subsection{\texorpdfstring{\textbf{Objective and
Overview}}{Objective and Overview}}\label{objective-and-overview}

The goal of this survey methodology is to accurately forecast the
outcome of the U.S. presidential election by collecting high-quality,
representative data from a diverse set of respondents across the
country. With a budget of \$100,000, this methodology incorporates
sophisticated sampling techniques, robust respondent recruitment
strategies, and rigorous data validation protocols. The approach is
designed to maximize accuracy, reduce bias, and account for various
demographic, geographic, and political factors that influence voting
behavior.

\subsubsection{\texorpdfstring{\textbf{Core
Objectives}:}{Core Objectives:}}\label{core-objectives}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Obtain a representative sample of the U.S. electorate.
\item
  Ensure data quality through rigorous validation.
\item
  Leverage statistical modeling and poll aggregation for an accurate
  prediction.
\end{enumerate}

\subsection{\texorpdfstring{\textbf{1. Sampling
Strategy}}{1. Sampling Strategy}}\label{sampling-strategy}

The sampling strategy is designed to ensure that the survey reaches a
broad, representative section of the voting population. To achieve this,
we will use \textbf{stratified random sampling} combined with
\textbf{quota sampling} for key demographics. This ensures that each
important subgroup within the population is adequately represented.

\subsubsection{\texorpdfstring{\textbf{Stratification
Variables}:}{Stratification Variables:}}\label{stratification-variables}

\begin{itemize}
\tightlist
\item
  \textbf{Age Groups}: 18-29, 30-44, 45-64, 65+\\
\item
  \textbf{Gender}: Male, Female, Non-binary/Other\\
\item
  \textbf{Race/Ethnicity}: White, Black, Hispanic/Latino, Asian,
  Indigenous, Other\\
\item
  \textbf{Education Level}: No high school, High school graduate,
  College graduate, Post-graduate\\
\item
  \textbf{Income Bracket}: \textless\$30,000, \$30,000-\$60,000,
  \$60,000-\$100,000, \textgreater\$100,000\\
\item
  \textbf{Geographic Region}: Northeast, Midwest, South, West
\end{itemize}

\textbf{Sample Size}:\\
A total of \textbf{10,000 respondents} will be surveyed, providing a
margin of error of approximately ±1\% at a 95\% confidence level. This
sample size will allow for detailed subgroup analysis (e.g., by state,
demographic group), yielding statistically robust predictions.

\textbf{Weighting}:\\
We will apply post-stratification weights to adjust for any oversampling
or undersampling of specific demographic groups. For example, younger
voters or underrepresented minorities will be weighted to reflect their
true proportions in the voting population.

\subsection{\texorpdfstring{\textbf{2. Recruitment
Strategy}}{2. Recruitment Strategy}}\label{recruitment-strategy}

\subsubsection{\texorpdfstring{\textbf{Recruitment
Channels}:}{Recruitment Channels:}}\label{recruitment-channels}

To maximize respondent diversity and ensure accurate sampling, the
survey will employ \textbf{multi-channel recruitment}:

\begin{itemize}
\tightlist
\item
  \textbf{Digital Advertisements}: Targeted ads on platforms like
  Facebook, Instagram, and Google will be used to recruit respondents
  based on their demographic profiles (age, gender, location, political
  interest). Custom audience features will be utilized to reach specific
  demographic and geographic groups.
\item
  \textbf{Email Outreach}: If permissible, we will access voter
  registration databases and send email invitations to registered
  voters. This will allow us to target specific voter demographics that
  are harder to reach via digital ads.
\item
  \textbf{Partnerships with Civic Organizations}: Partnering with
  non-profits and civic organizations that engage diverse communities
  (e.g., minority voter outreach programs) will further boost respondent
  diversity.
\item
  \textbf{Incentives}: To increase response rates, each participant will
  be entered into a lottery with a chance to win a \$100 gift card,
  encouraging broader participation.
\end{itemize}

\subsection{\texorpdfstring{\textbf{3. Data Validation and Quality
Assurance}}{3. Data Validation and Quality Assurance}}\label{data-validation-and-quality-assurance}

Maintaining data integrity and ensuring high-quality responses are
critical to the accuracy of the election forecast. Therefore, several
measures will be put in place to validate responses and reduce noise in
the dataset.

\subsubsection{\texorpdfstring{\textbf{Data Validation
Protocols}:}{Data Validation Protocols:}}\label{data-validation-protocols}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Real-time Captcha Verification}: This will prevent automated
  bots from submitting responses.
\item
  \textbf{Email/Phone Verification}: Respondents will verify their email
  or phone number to ensure authenticity. This ensures that each
  respondent only participates once.
\item
  \textbf{Time on Task Monitoring}: The survey platform will monitor the
  time respondents spend on each question. Responses completed
  suspiciously quickly (e.g., below 30\% of the average completion time)
  will be flagged for review or exclusion.
\item
  \textbf{Voter Registration Cross-Check}: If feasible, respondents will
  be cross-referenced with voter registration records to ensure they are
  eligible to vote in the upcoming election.
\item
  \textbf{Response Audits}: Randomly selected respondents will be
  contacted to verify the accuracy of their responses, ensuring
  integrity in the dataset.
\end{enumerate}

\subsection{\texorpdfstring{\textbf{4. Poll Aggregation and Data
Analysis}}{4. Poll Aggregation and Data Analysis}}\label{poll-aggregation-and-data-analysis}

\subsubsection{\texorpdfstring{\textbf{Poll
Aggregation}:}{Poll Aggregation:}}\label{poll-aggregation}

This survey will be combined with results from reputable polling firms
(e.g., YouGov, Ipsos, Gallup) to strengthen our forecast through a
\textbf{poll-of-polls} approach.

\begin{itemize}
\tightlist
\item
  \textbf{Weighting by Methodology and Recency}: Poll results will be
  weighted based on the rigor of their methodology (e.g., online
  vs.~phone surveys, sample size) and the recency of the poll. Recent,
  methodologically sound polls will receive more weight in the
  aggregation process.
\item
  \textbf{Handling Bias and Variability}: Aggregated results will adjust
  for pollster house effects (biases in methodology) and variability
  between polls, ensuring that no single poll dominates the prediction.
\end{itemize}

\subsubsection{\texorpdfstring{\textbf{Modeling
Approach}:}{Modeling Approach:}}\label{modeling-approach}

We will implement \textbf{Bayesian hierarchical models} to account for
variability across different states, demographics, and regions. This
will allow us to model the popular vote and potentially translate it
into \textbf{Electoral College predictions}.

\subsection{\texorpdfstring{\textbf{5. Budget
Allocation}}{5. Budget Allocation}}\label{budget-allocation}

\begin{itemize}
\tightlist
\item
  \textbf{Respondent Recruitment (Targeted ads, outreach)}: \$70,000\\
\item
  \textbf{Incentives (e.g., lottery prizes)}: \$10,000\\
\item
  \textbf{Survey Platform (Google Forms, Qualtrics subscription)}:
  \$5,000\\
\item
  \textbf{Data Validation Tools}: \$5,000\\
\item
  \textbf{Poll Aggregation \& Analysis Software}: \$10,000
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{\texorpdfstring{\textbf{6. Survey
Implementation}}{6. Survey Implementation}}\label{survey-implementation}

The survey will be implemented via \textbf{Google Forms}, which offers a
cost-effective platform for data collection. The link to the live survey
can be found here: \href{https://forms.gle/RC1464SvLvtoAYdv6}{Google
Form Survey}. A copy of the questions is provided below.

\subsubsection{\texorpdfstring{\textbf{Survey
Structure}:}{Survey Structure:}}\label{survey-structure}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Introduction}: Thank you for taking part in this survey aimed
  at predicting the outcome of the 2024 US Presidential election. Your
  insights are valuable to our research.
\end{enumerate}

Please note: - \textbf{All responses will be kept strictly
confidential.} - \textbf{Your participation is entirely voluntary.} -
\textbf{We kindly request that you answer all questions honestly and to
the best of your knowledge.} - \textbf{The survey is estimated to take
approximately 10 minutes to complete.} If you have any inquiries or
concerns regarding this survey, please don't hesitate to contact the
research team at
\href{mailto:shaw.wei@mail.utoronto.ca}{\nolinkurl{shaw.wei@mail.utoronto.ca}}.

Your contribution to this study is greatly appreciated! Each participant
will be entered into a lottery with a chance to win a \$100 gift card!

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \textbf{Section 1: Eligibility Screening}: Are you a U.S. citizen?
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Yes
\item
  No {[}If No, end survey{]}
\end{itemize}

Will you be 18 or older by Election Day (November 5, 2024)? - Yes - No
{[}If No, end survey{]}

Are you registered to vote in the United States? - Yes - No - Not sure -
Plan to register before the election

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  \textbf{Section 2: Demographic Information}: What is your age group?
\end{enumerate}

\begin{itemize}
\tightlist
\item
  18-29
\item
  30-44
\item
  45-64
\item
  65 or older
\item
  Prefer not to say
\end{itemize}

What is your gender? - Male - Female - Non-binary/Other - Prefer not to
say

What is your race/ethnicity? (Select all that apply) - White - Black or
African American - Hispanic or Latino - Asian - American Indian or
Alaska Native - Native Hawaiian or Pacific Islander - Prefer not to say
- Other: {[}Short text answer{]}

What is your highest level of education completed? - No high school -
High school graduate or equivalent - Some college, no degree -
Bachelor's degree - Graduate or professional degree - Prefer not to say

What was your total household income in 2023? - Less than \$30,000 -
\$30,000 - \$59,999 - \$60,000 - \$99,999 - \$100,000 - \$149,999 -
\$150,000 or more - Prefer not to say

In which region of the United States do you currently reside? -
Northeast (ME, NH, VT, MA, RI, CT, NY, NJ, PA) - Midwest (OH, IN, IL,
MI, WI, MN, IA, MO, ND, SD, NE, KS) - South (DE, MD, DC, VA, WV, NC, SC,
GA, FL, KY, TN, AL, MS, AR, LA, OK, TX) - West (MT, ID, WY, CO, NM, AZ,
UT, NV, WA, OR, CA, AK, HI)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  \textbf{Section 3: Political Views and Voting Intentions}: How likely
  are you to vote in the 2024 Presidential election?
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Definitely will vote
\item
  Probably will vote
\item
  Might or might not vote
\item
  Probably will not vote
\item
  Definitely will not vote
\end{itemize}

Generally speaking, do you usually think of yourself as a: - Democrat -
Republican - Independent - Prefer not to say - Other: {[}Short text
answer{]}

If the 2024 Presidential election were held today, who would you vote
for? - Kamala Harris (Democrat) - Donald Trump (Republican) - Undecided
- Prefer not to say - Other: {[}Short text answer{]}

How certain are you about your choice? - Very certain - Somewhat certain
- Not very certain - Not at all certain - Prefer not to say

Which THREE issues are most important to you in deciding your vote?
(Select exactly three) - Economy and jobs - Healthcare - Immigration -
Climate change - National security - Education - Gun policy - Social
justice/racial equality - Taxes - Crime and public safety - Foreign
policy - Other: {[}Short text answer{]}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \textbf{Section 4: Information Sources and Engagement}:
\end{enumerate}

What is your primary source of political news? (Select all that apply) -
Network TV news (ABC, CBS, NBC) - Cable TV news (CNN, Fox News, MSNBC) -
News websites - Social media - Radio - Print newspapers - Friends and
family - Other: {[}Short text answer{]}

How closely have you been following news about the 2024 Presidential
election? - Very closely - Somewhat closely - Not too closely - Not at
all - Not sure

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  \textbf{Section 5: Validation and Consent}: Please verify that you are
  a human by selecting ``Blue'' from the following options:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Red
\item
  Green
\item
  Blue
\item
  Yellow
\end{itemize}

Consent Statement: ``I understand that my participation in this survey
is voluntary and that my responses will be kept confidential. I agree
that my responses may be used for research purposes.'' - Yes, I agree -
No, I do not agree

Email Address: {[}Email field{]}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  \textbf{End Message}: ``Thank you for completing this survey. Your
  response has been recorded. If you have any questions about this
  survey or would like to be informed about the results, please contact
  {[}Your Contact Information{]}.''
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{\texorpdfstring{\textbf{7. Survey Design
Considerations}}{7. Survey Design Considerations}}\label{survey-design-considerations}

\begin{itemize}
\tightlist
\item
  \textbf{Question Wording}: All questions are carefully designed to
  avoid bias or leading responses.
\item
  \textbf{Neutrality}: Political questions are framed neutrally to avoid
  pushing respondents toward specific answers.
\item
  \textbf{Pilot Testing}: Before full deployment, the survey will
  undergo a pilot test to identify and resolve any issues.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

This methodology, combining rigorous sampling, data validation, and
aggregation, ensures that the election forecast is as accurate and
representative as possible.

\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
\begin{quote}
7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}
\end{quote}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Posterior predictive
check}\label{posterior-predictive-check}

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}
Examining how the model fits, and is affected by, the
data\end{minipage}%

\end{figure}%

\subsection{Diagnostics}\label{diagnostics}

\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\begin{figure}

\begin{minipage}{0.50\linewidth}
Checking the convergence of the MCMC algorithm\end{minipage}%

\end{figure}%

\newpage

\section{Acknowledgements}\label{acknowledgements}

R Core Team (2023)

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-tellingstories}
Alexander, Rohan. 2023. \emph{Telling Stories with Data}. Chapman;
Hall/CRC. \url{https://tellingstorieswithdata.com/}.

\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-palmerpenguins}
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{{palmerpenguins: Palmer Archipelago (Antarctica) penguin data}}.
\url{https://doi.org/10.5281/zenodo.3960218}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-shelter}
Toronto Shelter \& Support Services. 2024. \emph{Deaths of Shelter
Residents}.
\url{https://open.toronto.ca/dataset/deaths-of-shelter-residents/}.

\end{CSLReferences}

\end{document}

### 2024-10-23 scripts/06-model_data.R
Model updated.

@@ -126,13 +126,12 @@ ggplot(analysis_data, aes(x = end_date_num, y = percent, color = pollster_rating
 # Read the data
 analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
 
-# Calculate Trump and Harris percentages for each state
+# Calculate Trump and Harris percentages for each state using summarise and case_when
 analysis_data <- analysis_data %>%
   group_by(state) %>%
   mutate(
-    Trump_percent = max(percent[candidate_name == "Donald Trump"], na.rm = TRUE),
-    Harris_percent = max(percent[candidate_name == "Kamala Harris"], na.rm = TRUE)
-  )
+    Trump_percent = mean(case_when(candidate_name == "Donald Trump" ~ percent), na.rm = TRUE),
+    Harris_percent = mean(case_when(candidate_name == "Kamala Harris" ~ percent), na.rm = TRUE))
 
 # Create a binary outcome for prediction: 1 if Trump is predicted to win, 0 if Harris
 analysis_data <- analysis_data %>%

### 2024-10-23 paper/paper.qmd
Update paper model section.

@@
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the logistic regression model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].
 
-## Logistic Regression Model Build up
+## Logistic Regression Model Setup
 
@@
 
-	•	pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
-	•	state accounts for geographic variations in voter preferences.
-	•	population_group represents different demographic categories.
-	•	numeric_grade reflects the poll’s quality rating.
-	•	sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
-	•	methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
+- pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
+- state accounts for geographic variations in voter preferences.
+- population_group represents different demographic categories.
+- numeric_grade reflects the poll’s quality rating.
+- sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
+- methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
 
@@
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
-\end{align}
+\begin{align*}
+y_i | \mu_i &\sim \text{Bernoulli}(\mu_i) \\
+\mu_i &= \alpha + \beta_i + \gamma_i \\
+\alpha &\sim \text{Normal}(0, 2.5) \\
+\beta_i &\sim \text{Normal}(0, 2.5) \\
+\gamma_i &\sim \text{Normal}(0, 2.5)
+\end{align*}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+$logit(\mu_i) = \alpha + \beta_1 \cdot \text{pollster\_rating\_name}_i + \beta_2 \cdot \text{state}_i + \beta_3 \cdot \text{population\_group}_i + \beta_4 \cdot \text{numeric\_grade}_i + \beta_5 \cdot \text{sample\_size}_i + \beta_6 \cdot \text{methodology}_i$
 
@@
 logistic_model <- readRDS(here::here(("models/logistic_model.rds")))
+summary(logistic_model)
 ```
@@
 # Diagnostic plots for the MLR model
+
+```{r}
 par(mfrow = c(2, 2))
-plot(mlr_harris_model)
-par(mfrow = c(1, 1))  # Reset plot layout
+plot(logistic_model)
+par(mfrow = c(1, 1))
+```
 
@@
 # Appendix {-}
-=======
+
 # Pollster Methodology Overview and Evaluation
@@
 
+# Load required library
+library(caret)
+
+# Set a seed for reproducibility
+set.seed(853)
+analysis_data_reduced<- analysis_data_reduced %>% na.omit(analysis_data_reduced)
+# Split the data (70% training, 30% testing)
+trainIndex <- createDataPartition(analysis_data_reduced$trump_win, p = 0.7, list=FALSE)
+train_data <- analysis_data_reduced[trainIndex, ]
+test_data <- analysis_data_reduced[-trainIndex, ]
+
+```
+
+```{r}
+# Make predictions on the test dataset
+predicted_probabilities <- predict(logistic_model, newdata = test_data, type = "response")
+
+# Binarize the predicted probabilities using a threshold of 0.5
+predicted_classes <- ifelse(predicted_probabilities > 0.5, 1, 0)
+
+# Confusion Matrix
+conf_matrix <- confusionMatrix(factor(predicted_classes), factor(test_data$trump_win))
+print(conf_matrix)
+
+# Precision, Recall, and F1-score
+precision <- posPredValue(factor(predicted_classes), factor(test_data$trump_win))
+recall <- sensitivity(factor(predicted_classes), factor(test_data$trump_win))
+f1_score <- 2 * ((precision * recall) / (precision + recall))
+
+cat("Precision:", precision, "\n")
+cat("Recall:", recall, "\n")
+cat("F1-score:", f1_score, "\n")
+```
+
+```{r}
+# Load the pre-trained logistic model from RDS
+logistic_model <- readRDS(here:here("models/logistic_model.rds"))
+
+# Calculate Trump and Harris percentages for each state (you still need to prepare the data)
+analysis_data <- analysis_data %>%
+  group_by(state) %>%
+  mutate(
+    Trump_percent = mean(case_when(candidate_name == "Donald Trump" ~ percent), na.rm = TRUE),
+    Harris_percent = mean(case_when(candidate_name == "Kamala Harris" ~ percent), na.rm = TRUE)
+  ) %>%
+  # Create a binary outcome for prediction: 1 if Trump is predicted to win, 0 if Harris
+  mutate(trump_win = ifelse(Trump_percent > Harris_percent, 1, 0))
+
+# Create 10-fold cross-validation resampling
+folds <- vfold_cv(analysis_data, v = 10)
+
+# Fit the resamples using the loaded logistic model
+cross_validation <- fit_resamples(
+  logistic_model,
+  data = analysis_data,
+  resamples = folds,
+  metrics = metric_set(accuracy, roc_auc),
+  control = control_resamples(save_pred = TRUE)
+)
+
+# Collect and display metrics
+collect_metrics(cross_validation) %>%
+  select(.metric, mean) %>%
+  knitr::kable(
+    col.names = c("Metric", "Mean"),
+    digits = 2,
+    format.args = list(big.mark = ",")
+  )
+
+# Display confusion matrix for resampled results
+conf_mat_resampled(cross_validation) %>%
+  mutate(Proportion = Freq / sum(Freq)) %>%
+  knitr::kable(
+    digits = 2,
+    format.args = list(big.mark = ","))
 ```

### 2024-10-23 scripts/06-model_data.R
Model update.

@@ -126,6 +126,9 @@ ggplot(analysis_data, aes(x = end_date_num, y = percent, color = pollster_rating
 # Read the data
 analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
 
+# For reproducibility
+set.seed(853)
+
 # Calculate Trump and Harris percentages for each state using summarise and case_when
 analysis_data <- analysis_data %>%
   group_by(state) %>%
@@ -138,15 +141,13 @@ analysis_data <- analysis_data %>%
   mutate(trump_win = ifelse(Trump_percent > Harris_percent, 1, 0))
 
 # Summarize and clean the data to avoid duplicates
-set.seed(853)
-
-analysis_data_reduced <- 
-  analysis_data |> 
-  slice_sample(n = 1000)
+analysis_data_split <- initial_split(analysis_data, prop = 0.70)
+analysis_data_train <- training(analysis_data_split)
+analysis_data_test <- testing(analysis_data_split)
 
 logistic_model <- stan_glm(
   trump_win ~ pollster_rating_name + state + population_group + numeric_grade + sample_size + methodology,
-  data = analysis_data_reduced,
+  data = analysis_data_train,
   family = binomial(link = "logit"),
   prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
   prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),

### 2024-10-23 scripts/03-clean_data.R
Update cleaned data csv format to parquet

@@ -8,8 +8,12 @@
 # Any other information needed? NA
 
 #### Workspace setup ####
+install.packages("arrow")
 library(tidyverse)
 library(dplyr)
+library(arrow)
+
+# Read the raw data
 raw_data <- read_csv("data/01-raw_data/US_voting.csv")
 colnames(raw_data)
 
@@ -74,3 +78,5 @@ head(cleaned_data)
 #### Save data ####
 # Save the cleaned dataset to a new CSV file
 write_csv(cleaned_data, "data/02-analysis_data/cleaned_US_voting.csv")
+
+write_parquet(cleaned_data, "data/02-analysis_data/cleaned_US_voting.parquet")

### 2024-10-23 paper/paper.qmd
Update model section and make prediction.

--- 2024-10-23 paper/paper.qmd
@@
 ```{r}
+#install.packages("tidymodels")
 library(tidyverse)
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+We use the statistical programming language R [@citeR].... Following @tellingstories, we consider...
 
@@
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+Some of our data is of penguins (@fig-bills),
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+To model Donald Trump’s polling percentages over time, we employed a Bayesian linear regression framework.
+Bayesian methods provide a flexible approach to inference by incorporating prior beliefs and updating them with observed data, allowing us to quantify uncertainty in both parameter estimates and predictions.
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].
 
-## Logistic Regression Model Build up
+## Multiple Linear Regression Model Overview
+The model now predicts Trump’s polling percentage (percent) using the following predictors:
 
-To predict whether Donald Trump would win over Kamala Harris based on polling data, we constructed a logistic regression model using a subset of 1,000 randomly sampled observations from our cleaned dataset.
-The dependent variable, trump_win, is a binary outcome representing whether Trump was predicted to win in a given state (1 for Trump win, 0 for Harris win).
-The independent variables included in the model are pollster_rating_name, state, population_group, numeric_grade, sample_size, and methodology.
+- Numeric Grade (numeric_grade): Reflects the quality rating of the pollster.
+- Sample Size (sample_size): The number of respondents in the poll.
+- State (state): A categorical variable for different U.S. states.
+- Transparency Score (transparency_score): A measure of how transparent the polling data and methodology are.
+- End Date (end_date): The date the poll was completed, which might capture trends over time.
 
-We used the logit link function given that our outcome variable is binary.
-The logistic regression model estimates the log odds of Trump winning as a linear function of these predictors.
-Each predictor variable was selected based on its relevance to polling outcomes:
+The model takes the form:
+The model takes the form:
 
-	•	pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
-	•	state accounts for geographic variations in voter preferences.
-	•	population_group represents different demographic categories.
-	•	numeric_grade reflects the poll’s quality rating.
-	•	sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
-	•	methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
+# #Interpretation of Coefficients:
 
-We applied a Bayesian approach to estimate the logistic regression model using Stan, with weakly informative priors (Normal distribution with mean 0 and standard deviation 2.5) for both the coefficients and the intercept.
-These priors reflect our assumption that the effect of each predictor is centered around 0, with a moderate level of uncertainty.
-By incorporating state and demographic information along with pollster quality and methodology, we aim to capture the variability in polling predictions across different regions and polling practices.
-The use of Bayesian inference allows us to quantify uncertainty in our predictions more effectively.
+- Intercept (\beta_0): This is the predicted Trump polling percentage when all predictors (numeric grade, sample size, state, transparency score, and end date) are at their baseline or zero value.
+- Numeric Grade (\beta_1): This coefficient measures how much Trump’s polling percentage changes as the pollster’s numeric grade increases.
+A positive and significant coefficient would indicate that higher-rated pollsters report better polling numbers for Trump, while a negative coefficient would suggest the opposite.
+- Sample Size (\beta_2): This measures the impact of the number of respondents on Trump’s polling percentage.
+A positive coefficient would indicate that larger sample sizes are associated with higher polling percentages for Trump.
+- State (\beta_3): The coefficients for the state variable represent differences in Trump’s polling percentage in each state compared to the reference state (baseline category).
+For example, if the coefficient for Florida is negative, it means Trump polls lower in Florida compared to the reference state.
+- Transparency Score (\beta_4): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll.
+A positive coefficient would indicate that polls with higher transparency tend to report higher polling percentages for Trump, whereas a negative coefficient would imply the opposite.
+- End Date (\beta_5): The end date is a time-related variable, capturing trends over time.
+A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.
 
-We use weakly informative Normal priors for the intercept ( \alpha ) and coefficients ( \beta_i ), centered around zero with a standard deviation of 2.5.
-These priors were chosen to allow the data to influence the predictions while still reflecting reasonable uncertainty.
-Specifically:
+## Interpretation
+The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:
+- The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
+A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.
+- The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.
+- The state-level effects account for regional differences in Trump’s support.
+Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
-\end{align}
+# Model Evalutation
+- R-squared
+@tbl-summary shows the summary table for the model. And then evaluate it on the test set. It appears as though the model is having difficulty identifying Trump supporters.
+```{r}
+#| echno: False
+#| label: tbl-summary
+#| tbl-cap: Relationship between wing length and width
+#| echo: false
+#| warning: false
+#| message: false
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+library(knitr)
+regression_model<-readRDS(here::here("models/regression_model.rds"))
+summary<-summary(regression_model)
+# Extract the coefficients (which can be formatted as a table)
+coefficients_table <- summary$coefficients
+
+# Display the coefficients table using kable
+kable(coefficients_table, digits = 3, caption = "Regression Model Coefficients")
+```
+
+# Diagnostic plots for the model
+```{r}
+#| echno: false
+#| label: fig-diagnosis
+#| tbl-cap: Linear Regression Assumptions hold.
+#| echo: false
+#| warning: false
+#| message: false
+
+par(mfrow = c(2, 2))  
+plot(regression_model)
+```
 
 ```{r}
-logistic_model <- readRDS(here::here(("models/logistic_model.rds")))
+library(car)
+vif(regression_model)
 ```
-
-# Diagnostic plots for the MLR model
-par(mfrow = c(2, 2))
-plot(mlr_harris_model)
-par(mfrow = c(1, 1))  # Reset plot layout
 
@@
 
-Our results are summarized in ...
+## Predict and Combine with Electroal College to Predict
 
-```{r}
+```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
+#| echno: false
+#| label: tbl-prediction
+#| tbl-cap: Prediction for Trump
+#| echo: false
+#| warning: false
+#| message: false
 
-library(rstanarm)
+# Define electoral votes for each state
+electoral_votes <- data.frame(
+  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", 
+            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
+            "Maine CD-1", "Maine CD-2", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+            "Missouri", "Montana", "Nebraska", "Nebraska CD-1", "Nebraska CD-2", "Nebraska CD-3", "Nevada", 
+            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
+            "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", 
+            "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
+            "District of Columbia"),
+  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 2, 1, 1, 10, 11, 15, 10, 6, 10, 
+                      3, 5, 1, 1, 2, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
+)
 
-first_model <-
-  readRDS(file = (here::here("models/logistic_model.rds")))
+# Apply the regression model to predict Trump's percentage in each state
+analysis_data$predicted_percent_trump <- predict(regression_model, newdata = analysis_data)
+
+# Summarize Trump's predicted percentage for each state
+total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data, FUN = mean)
+
+# Join electoral vote data with Trump's predictions
+state_predictions <- merge(total_trump, electoral_votes, by = "state")
+
+# Determine the winner for each state based on Trump’s predicted percentage
+state_predictions$winner <- ifelse(state_predictions$predicted_percent_trump > 50, "Trump", "Harris")
+
+# Create a table showing the prediction results
+library(knitr)
+kable(state_predictions, col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),
+      digits = 2, caption = "Prediction for Trump by State")
 ```
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
 ```{r}
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
 ```{r}
@@
 #| layout-ncol: 2
+library(caret)
+library(rstanarm)
+library(ggplot2)
+library(dplyr)
+# Split the data into training (70%) and test (30%) sets
+set.seed(853)  # For reproducibility
 

### 2024-10-23 paper/paper.tex
Model update.
Update model section and make prediction.

@@
 \author{First author \and Yongqi Liu \and Yuxuan Wei}
-\date{October 22, 2024}
+\date{October 23, 2024}
 
@@
 \begin{Highlighting}[]
+\CommentTok{\#install.packages("tidymodels")}
 \FunctionTok{library}\NormalTok{(tidyverse)}
@@
 \begin{verbatim}
-Rows: 1951 Columns: 10
+Rows: 1683 Columns: 11
 -- Column specification --------------------------------------------------------
@@
 chr  (5): pollster_rating_name, methodology, state, candidate_name, populati...
-dbl  (3): numeric_grade, sample_size, percent
+dbl  (4): numeric_grade, sample_size, percent, transparency_score
 date (2): start_date, end_date
@@
 We use the statistical programming language R (R Core Team 2023)\ldots.
-Our data (Toronto Shelter \& Support Services 2024)\ldots. Following
-Alexander (2023), we consider\ldots{}
+Following Alexander (2023), we consider\ldots{}
 
@@
 
-Some of our data is of penguins (\textbf{?@fig-bills}), from Horst,
-Hill, and Gorman (2020).
+Some of our data is of penguins (\textbf{?@fig-bills}),
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,\ldots{}
-
-Here we briefly describe the Bayesian analysis model used to
-investigate\ldots{} Background details and diagnostics are included in
-Appendix~\ref{sec-model-details}.
-
-\subsection{Logistic Regression Model Build
-up}\label{logistic-regression-model-build-up}
-
-To predict whether Donald Trump would win over Kamala Harris based on
-polling data, we constructed a logistic regression model using a subset
-of 1,000 randomly sampled observations from our cleaned dataset. The
-dependent variable, trump\_win, is a binary outcome representing whether
-Trump was predicted to win in a given state (1 for Trump win, 0 for
-Harris win). The independent variables included in the model are
-pollster\_rating\_name, state, population\_group, numeric\_grade,
-sample\_size, and methodology.
-
-We used the logit link function given that our outcome variable is
-binary. The logistic regression model estimates the log odds of Trump
-winning as a linear function of these predictors. Each predictor
-variable was selected based on its relevance to polling outcomes:
-
-\begin{verbatim}
-•   pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
-•   state accounts for geographic variations in voter preferences.
-•   population_group represents different demographic categories.
-•   numeric_grade reflects the poll’s quality rating.
-•   sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
-•   methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
-\end{verbatim}
-
-We applied a Bayesian approach to estimate the logistic regression model
-using Stan, with weakly informative priors (Normal distribution with
-mean 0 and standard deviation 2.5) for both the coefficients and the
-intercept. These priors reflect our assumption that the effect of each
-predictor is centered around 0, with a moderate level of uncertainty. By
-incorporating state and demographic information along with pollster
-quality and methodology, we aim to capture the variability in polling
-predictions across different regions and polling practices. The use of
-Bayesian inference allows us to quantify uncertainty in our predictions
-more effectively.
-
-We use weakly informative Normal priors for the intercept ( \alpha ) and
-coefficients ( \beta\_i ), centered around zero with a standard
-deviation of 2.5. These priors were chosen to allow the data to
-influence the predictions while still reflecting reasonable uncertainty.
-Specifically:
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
-\end{align}
-
-We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
-package of Goodrich et al. (2022). We use the default priors from
-\texttt{rstanarm}.
+To model Donald Trump's polling percentages over time, we employed a
+Bayesian linear regression framework. Bayesian methods provide a
+flexible approach to inference by incorporating prior beliefs and
+updating them with observed data, allowing us to quantify uncertainty in
+both parameter estimates and predictions.
+
+Here we briefly describe the Bayesian model used to investigate the
+winning probability of Trump. Background details and diagnostics are
+included in Appendix~\ref{sec-model-details}.
+
+\subsection{Multiple Linear Regression Model
+Overview}\label{multiple-linear-regression-model-overview}
+
+The model now predicts Trump's polling percentage (percent) using the
+following predictors:
+
+\begin{itemize}
+\tightlist
+\item
+  Numeric Grade (numeric\_grade): Reflects the quality rating of the
+  pollster.
+\item
+  Sample Size (sample\_size): The number of respondents in the poll.
+\item
+  State (state): A categorical variable for different U.S. states.
+\item
+  Transparency Score (transparency\_score): A measure of how transparent
+  the polling data and methodology are.
+\item
+  End Date (end\_date): The date the poll was completed, which might
+  capture trends over time.
+\end{itemize}
+
+The model takes the form: The model takes the form:
+
+\section{\#Interpretation of
+Coefficients:}\label{interpretation-of-coefficients}
+
+\begin{itemize}
+\tightlist
+\item
+  Intercept (\beta\_0): This is the predicted Trump polling percentage
+  when all predictors (numeric grade, sample size, state, transparency
+  score, and end date) are at their baseline or zero value.
+\item
+  Numeric Grade (\beta\_1): This coefficient measures how much Trump's
+  polling percentage changes as the pollster's numeric grade increases.
+  A positive and significant coefficient would indicate that
+  higher-rated pollsters report better polling numbers for Trump, while
+  a negative coefficient would suggest the opposite.
+\item
+  Sample Size (\beta\_2): This measures the impact of the number of
+  respondents on Trump's polling percentage. A positive coefficient
+  would indicate that larger sample sizes are associated with higher
+  polling percentages for Trump.
+\item
+  State (\beta\_3): The coefficients for the state variable represent
+  differences in Trump's polling percentage in each state compared to
+  the reference state (baseline category). For example, if the
+  coefficient for Florida is negative, it means Trump polls lower in
+  Florida compared to the reference state.
+\item
+  Transparency Score (\beta\_4): This coefficient shows how much Trump's
+  polling percentage is affected by the transparency of the poll. A
+  positive coefficient would indicate that polls with higher
+  transparency tend to report higher polling percentages for Trump,
+  whereas a negative coefficient would imply the opposite.
+\item
+  End Date (\beta\_5): The end date is a time-related variable,
+  capturing trends over time. A positive and significant coefficient
+  would suggest that Trump's polling percentage has increased as the
+  election date approaches, while a negative coefficient would suggest a
+  decrease in his polling numbers over time.
+\end{itemize}
+
+\subsection{Interpretation}\label{interpretation}
+
+The posterior distributions of the parameters allow us to quantify the
+uncertainty around each effect: - The coefficient for end\_date informs
+us about how Trump's polling percentages have evolved over time. A
+positive coefficient would suggest an upward trend, while a negative
+coefficient would indicate a decline. - The coefficient for
+numeric\_grade captures the impact of pollster quality on the polling
+percentage. High-quality pollsters may produce different estimates
+compared to lower-quality ones. - The state-level effects account for
+regional differences in Trump's support. Some states may show
+significantly higher or lower levels of support, even after adjusting
+for the time of the poll and pollster quality.
+
+\section{Model Evalutation}\label{model-evalutation}
+
+\begin{itemize}
+\tightlist
+\item
+  R-squared Table~\ref{tbl-summary} shows the summary table for the
+  model. And then evaluate it on the test set. It appears as though the
+  model is having difficulty identifying Trump supporters.
+\end{itemize}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2985}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1343}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1642}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1194}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2836}}@{}}
+
+\caption{\label{tbl-summary}Relationship between wing length and width}
+
+\tabularnewline
+
+\caption{Regression Model Coefficients}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Std. Error
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+t value
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Pr(\textgreater\textbar t\textbar)
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Std. Error
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+t value
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Pr(\textgreater\textbar t\textbar)
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+(Intercept) & -67.184 & 14.445 & -4.651 & 0.000 \\
+numeric\_grade & 0.914 & 1.006 & 0.909 & 0.364 \\
+sample\_size & 0.000 & 0.000 & 0.205 & 0.838 \\
+stateArizona & -5.020 & 2.582 & -1.944 & 0.052 \\
+stateArkansas & 5.569 & 4.380 & 1.272 & 0.204 \\
+stateCalifornia & -18.345 & 2.738 & -6.699 & 0.000 \\
+stateColorado & -13.340 & 3.002 & -4.443 & 0.000 \\
+stateConnecticut & -13.480 & 3.574 & -3.772 & 0.000 \\
+stateFlorida & -3.214 & 2.740 & -1.173 & 0.241 \\
+stateGeorgia & -4.814 & 2.573 & -1.871 & 0.062 \\
+stateIdaho & 3.467 & 4.379 & 0.792 & 0.429 \\
+stateIllinois & -14.064 & 3.275 & -4.294 & 0.000 \\
+stateIndiana & 0.902 & 3.268 & 0.276 & 0.783 \\
+stateIowa & -4.692 & 3.101 & -1.513 & 0.131 \\
+stateKansas & -0.798 & 3.275 & -0.244 & 0.808 \\
+stateMaine & -10.182 & 2.726 & -3.735 & 0.000 \\
+stateMaryland & -20.244 & 2.998 & -6.753 & 0.000 \\
+stateMassachusetts & -22.543 & 2.753 & -8.190 & 0.000 \\
+stateMichigan & -6.635 & 2.576 & -2.576 & 0.010 \\
+stateMinnesota & -10.250 & 2.684 & -3.819 & 0.000 \\
+stateMissouri & 1.087 & 2.803 & 0.388 & 0.698 \\
+stateMontana & 1.379 & 2.784 & 0.495 & 0.620 \\
+stateNational & -7.935 & 2.546 & -3.117 & 0.002 \\
+stateNebraska & -7.528 & 2.782 & -2.706 & 0.007 \\
+stateNevada & -5.617 & 2.594 & -2.165 & 0.031 \\
+stateNew Hampshire & -8.778 & 2.655 & -3.306 & 0.001 \\
+stateNew Jersey & -15.189 & 3.577 & -4.246 & 0.000 \\
+stateNew Mexico & -10.980 & 3.099 & -3.543 & 0.000 \\
+stateNew York & -15.239 & 2.633 & -5.789 & 0.000 \\
+stateNorth Carolina & -4.783 & 2.582 & -1.853 & 0.064 \\
+stateNorth Dakota & 2.970 & 4.380 & 0.678 & 0.498 \\
+stateOhio & -2.796 & 2.677 & -1.045 & 0.296 \\
+stateOklahoma & 8.450 & 4.385 & 1.927 & 0.054 \\
+stateOregon & -14.974 & 4.385 & -3.415 & 0.001 \\
+statePennsylvania & -6.375 & 2.568 & -2.483 & 0.013 \\
+stateRhode Island & -13.374 & 2.994 & -4.467 & 0.000 \\
+stateSouth Carolina & -1.939 & 4.376 & -0.443 & 0.658 \\
+stateSouth Dakota & 0.394 & 3.096 & 0.127 & 0.899 \\
+stateTennessee & 3.624 & 4.378 & 0.828 & 0.408 \\
+stateTexas & -3.825 & 2.681 & -1.427 & 0.154 \\
+stateUtah & -3.243 & 4.385 & -0.740 & 0.460 \\
+stateVermont & -23.452 & 3.581 & -6.549 & 0.000 \\
+stateVirginia & -9.518 & 2.663 & -3.575 & 0.000 \\
+stateWashington & -15.876 & 3.264 & -4.864 & 0.000 \\
+stateWest Virginia & 8.265 & 4.379 & 1.887 & 0.059 \\
+stateWisconsin & -6.444 & 2.571 & -2.506 & 0.012 \\
+stateWyoming & 15.921 & 4.377 & 3.637 & 0.000 \\
+transparency\_score & -0.646 & 0.088 & -7.383 & 0.000 \\
+end\_date & 0.006 & 0.001 & 8.880 & 0.000 \\
+
+\end{longtable}
+
+\section{Diagnostic plots for the
+model}\label{diagnostic-plots-for-the-model}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-diagnosis-1.pdf}
+
+}
+
+\caption{\label{fig-diagnosis}}
+
+\end{figure}%
 
@@
 \begin{Highlighting}[]
-\NormalTok{logistic\_model }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{((}\StringTok{"models/logistic\_model.rds"}\NormalTok{)))}
+\FunctionTok{library}\NormalTok{(car)}
 \end{Highlighting}
@@
 
-\section{Diagnostic plots for the MLR
-model}\label{diagnostic-plots-for-the-mlr-model}
-
-par(mfrow = c(2, 2)) plot(mlr\_harris\_model) par(mfrow = c(1, 1)) \#
-Reset plot layout
+\begin{verbatim}
+Loading required package: carData
+\end{verbatim}
+
+\begin{verbatim}
+
+Attaching package: 'car'
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:dplyr':
+
+    recode
+\end{verbatim}
+
+\begin{verbatim}
+The following object is masked from 'package:purrr':
+
+    some
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{vif}\NormalTok{(regression\_model)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+                       GVIF Df GVIF^(1/(2*Df))
+numeric_grade      1.294110  1        1.137590
+sample_size        1.289750  1        1.135672
+state              2.082151 44        1.008369
+transparency_score 1.263558  1        1.124081
+end_date           1.309491  1        1.144330
+\end{verbatim}
 
@@
 
-Our results are summarized in \ldots{}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(rstanarm)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Loading required package: Rcpp
-\end{verbatim}
-
-\begin{verbatim}
-This is rstanarm version 2.32.1
-\end{verbatim}
-
-\begin{verbatim}
-- See https://mc-stan.org/rstanarm/articles/priors for changes to default priors!
-\end{verbatim}
-
-\begin{verbatim}
-- Default priors may change, so it's safest to specify priors, even if equivalent to the defaults.
-\end{verbatim}
-
-\begin{verbatim}
-- For execution on a local, multicore CPU with excess RAM we recommend calling
-\end{verbatim}
-
-\begin{verbatim}
-  options(mc.cores = parallel::detectCores())
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{first\_model }\OtherTok{\textless{}{-}}
-  \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =}\NormalTok{ (here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"models/logistic\_model.rds"}\NormalTok{)))}
-\end{Highlighting}
-\end{Shaded}
+\subsection{Predict and Combine with Electroal College to
+Predict}\label{predict-and-combine-with-electroal-college-to-predict}
+
+\begin{longtable}[]{@{}lrrl@{}}
+
+\caption{\label{tbl-prediction}Prediction for Trump}
+
+\tabularnewline
+
+\caption{Prediction for Trump by State}\tabularnewline
+\toprule\noalign{}
+State & Trump Predicted \% & Electoral Votes & Winner \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+State & Trump Predicted \% & Electoral Votes & Winner \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Alaska & 53.00 & 3 & Trump \\
+Arizona & 47.62 & 11 & Harris \\
+Arkansas & 56.60 & 6 & Trump \\
+California & 34.39 & 55 & Harris \\
+Colorado & 37.60 & 9 & Harris \\
+Connecticut & 39.09 & 7 & Harris \\
+Florida & 48.89 & 29 & Harris \\
+Georgia & 47.71 & 16 & Harris \\
+Idaho & 54.50 & 4 & Trump \\
+Illinois & 36.37 & 20 & Harris \\
+Indiana & 53.73 & 11 & Trump \\
+Iowa & 46.68 & 6 & Harris \\
+Kansas & 49.63 & 6 & Harris \\
+Maine & 41.13 & 2 & Harris \\
+Maryland & 32.88 & 10 & Harris \\
+Massachusetts & 29.80 & 11 & Harris \\
+Michigan & 45.92 & 15 & Harris \\
+Minnesota & 42.40 & 10 & Harris \\
+Missouri & 52.51 & 10 & Trump \\
+Montana & 54.20 & 3 & Trump \\
+Nebraska & 45.16 & 5 & Harris \\
+Nevada & 47.00 & 6 & Harris \\
+New Hampshire & 42.86 & 4 & Harris \\
+New Jersey & 37.60 & 14 & Harris \\
+New Mexico & 42.05 & 5 & Harris \\
+New York & 37.45 & 29 & Harris \\
+North Carolina & 47.98 & 16 & Harris \\
+North Dakota & 54.00 & 3 & Trump \\
+Ohio & 49.58 & 18 & Harris \\
+Oklahoma & 58.70 & 7 & Trump \\
+Oregon & 35.30 & 6 & Harris \\
+Pennsylvania & 46.28 & 20 & Harris \\
+Rhode Island & 39.12 & 4 & Harris \\
+South Carolina & 50.60 & 9 & Trump \\
+South Dakota & 52.18 & 3 & Trump \\
+Tennessee & 55.30 & 11 & Trump \\
+Texas & 48.51 & 38 & Harris \\
+Utah & 47.00 & 6 & Harris \\
+Vermont & 28.00 & 3 & Harris \\
+Virginia & 43.22 & 13 & Harris \\
+Washington & 36.33 & 12 & Harris \\
+West Virginia & 59.30 & 5 & Trump \\
+Wisconsin & 45.96 & 10 & Harris \\
+Wyoming & 67.60 & 3 & Trump \\
+
+\end{longtable}
 
@@
 
-\section*{\# Appendix}\label{appendix}
-\addcontentsline{toc}{section}{\# Appendix}
+\section*{Appendix}\label{appendix}
+\addcontentsline{toc}{section}{Appendix}
 
@@
 
-In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
-predictive check. This shows\ldots{}
-
-In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
-with the prior. This shows\ldots{}
-
 \begin{figure}
@@
 \subsection{Diagnostics}\label{diagnostics}
-
-\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
-suggests\ldots{}
-
-\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
-suggests\ldots{}
 
@@
 
-\bibitem[\citeproctext]{ref-rstanarm}
-Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
-{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
-\url{https://mc-stan.org/rstanarm/}.
-
-\bibitem[\citeproctext]{ref-palmerpenguins}
-Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
-\emph{{palmerpenguins: Palmer Archipelago (Antarctica) penguin data}}.
-\url{https://doi.org/10.5281/zenodo.3960218}.
-
 \bibitem[\citeproctext]{ref-citeR}
@@
 
-\bibitem[\citeproctext]{ref-shelter}
-Toronto Shelter \& Support Services. 2024. \emph{Deaths of Shelter
-Residents}.
-\url{https://open.toronto.ca/dataset/deaths-of-shelter-residents/}.
-
 \end{CSLReferences}

### 2024-10-23 scripts/03-clean_data.R

@@ -33,7 +33,7 @@ cleaned_data <- cleaned_data %>%
 # Clean raw dataset, remove columns with many missing values and keep the columns we want to make analysis on
 cleaned_data <- cleaned_data %>% dplyr::select(pollster_rating_name, methodology, numeric_grade, start_date,
                                                end_date, sample_size, population, state, 
-                                           candidate_name, pct) 
+                                           candidate_name, pct, transparency_score) 
 
 # Change name for different types of voters in population column
 cleaned_data <- cleaned_data %>%

### 2024-10-23 scripts/06-model_data.R

@@ -9,155 +9,77 @@
 
 
 #### Workspace setup ####
-#install.packages("splines")
+#install.packages("caret")
+#install.packages("rsample")
 library(tidyverse)
 library(dplyr)
-library(splines)
 library(rstanarm)
 library(bayesplot)
-library(rstanarm)
 library(ggplot2)
-#install.packages("caret")
 library(caret)
 library(modelsummary)
+library(arrow)
+library(rsample)
+library(splines)
 
 
 #### Read data ####
-analysis_data <- read_csv("data/02-analysis_data/cleaned_US_voting.csv")
+analysis_data <- read_parquet("data/02-analysis_data/cleaned_US_voting.parquet")
+
+analysis_data <- analysis_data |>
+  filter(candidate_name == "Donald Trump") 
+
+# Build up model
+regression_model <- lm(percent ~ numeric_grade + sample_size + state + transparency_score + end_date, 
+                      data = analysis_data)
+
+#### Save model ####
+# Save the model 
+saveRDS(regression_model, file = "models/regression_model.rds")
+
+
+
 
 ### Model data ####
-# 1. Bayesian Model
-# Change 'end_date' and 'state' to factor variables
-analysis_data <- analysis_data |>
-  mutate( end_date = as.numeric(end_date), state = factor(state))
-
-# Bayesian Regression Model (Without State Effect):
-bayesian_model <- stan_glm(
-  percent ~ ns(end_date, df = 9) + pollster_rating_name, 
-  data = analysis_data,
-  family = gaussian(),
-  prior = normal(0, 2.5),  # Weakened prior to allow more spread
-  prior_intercept = normal(50, 20),  # Slightly wider prior for intercept
-  seed = 1234,
-  iter = 3000,  # Increase iterations for better convergence
-  chains = 4,
-  refresh = 0)
-
-# Bayesian Mixed-Effects Model (With Random Effects for State and Pollster):
-bayesian_model_state <- stan_glmer(
-  percent ~ ns(end_date, df = 9) + (1 | pollster_rating_name) + (1 | state),
-  data = analysis_data,
-  family = gaussian(),
-  prior = normal(0, 5),  # Moderate prior for the coefficients
-  prior_intercept = normal(50, 20),  # Adjusted prior intercept
-  seed = 1234,
-  adapt_delta = 0.99,  # Increased adapt_delta to improve convergence
[…]

### 2024-10-24 paper/paper.qmd
Update paper.

@@
       digits = 2, caption = "Prediction for Trump by State")
+
+# Print the results
+print(paste("Trump Electoral Votes:", trump_electoral_votes))
+print(paste("Harris Electoral Votes:", harris_electoral_votes))
+```
+
+```{r}
+summary(regression_model)
 ```

### 2024-10-24 paper/paper.tex
Update Data Section in the Paper

@@
 
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{241,243,245}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-
 \providecommand{\tightlist}{%
@@
   pdftitle={My title},
-  pdfauthor={First author; Yongqi Liu; Yuxuan Wei},
+  pdfauthor={Xuanle Zhou; Yongqi Liu; Yuxuan Wei},
   colorlinks=true,
@@
 \subtitle{My subtitle if needed}
-\author{First author \and Yongqi Liu \and Yuxuan Wei}
+\author{Xuanle Zhou \and Yongqi Liu \and Yuxuan Wei}
 \date{October 23, 2024}
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\#install.packages("tidymodels")}
-\FunctionTok{library}\NormalTok{(tidyverse)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
--- Attaching core tidyverse packages ------------------------ tidyverse 2.0.0 --
-v dplyr     1.1.4     v readr     2.1.5
-v forcats   1.0.0     v stringr   1.5.1
-v ggplot2   3.5.1     v tibble    3.2.1
-v lubridate 1.9.3     v tidyr     1.3.1
-v purrr     1.0.2     
--- Conflicts ------------------------------------------ tidyverse_conflicts() --
-x dplyr::filter() masks stats::filter()
-x dplyr::lag()    masks stats::lag()
-i Use the conflicted package (<http://conflicted.r-lib.org/>) to force all conflicts to become errors
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(ggplot2)}
-\NormalTok{analysis\_data }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data/02{-}analysis\_data/cleaned\_US\_voting.csv"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Rows: 1683 Columns: 11
--- Column specification --------------------------------------------------------
-Delimiter: ","
-chr  (5): pollster_rating_name, methodology, state, candidate_name, populati...
-dbl  (4): numeric_grade, sample_size, percent, transparency_score
-date (2): start_date, end_date
-
-i Use `spec()` to retrieve the full column specification for this data.
-i Specify the column types or set `show_col_types = FALSE` to quiet this message.
-\end{verbatim}
-
 \section{Introduction}\label{introduction}
@@
 
-We use the statistical programming language R (R Core Team 2023)\ldots.
-Following Alexander (2023), we consider\ldots{}
-
-Overview text
-
-\subsection{Measurement}\label{measurement}
-
-Some paragraphs about how we go from a phenomena in the world to an
-entry in the dataset.
+This study uses R packages (R Core Team 2023) to clean and analyz the
+dataset , including libraries from tidyverse {[}{]}, ggplot2{[}{]}.
+
+After cleaning the data, which included grouping and removing missing
+values, the analysis dataset consists of 1,683 observations, focusing on
+the following 11 variables: pollster name, methodology, numeric grade,
+start date, end date, sample size, candidate name, percentage,
+transparency score, and population group.
+
+\subsection{Data Measurement and
+Considerations}\label{data-measurement-and-considerations}
+
+The dataset for this analysis is sourced from FiveThirtyEight, which
+rigorously collects and aggregates polling data from a variety of firms
+to reflect public opinion. To ensure the integrity of the data, only
+polls that adhere to specific criteria are included in the dataset. Each
+poll must provide essential information, such as the pollster's name,
+survey dates, sample sizes, and methodological details (e.g., polling
+medium, voter files, weighting criteria). Polls that are deemed
+nonscientific, that blend data from multiple sources, or that are
+conducted by hobbyists are excluded.
+
+Once a poll meets these stringent standards, it is incorporated into the
+database, enabling it to inform polling averages, forecasts, and
+political coverage. This careful selection process ensures that the
+dataset accurately captures and reflects the nuances of public sentiment
+and behavior.
 
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome
-variable or update the subheading to be singular.
-
-Some of our data is of penguins (\textbf{?@fig-bills}),
-
-Talk more about it.
-
-And also planes (\textbf{?@fig-planes}). (You can change the height and
-width, but don't worry about doing that until you have finished every
-other aspect of the paper - Quarto will try to make it look nice and the
-defaults usually work well once you have enough text.)
-
-Talk way more about it.
+The outcome variable of interest for this research is the percentage,
+representing the level of public support for Donald Trump. The
+distribution in Figure~\ref{fig-pct} indicates that most observations
+cluster around a support percentage of approximately 48\%, suggesting
+moderate backing from the electorate. Additionally, a smaller proportion
+of polls show support exceeding 55\%, indicating that while Trump has a
+core base, many voters remain either indifferent or opposed to him.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-pct-1.pdf}
+
+}
+
+\caption{\label{fig-pct}Distribution of Support (percent) for Donald
+Trump}
+
+\end{figure}%
 
@@
 
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine
-a few into one if they go together naturally.
+\subsubsection{Numeric Grade}\label{numeric-grade}
+
+The numeric grade reflects the quality of the pollster, with
+FiveThirtyEight defining a scale from 0 to 3. A grade of 0 indicates a
+low-quality poll, while a grade of 3 signifies a high-quality pollster.
+After filtering for pollsters with a numeric grade higher than 2.5, we
+identified a total of 30 distinct pollsters, with half of them scoring
+between 2.6 and 2.8, as shown in Figure~\ref{fig-numeric-grade} .
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-numeric-grade-1.pdf}
+
+}
+
+\caption{\label{fig-numeric-grade}Distribution of Numeric Grades (2.6 to
+3.0)}
+
+\end{figure}%
+
+\subsubsection{Sample Size}\label{sample-size}
+
+The sample size indicates the number of respondents in each poll. The
+distribution in Figure~\ref{fig-sample-size} exhibits a right-skewed
+shape, suggesting that there are more observations with smaller sample
+sizes compared to larger ones. The peak of the distribution is around
+1,000, indicating that this is the most common sample size used in the
+polls. Overall, the sample size data highlights that each poll contains
+a sufficient number of respondents to provide reliable insights.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-sample-size-1.pdf}
+
+}
+
+\caption{\label{fig-sample-size}Distribution of Sample Size}
+
+\end{figure}%
+
+\subsubsection{Transparency Score}\label{transparency-score}
+
+The Transparency Score measures how transparent a pollster is,
+calculated based on the amount of information disclosed about its polls,
+weighted by recency. The highest possible score is 10, while the lowest
+is 0. The distribution of Transparency Scores for the filtered pollsters
+shows a peak around 9 as presented in
+Figure~\ref{fig-transparency-score}, indicating that this is the most
+common score. This suggests that among the selected pollsters, there is
+a predominance of high transparency scores.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-transparency-score-1.pdf}
+
+}
+
+\caption{\label{fig-transparency-score}Distribution of Transparency
+Score}
+
+\end{figure}%
+
+\subsubsection{end date}\label{end-date}
+
+The end date indicates when each poll concluded.
+Figure~\ref{fig-end-date} shows that as the final result of the U.S.
+election approached, more polls were conducted and completed. This trend
+reflects an increased interest in capturing public opinion and
+predicting electoral outcomes as election day neared, emphasizing the
+significance of real-time sentiment analysis during this critical
+period.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{paper_files/figure-pdf/fig-end-date-1.pdf}
+
+}
+
+\caption{\label{fig-end-date}Distribution of End Dates}
+
+\end{figure}%
 
@@
 To model Donald Trump's polling percentages over time, we employed a
-Bayesian linear regression framework. Bayesian methods provide a
-flexible approach to inference by incorporating prior beliefs and
-updating them with observed data, allowing us to quantify uncertainty in
-both parameter estimates and predictions.
-
-Here we briefly describe the Bayesian model used to investigate the
-winning probability of Trump. Background details and diagnostics are
-included in Appendix~\ref{sec-model-details}.
+multiple linear regression framework. This approach estimates the
+relationship between polling percentages and various predictors by
+fitting a linear equation to the data. By analyzing the coefficients, we
+can quantify the impact of each predictor on Trump's polling
+percentages, while also assessing the overall fit of the model and
+making predictions based on the observed trends.
+
+Here we briefly describe the multiple linear regression model used to
+investigate the winning probability of Trump. Background details and
+diagnostics are included in Appendix~\ref{sec-model-details}.
 
@@
 
-The model takes the form: The model takes the form:
-
-\section{\#Interpretation of
+The model takes the form:
+
+\begin{align}
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
+             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
+\epsilon_i &\sim \text{Normal}(0, \sigma^2)
+\end{align}
+
+Where: \begin{align}
+\beta_0 & \text{ is the intercept term} \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
+\sigma^2 & \text{ is the variance of the error term}
+\end{align}
+
+\section{Interpretation of
 Coefficients:}\label{interpretation-of-coefficients}
@@
 The posterior distributions of the parameters allow us to quantify the
-uncertainty around each effect: - The coefficient for end\_date informs
-us about how Trump's polling percentages have evolved over time. A
-positive coefficient would suggest an upward trend, while a negative
-coefficient would indicate a decline. - The coefficient for
-numeric\_grade captures the impact of pollster quality on the polling
-percentage. High-quality pollsters may produce different estimates
-compared to lower-quality ones. - The state-level effects account for
-regional differences in Trump's support. Some states may show
-significantly higher or lower levels of support, even after adjusting
-for the time of the poll and pollster quality.
+uncertainty around each effect:\\
+
+\begin{itemize}
+\tightlist
+\item
+  The coefficient for end\_date informs us about how Trump's polling
+  percentages have evolved over time. A positive coefficient would
+  suggest an upward trend, while a negative coefficient would indicate a
+  decline.\\
+\item
+  The coefficient for numeric\_grade captures the impact of pollster
+  quality on the polling percentage. High-quality pollsters may produce
+  different estimates compared to lower-quality ones.\\
+\item
+  The state-level effects account for regional differences in Trump's
+  support. Some states may show significantly higher or lower levels of
+  support, even after adjusting for the time of the poll and pollster
+  quality.
+\end{itemize}
 
@@
 
-\includegraphics{paper_files/figure-pdf/fig-diagnosis-1.pdf}
+\includegraphics{paper_files/figure-pdf/fig-diagnosis-1-1.pdf}
 
@@
 
-\caption{\label{fig-diagnosis}}
+\caption{\label{fig-diagnosis-1}}
 
 \end{figure}%
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(car)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-Loading required package: carData
-\end{verbatim}
-
-\begin{verbatim}
-
-Attaching package: 'car'
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:dplyr':
-
-    recode
-\end{verbatim}
-
-\begin{verbatim}
-The following object is masked from 'package:purrr':
-
-    some
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{vif}\NormalTok{(regression\_model)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-                       GVIF Df GVIF^(1/(2*Df))
-numeric_grade      1.294110  1        1.137590
-sample_size        1.289750  1        1.135672
-state              2.082151 44        1.008369
-transparency_score 1.263558  1        1.124081
-end_date           1.309491  1        1.144330
-\end{verbatim}
 
@@
 
-\section{Appendix B: Idealized Methodology and
-Survey}\label{appendix-b-idealized-methodology-and-survey}
+\textless\textless\textless\textless\textless\textless\textless{}
+Updated upstream \# Appendix B: Idealized Methodology and Survey
 
@@
 
+\section{\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{}
+7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4}\label{bdf4d96b1910dc96b7cd995f3c7eccd50b162f4}
+
+\section{Idealized Methodology and
+Survey}\label{idealized-methodology-and-survey}
+
 \begin{quote}
@@
 \begin{quote}
-7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4
+Stashed changes
 \end{quote}
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-tellingstories}
-Alexander, Rohan. 2023. \emph{Telling Stories with Data}. Chapman;
-Hall/CRC. \url{https://tellingstorieswithdata.com/}.
-
 \bibitem[\citeproctext]{ref-citeR}

### 2024-10-24 paper/paper.qmd
Update model result part.

--- 2024-10-23 paper/paper.qmd
@@
 
-# Join electoral vote data with Trump's predictions
+# Combine electoral vote data with Trump's predictions
 state_predictions <- merge(total_trump, electoral_votes, by = "state")
@@
 
+# Calculate the electoral votes for each candidate
+state_predictions$trump_electoral_votes <- ifelse(state_predictions$winner == "Trump", state_predictions$electoral_votes, 0)
+state_predictions$harris_electoral_votes <- ifelse(state_predictions$winner == "Harris", state_predictions$electoral_votes, 0)
+
+# Summarize total electoral votes for each candidate
+trump_electoral_votes <- sum(state_predictions$trump_electoral_votes)
+harris_electoral_votes <- sum(state_predictions$harris_electoral_votes)
+
 # Create a table showing the prediction results
 library(knitr)
-kable(state_predictions, col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),
-      digits = 2, caption = "Prediction for Trump by State")
+
+# Create the table using kable
+kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
+      col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
+      digits = 2, 
+      caption = "Prediction for Trump by State")
+
+# Print the results for the total electoral votes
+print(paste("Trump Electoral Votes:", trump_electoral_votes))
+print(paste("Harris Electoral Votes:", harris_electoral_votes))
+```
+
+```{r}
+summary(regression_model)
 ```

### 2024-10-24 paper/paper.qmd
Update Result and Discussion parts; Modify Appendix B

@@
 
-Some of our data is of penguins (@fig-bills),
+Some of our data is of penguins (fig-bills),
 
@@
 
-And also planes (@fig-planes).
+And also planes (fig-planes).
 (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
@@
 
-Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].
+Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix @sec-model-details].
 
@@
 
-# #Interpretation of Coefficients:
+## Interpretation of Coefficients:
 
@@
 
-### Model justification
+```{r}
+summary(regression_model)
+```
+
+## Model justification
 
@@
 
+\newpage
+
 # Results
 
-## Predict and Combine with Electroal College to Predict
+## Predicted Electoral Outcomes
+We applied a regression model to predict the percentage of votes Trump is expected to receive in each state.
+The model results, combined with each state's electoral vote allocation, allowed us to predict the winner in each state.
+Based on this, we calculated the total number of electoral votes for both Trump and Harris.
+
+The table below (@tbl-prediction) summarizes the predicted results, showing Trump’s predicted percentage, the number of electoral votes in each state, and the predicted winner (either Trump or Harris).
+For instance:
+- Alabama: Trump is predicted to win 53% of the vote, securing all 9 electoral votes.
+- California: Trump is predicted to receive 34.39% of the vote, resulting in a victory for Harris, who takes California's 55 electoral votes.
+- Florida: The model predicts a close race, with Trump at 48.89% of the vote, resulting in a Harris win in this critical battleground state.
+
+Electoral Vote Count:
+- Trump Electoral Votes: 78
+- Harris Electoral Votes: 416
+These results indicate that based on the current model predictions, Harris is expected to win the 2024 U.S.
+Presidential Election, securing 416 electoral votes, compared to Trump’s 78 electoral votes.
+The election outcome hinges on several battleground states, where the vote margins are predicted to be narrow.
 
@@
 
-```{r}
-summary(regression_model)
+## Predicted Electoral Outcomes by State
+The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S. Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
+```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
+#| echno: false
+#| label: fig-statemap
+#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
+#| echo: false
+#| warning: false
+#| message: false
+#| 
+# Load necessary libraries
+library(usmap)
+
+# "red" for Trump and "blue" for Harris
+state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "red", "blue")
+
+# Create a map visualization showing the predicted winner by state
+plot_usmap(data = state_predictions, values = "winner_color", regions = "states") +
+  scale_fill_manual(values = c("red" = "red", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
+  labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
+  theme(legend.position = "right")
+
 ```
+The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois.
+However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
 
-# Discussion
+# Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## What Is Done in This Paper?
+This paper uses a regression model to predict the outcome of the 2024 U.S.
+Presidential Election between Donald Trump and Kamala Harris.
+By analyzing historical voting data, the model forecasts the percentage of votes Trump is expected to receive in each state.
+These predictions are combined with the state's electoral vote allocation to determine the overall winner.
+The findings indicate a significant electoral victory for Harris, projecting 416 electoral votes for her compared to 78 for Trump.
+A geographic map is also presented to visualize state-level outcomes and highlight regional voting trends.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## What Do We Learn About the World?
+The study highlights the persistence of geographic voting patterns in U.S.
+elections.
+Even with changes in candidates, many states follow their historical voting tendencies.
+Republican-leaning states like Alabama and Wyoming are projected to support Trump, while Democratic-leaning states such as California and New York favor Harris.
+This pattern shows the strong influence of regional political loyalties, which continue to shape election outcomes.
 
-## Second discussion point
+## Another Thing We Learn About the World
+The analysis underscores the importance of battleground states in determining the election's outcome.
+States like Florida and Arizona, predicted to lean toward Harris, play a decisive role in the projected electoral victory.
+This illustrates how close contests in a few states can influence the overall election result, emphasizing the significant impact these states have in shaping the presidency.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+## Weaknesses of What Was Done
+While the model offers a useful prediction, it has limitations.
+It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election.
+The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts.
+Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape.
 
-## Third discussion point
+## What Is Left to Learn or How Should We Proceed in the Future?
+Future research should incorporate more detailed data, including demographic shifts and economic factors that may influence voter preferences.
+It would be valuable to examine how emerging political movements and changes in communication strategies affect elections, particularly in closely contested states.
+Post-election analysis comparing predictions with actual results will also be essential to improving the accuracy of models and understanding how unforeseen events may alter outcomes.
 
 ## Weaknesses and next steps
+The logistic regression model is limited by the lack of interaction terms between states, which may obscure regional trends or external factors that influence neighboring states.
+Additionally, the model assumes that polling data accurately reflects voter intentions, but biases or missing data in key regions could affect the predictions.
 
-Weaknesses and next steps should also be included.
+Future iterations of this model should incorporate voter turnout predictions, demographic variables, and real-time polling updates to better capture the dynamics of voter behavior.
+Including social media sentiment analysis and analyzing cross-state interactions could refine the prediction model, offering more nuanced insights into election forecasts.
 
@@
 
-## **Objective and Overview**
+## Objective and Overview
 The goal of this survey methodology is to accurately forecast the outcome of the U.S.
 presidential election by collecting high-quality, representative data from a diverse set of respondents across the country.
-With a budget of $100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols.
+With a budget of \$100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols.
 The approach is designed to maximize accuracy, reduce bias, and account for various demographic, geographic, and political factors that influence voting behavior.
 
-### **Core Objectives**:
-1. Obtain a representative sample of the U.S. electorate.
-2. Ensure data quality through rigorous validation.
-3. Leverage statistical modeling and poll aggregation for an accurate prediction.
+## Core Objectives
+* Obtain a representative sample of the U.S. electorate.
+* Ensure data quality through rigorous validation.
+* Leverage statistical modeling and poll aggregation for an accurate prediction.
 
-## **1. Sampling Strategy**
-
+## Sampling Strategy
 The sampling strategy is designed to ensure that the survey reaches a broad, representative section of the voting population.
@@
 
-### **Stratification Variables**:
-- **Age Groups**: 18-29, 30-44, 45-64, 65+  
-- **Gender**: Male, Female, Non-binary/Other  
-- **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other  
-- **Education Level**: No high school, High school graduate, College graduate, Post-graduate  
-- **Income Bracket**: <$30,000, $30,000-$60,000, $60,000-$100,000, >$100,000  
-- **Geographic Region**: Northeast, Midwest, South, West
+### Stratification Variables
+* **Age Groups**: 18-29, 30-44, 45-64, 65+ 
+* **Gender**: Male, Female, Non-binary/Other 
+* **Race/Ethnicity**: White, Black, Hispanic/Latino, Asian, Indigenous, Other 
+* **Education Level**: No high school, High school graduate, College graduate, Post-graduate 
+* **Income Bracket**: <$30,000, \$30,000-\$60,000, \$60,000-\$100,000, >\$100,000 
+* **Geographic Region**: Northeast, Midwest, South, West
 
-**Sample Size**:  
-A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1% at a 95% confidence level.
+### Sample Size
+A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1\% at a 95\% confidence level.
 This sample size will allow for detailed subgroup analysis (e.g., by state, demographic group), yielding statistically robust predictions.
 
-**Weighting**:  
-We will apply post-stratification weights to adjust for any oversampling or undersampling of specific demographic groups.
+### Weighting
+Post-stratification weights will be applied to adjust for any oversampling or undersampling of specific demographic groups.
 For example, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.
 
-## **2. Recruitment Strategy**
-
-### **Recruitment Channels**:
+## Recruitment Strategy
 To maximize respondent diversity and ensure accurate sampling, the survey will employ **multi-channel recruitment**:
 
-- **Digital Advertisements**: Targeted ads on platforms like Facebook, Instagram, and Google will be used to recruit respondents based on their demographic profiles (age, gender, location, political interest).
-Custom audience features will be utilized to reach specific demographic and geographic groups.
-- **Email Outreach**: If permissible, we will access voter registration databases and send email invitations to registered voters.
-This will allow us to target specific voter demographics that are harder to reach via digital ads.
-- **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities (e.g., minority voter outreach programs) will further boost respondent diversity.
-- **Incentives**: To increase response rates, each participant will be entered into a lottery with a chance to win a $100 gift card, encouraging broader participation.
+* **Digital Advertisements**: Targeted ads on platforms like Facebook, Instagram, and Google will recruit respondents based on their demographic profiles (age, gender, location, political interest).
+* **Email Outreach**: If permissible, voter registration databases will be accessed to send email invitations to registered voters.
+* **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities will further boost respondent diversity.
+* **Incentives**: Each participant will be entered into a lottery with a chance to win a \$100 gift card to encourage participation.
 
-## **3. Data Validation and Quality Assurance**
+## Data Validation and Quality Assurance
+Maintaining data integrity and ensuring high-quality responses are critical to the accuracy of the election forecast.
+Several measures will be put in place to validate responses and reduce noise in the dataset.
 
-Maintaining data integrity and ensuring high-quality responses are critical to the accuracy of the election forecast.
-Therefore, several measures will be put in place to validate responses and reduce noise in the dataset.
+### Data Validation Protocols
+* **Real-time Captcha Verification**: This will prevent automated bots from submitting responses.
+* **Email/Phone Verification**: Respondents will verify their email or phone number to ensure authenticity and prevent duplicate submissions.
+* **Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question. Responses completed suspiciously quickly will be flagged for review.
+* **Voter Registration Cross-Check**: If feasible, respondents will be cross-referenced with voter registration records to ensure eligibility.
+* **Response Audits**: Randomly selected respondents will be contacted to verify the accuracy of their responses, ensuring dataset integrity.
 
-### **Data Validation Protocols**:
-1. **Real-time Captcha Verification**: This will prevent automated bots from submitting responses.
-2. **Email/Phone Verification**: Respondents will verify their email or phone number to ensure authenticity. This ensures that each respondent only participates once.
-3.
-**Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question.
-Responses completed suspiciously quickly (e.g., below 30% of the average completion time) will be flagged for review or exclusion.
-4. **Voter Registration Cross-Check**: If feasible, respondents will be cross-referenced with voter registration records to ensure they are eligible to vote in the upcoming election.
-5. **Response Audits**: Randomly selected respondents will be contacted to verify the accuracy of their responses, ensuring integrity in the dataset.
+## Poll Aggregation and Data Analysis
+### Poll Aggregation
+This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach.
 
-## **4. Poll Aggregation and Data Analysis**
+* **Weighting by Methodology and Recency**: Poll results will be weighted based on the rigor of their methodology and the recency of the poll.
+* **Handling Bias and Variability**: Aggregated results will adjust for pollster biases and variability between polls to ensure that no single poll dominates the prediction.
 
-### **Poll Aggregation**:
-This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen our forecast through a **poll-of-polls** approach.
+### Modeling Approach
+**Bayesian hierarchical models** will account for variability across different states, demographics, and regions.
+This will allow for modeling the popular vote and potentially translating it into **Electoral College predictions**.
 
-- **Weighting by Methodology and Recency**: Poll results will be weighted based on the rigor of their methodology (e.g., online vs.
-phone surveys, sample size) and the recency of the poll.
-Recent, methodologically sound polls will receive more weight in the aggregation process.
-- **Handling Bias and Variability**: Aggregated results will adjust for pollster house effects (biases in methodology) and variability between polls, ensuring that no single poll dominates the prediction.
-
-### **Modeling Approach**:
-We will implement **Bayesian hierarchical models** to account for variability across different states, demographics, and regions.
-This will allow us to model the popular vote and potentially translate it into **Electoral College predictions**.
-
-## **5. Budget Allocation**
-
-- **Respondent Recruitment (Targeted ads, outreach)**: $70,000  
-- **Incentives (e.g., lottery prizes)**: $10,000  
-- **Survey Platform (Google Forms, Qualtrics subscription)**: $5,000  
-- **Data Validation Tools**: $5,000  
-- **Poll Aggregation & Analysis Software**: $10,000
+## Budget Allocation
+* **Respondent Recruitment (Targeted ads, outreach)**: \$70,000
+* **Incentives (e.g., lottery prizes)**: \$10,000
+* **Survey Platform (Google Forms, Qualtrics subscription)**: \$5,000
+* **Data Validation Tools**: \$5,000
+* **Poll Aggregation \& Analysis Software**: \$10,000
 
@@
 
-## **6. Survey Implementation**
-
+## Survey Implementation
 The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection.
-The link to the live survey can be found here: [Google Form Survey](https://forms.gle/RC1464SvLvtoAYdv6).
-A copy of the questions is provided below.
+You can access the survey at the following link: [Google Form Survey](https://forms.gle/XxtMTMc45d6VzNuy8)
 
@@
 
-1. **Introduction**:
+\begingroup
+\small
+**Introduction**:
+
 Thank you for taking part in this survey aimed at predicting the outcome of the 2024 US Presidential election. Your insights are valuable to our research.
@@
 Please note:
+
 - **All responses will be kept strictly confidential.**
@@
 - **The survey is estimated to take approximately 10 minutes to complete.**
-If you have any inquiries or concerns regarding this survey, please don't hesitate to contact the research team at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca).
+
+If you have any inquiries or concerns regarding this survey, please don't hesitate to contact the research team at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca).(Yuxuan Wei, Xuanle Zhou, Yongqi Liu)
 
@@
 
-2. **Section 1: Eligibility Screening**:
+**Section 1: Eligibility Screening**:
+
 Are you a U.S. citizen?
@@
 
-3. **Section 2: Demographic Information**:
+**Section 2: Demographic Information**:
+
 What is your age group?
@@
 
-4. **Section 3: Political Views and Voting Intentions**:
+**Section 3: Political Views and Voting Intentions**:
+
 How likely are you to vote in the 2024 Presidential election?
@@
 
-5. **Section 4: Information Sources and Engagement**:
+**Section 4: Information Sources and Engagement**:
 
@@
 
-6. **Section 5: Validation and Consent**:
+**Section 5: Validation and Consent**:
+
 Please verify that you are a human by selecting "Blue" from the following options:
@@
 
-7. **End Message**:
+**End Message**:
+
 "Thank you for completing this survey. Your response has been recorded.
-If you have any questions about this survey or would like to be informed about the results, please contact [Your Contact Information]."
+If you have any questions about this survey or would like to be informed about the results, please contact at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca)."
+
+\endgroup
 
@@
 
-### **7. Survey Design Considerations**
-
-- **Question Wording**: All questions are carefully designed to avoid bias or leading responses.
-- **Neutrality**: Political questions are framed neutrally to avoid pushing respondents toward specific answers.
-- **Pilot Testing**: Before full deployment, the survey will undergo a pilot test to identify and resolve any issues.
-
----
-
-This methodology, combining rigorous sampling, data validation, and aggregation, ensures that the election forecast is as accurate and representative as possible.
-
->>>>>>> 7bdf4d96b1910dc96b7cd995f3c7eccd50b162f4
+## Survey Design Considerations
+* **Question Wording**: All questions are designed to avoid bias or leading responses.
+* **Neutrality**: Political questions are framed neutrally to avoid influencing respondents' answers.
+* **Pilot Testing**: The survey will undergo a pilot test to identify and resolve any issues before full deployment.
 

### 2024-10-24 paper/paper.qmd
Add Result and Discussion parts; Modify Appendix B

@@
 author: 
-  - First author
+  - Xuanle Zhou
   - Yongqi Liu
@@
 ```{r}
+#| include: false
+#| warning: false
+#| message: false
+
 #install.packages("tidymodels")
+
 library(tidyverse)
 library(ggplot2)
+library(rstanarm)
+library(knitr)
+
 analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
@@
 
-We use the statistical programming language R [@citeR].... Following @tellingstories, we consider...
+This study uses R packages [@citeR] to clean and analyz the dataset , including libraries from tidyverse [], ggplot2[].
 
-Overview text
+After cleaning the data, which included grouping and removing missing values, the analysis dataset consists of 1,683 observations, focusing on the following 11 variables: pollster name, methodology, numeric grade, start date, end date, sample size, candidate name, percentage, transparency score, and population group.
 
-## Measurement
+## Data Measurement and Considerations
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The dataset for this analysis is sourced from FiveThirtyEight, which rigorously collects and aggregates polling data from a variety of firms to reflect public opinion.
+To ensure the integrity of the data, only polls that adhere to specific criteria are included in the dataset.
+Each poll must provide essential information, such as the pollster’s name, survey dates, sample sizes, and methodological details (e.g., polling medium, voter files, weighting criteria).
+Polls that are deemed nonscientific, that blend data from multiple sources, or that are conducted by hobbyists are excluded.
+
+Once a poll meets these stringent standards, it is incorporated into the database, enabling it to inform polling averages, forecasts, and political coverage.
+This careful selection process ensures that the dataset accurately captures and reflects the nuances of public sentiment and behavior.
 
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (fig-bills),
+The outcome variable of interest for this research is the percentage, representing the level of public support for Donald Trump.
+The distribution in @fig-pct indicates that most observations cluster around a support percentage of approximately 48%, suggesting moderate backing from the electorate.
+Additionally, a smaller proportion of polls show support exceeding 55%, indicating that while Trump has a core base, many voters remain either indifferent or opposed to him.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-pct
+#| fig-cap: Distribution of Support (percent) for Donald Trump
 #| echo: false
-
+#| warning: false
+#| message: false
+ggplot(analysis_data, aes(x = percent)) +
+  geom_histogram(binwidth = 2, fill = "green", color = "black", alpha = 0.7) +
+  labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
+  theme_minimal()
 ```
 
-Talk more about it.
+## Predictor variables
 
-And also planes (fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+### Numeric Grade
+
+The numeric grade reflects the quality of the pollster, with FiveThirtyEight defining a scale from 0 to 3.
+A grade of 0 indicates a low-quality poll, while a grade of 3 signifies a high-quality pollster.
+After filtering for pollsters with a numeric grade higher than 2.5, we identified a total of 30 distinct pollsters, with half of them scoring between 2.6 and 2.8, as shown in @fig-numeric-grade .
 
 ```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+#| label: fig-numeric-grade
+#| fig-cap: Distribution of Numeric Grades (2.6 to 3.0)
 #| echo: false
@@
 
+summary_data <- analysis_data %>%
+    distinct(pollster_rating_name, .keep_all = TRUE) %>%
+    group_by(numeric_grade) %>%
+    summarise(count = n())
+
+ggplot(analysis_data %>% distinct(pollster_rating_name, .keep_all = TRUE), 
+       aes(x = numeric_grade)) + 
+    geom_histogram(binwidth = 0.1, fill = "green", color = "black", alpha = 0.7) + 
+    scale_x_continuous(breaks = seq(2.5, 3.0, by = 0.1)) + 
+    scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) + 
+    labs(title = "Distribution of Numeric Grades (2.6 to 3.0)", 
+         x = "Numeric Grade", 
+         y = "Count of Distinct Polls") + 
+    theme_minimal()
+```
+### Sample Size
+
+The sample size indicates the number of respondents in each poll.
+The distribution in @fig-sample-size exhibits a right-skewed shape, suggesting that there are more observations with smaller sample sizes compared to larger ones.
+The peak of the distribution is around 1,000, indicating that this is the most common sample size used in the polls.
+Overall, the sample size data highlights that each poll contains a sufficient number of respondents to provide reliable insights.
+
+```{r}
+#| label: fig-sample-size
+#| fig-cap: Distribution of Sample Size
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(analysis_data %>% filter(sample_size < 3000), aes(x = sample_size)) +
+  geom_histogram(binwidth = 100, fill = "green", color = "black", alpha = 0.7) +
+  labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
+  theme_minimal()
+```
+### Transparency Score
+
+The Transparency Score measures how transparent a pollster is, calculated based on the amount of information disclosed about its polls, weighted by recency.
+The highest possible score is 10, while the lowest is 0.
+The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that this is the most common score.
+This suggests that among the selected pollsters, there is a predominance of high transparency scores.
+
+```{r}
+#| label: fig-transparency-score
+#| fig-cap: Distribution of Transparency Score
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(analysis_data %>% 
+         distinct(pollster_rating_name, .keep_all = TRUE), 
+       aes(x = transparency_score)) + 
+  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.7) + 
+  scale_x_continuous(breaks = 3:10) +
+  scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) +  
+  labs(title = "Distribution of Transparency Score", x = "Transparency Score", y = "Count of Distinct Polls") + 
+  theme_minimal()
 ```
 
-Talk way more about it.
+### end date
 
-## Predictor variables
+The end date indicates when each poll concluded.
+@fig-end-date shows that as the final result of the U.S.
+election approached, more polls were conducted and completed.
+This trend reflects an increased interest in capturing public opinion and predicting electoral outcomes as election day neared, emphasizing the significance of real-time sentiment analysis during this critical period.
 
-Add graphs, tables and text.
+```{r}
+#| label: fig-end-date
+#| fig-cap: Distribution of End Dates
+#| echo: false
+#| warning: false
+#| message: false
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+ggplot(analysis_data, aes(x = as.Date(end_date))) + 
+  geom_line(stat = "count", color = "black", size = 1) + 
+  labs(title = "Distribution of End Dates", x = "End Date", y = "Count") + 
+  theme_minimal()
+```
 
@@
 
-To model Donald Trump’s polling percentages over time, we employed a Bayesian linear regression framework.
-Bayesian methods provide a flexible approach to inference by incorporating prior beliefs and updating them with observed data, allowing us to quantify uncertainty in both parameter estimates and predictions.
+To model Donald Trump’s polling percentages over time, we employed a multiple linear regression framework.
+This approach estimates the relationship between polling percentages and various predictors by fitting a linear equation to the data.
+By analyzing the coefficients, we can quantify the impact of each predictor on Trump’s polling percentages, while also assessing the overall fit of the model and making predictions based on the observed trends.
 
-Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix @sec-model-details].
+Here we briefly describe the multiple linear regression model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].
 
@@
 The model takes the form:
-The model takes the form:
 
-## Interpretation of Coefficients:
+\begin{align}
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
+             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
+\epsilon_i &\sim \text{Normal}(0, \sigma^2)
+\end{align}
+
+Where: 
+\begin{align}
+\beta_0 & \text{ is the intercept term} \\
+\beta_1, \beta_2, \beta_3, \beta_4, \beta_5 & \text{ are the coefficients for each predictor} \\
+\sigma^2 & \text{ is the variance of the error term}
+\end{align}
+
+# Interpretation of Coefficients:
 
@@
 ## Interpretation
-The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:
-- The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
-A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.
-- The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.
-- The state-level effects account for regional differences in Trump’s support.
+
+The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\
+
+* The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
+A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.\
+* The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
+* The state-level effects account for regional differences in Trump’s support.
 Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.
@@
 #| echno: false
-#| label: fig-diagnosis
+#| label: fig-diagnosis-1
 #| tbl-cap: Linear Regression Assumptions hold.
@@
 ```{r}
-library(car)
-vif(regression_model)
+#| echno: false
+#| label: fig-diagnosis-2
+#| tbl-cap: Linear Regression Assumptions hold.
+#| echo: false
+#| warning: false
+#| message: false
+
+#library(car)
+#vif(regression_model)
 ```
 
-```{r}
-summary(regression_model)
-```
-
-## Model justification
+### Model justification
 

### 2024-10-24 paper/paper.qmd
Update typos.

@@
   - Yuxuan Wei
-thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
+thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git."
 date: today
 date-format: long
+toc: true
 abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
@@
 #install.packages("tidymodels")
-
+#install.packages("usmap")
 library(tidyverse)
@@
 library(knitr)
+library(usmap)
 
@@
 
-### end date
+### End Date
 
@@
 
-# Interpretation of Coefficients:
+## Interpretation of Coefficients
 
-- Intercept (\beta_0): This is the predicted Trump polling percentage when all predictors (numeric grade, sample size, state, transparency score, and end date) are at their baseline or zero value.
-- Numeric Grade (\beta_1): This coefficient measures how much Trump’s polling percentage changes as the pollster’s numeric grade increases.
+- Intercept ($\beta_0$): This is the predicted Trump polling percentage when all predictors (numeric grade, sample size, state, transparency score, and end date) are at their baseline or zero value.
+- Numeric Grade ($\beta_1$): This coefficient measures how much Trump’s polling percentage changes as the pollster’s numeric grade increases.
 A positive and significant coefficient would indicate that higher-rated pollsters report better polling numbers for Trump, while a negative coefficient would suggest the opposite.
-- Sample Size (\beta_2): This measures the impact of the number of respondents on Trump’s polling percentage.
+- Sample Size ($\beta_2$): This measures the impact of the number of respondents on Trump’s polling percentage.
 A positive coefficient would indicate that larger sample sizes are associated with higher polling percentages for Trump.
-- State (\beta_3): The coefficients for the state variable represent differences in Trump’s polling percentage in each state compared to the reference state (baseline category).
+- State ($\beta_3$): The coefficients for the state variable represent differences in Trump’s polling percentage in each state compared to the reference state (baseline category).
 For example, if the coefficient for Florida is negative, it means Trump polls lower in Florida compared to the reference state.
-- Transparency Score (\beta_4): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll.
+- Transparency Score ($\beta_4$): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll.
 A positive coefficient would indicate that polls with higher transparency tend to report higher polling percentages for Trump, whereas a negative coefficient would imply the opposite.
-- End Date (\beta_5): The end date is a time-related variable, capturing trends over time.
+- End Date ($\beta_5$): The end date is a time-related variable, capturing trends over time.
 A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.
@@
 The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\
-
 * The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
@@
 
-# Model Evalutation
-- R-squared
+## Model Justification
 @tbl-summary shows the summary table for the model. And then evaluate it on the test set. It appears as though the model is having difficulty identifying Trump supporters.
@@
 #| label: tbl-summary
-#| tbl-cap: Relationship between wing length and width
+#| tbl-cap: Regression Model Estimate Summary
 #| echo: false
@@
 
-library(knitr)
 regression_model<-readRDS(here::here("models/regression_model.rds"))
 summary<-summary(regression_model)
-# Extract the coefficients (which can be formatted as a table)
+
+# Extract the coefficients to form a table
 coefficients_table <- summary$coefficients
 
-# Display the coefficients table using kable
-kable(coefficients_table, digits = 3, caption = "Regression Model Coefficients")
+# Display the first 10 rows of the coefficients table using kable, formatted to 4 decimal places
+kable(head(coefficients_table, 10), digits = 4)
 ```
 
-# Diagnostic plots for the model
+### VIF Evaluation
+@tbl-vif displays that
+
 ```{r}
 #| echno: false
-#| label: fig-diagnosis-1
-#| tbl-cap: Linear Regression Assumptions hold.
+#| label: tbl-vif
+#| tbl-cap: VIF shows a reasonable output.
 #| echo: false
@@
 
-par(mfrow = c(2, 2))  
-plot(regression_model)
+library(car)
+kable(vif(regression_model))
 ```
-
-```{r}
-#| echno: false
-#| label: fig-diagnosis-2
-#| tbl-cap: Linear Regression Assumptions hold.
-#| echo: false
-#| warning: false
-#| message: false
-
-#library(car)
-#vif(regression_model)
-```
-
-### Model justification
 
@@
 
-```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
+```{r tbl-prediction}
 #| echno: false
 #| label: tbl-prediction
-#| tbl-cap: Prediction for Trump
+#| tbl-cap: Prediction for Trump and Harris by Electoral College
 #| echo: false
@@
       col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
-      digits = 2, 
-      caption = "Prediction for Trump by State")
+      digits = 2)
 
@@
 The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S. Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
-```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
+
+```{r tbl-prediction}
 #| echno: false
@@
 #| message: false
-#| 
-# Load necessary libraries
-library(usmap)
 
@@
 
-## Weaknesses of What Was Done
-While the model offers a useful prediction, it has limitations.
-It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election.
-The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts.
-Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape.
-
 ## What Is Left to Learn or How Should We Proceed in the Future?
@@
 
-## Weaknesses and next steps
+## Weaknesses and Next Steps
+While the model offers a useful prediction, it has limitations.
+It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election.
+The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts.
+Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape.
 The logistic regression model is limited by the lack of interaction terms between states, which may obscure regional trends or external factors that influence neighboring states.
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
-
-## Posterior predictive check
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-```
 
@@
 ```{r}
+#| echno: false
+#| label: fig-diagnosis-1
+#| tbl-cap: Linear Regression Assumptions hold
 #| echo: false
-#| eval: true
+#| warning: false
 #| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-library(caret)
-library(rstanarm)
-library(ggplot2)
-library(dplyr)
-# Split the data into training (70%) and test (30%) sets
-set.seed(853)  # For reproducibility
+
+par(mfrow = c(2, 2))  
+plot(regression_model)
 
 ```
+
+## Multicolinearity Check
 
@@
 @citeR
+Thanks to Open AI and ChatGPT 4.0 is used to write the analysis of the paper.
 

### 2024-10-24 paper/paper.qmd
Update LLM usage.
Renew the data to the October 24, 2024.

@@
             "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
-            "Maine CD-1", "Maine CD-2", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
-            "Missouri", "Montana", "Nebraska", "Nebraska CD-1", "Nebraska CD-2", "Nebraska CD-3", "Nevada", 
+            "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
+            "Missouri", "Montana", "Nebraska", "Nevada", 
             "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
@@
             "District of Columbia"),
-  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 2, 1, 1, 10, 11, 15, 10, 6, 10, 
-                      3, 5, 1, 1, 2, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
+  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
+                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
 )
@@
 @citeR
-Thanks to Open AI and ChatGPT 4.0 is used to write the analysis of the paper.
+Thanks to Open AI [@openai2024chatgpt] and ChatGPT 4.0 is used to write the analysis of the paper.
 

### 2024-10-24 paper/paper.qmd
Add title and subtitle for the paper

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Predicting Kamala Harris's Victory in the 2024 US Election"
+subtitle: "An Investigation into Poll Data Using Multiple Linear Regression"
 author: 

### 2024-10-24 paper/paper.qmd
Update Abstract

--- 2024-10-24 paper/paper.qmd
@@
 toc: true
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study predicts the outcome of the 2024 U.S.
+presidential election using multiple regression analysis based on state-by-state electoral votes.
+The predictive model offers prediction that can inform campaign strategies and shape public discourse.
+Results suggest a strong likelihood of Kamala Harris securing victory in the 2024 election cycle."
 format: pdf

### 2024-10-25 scripts/03-clean_data.R
Split the analysis data into test and train.

@@ -8,7 +8,7 @@
 # Any other information needed? NA
 
 #### Workspace setup ####
-install.packages("arrow")
+#install.packages("arrow")
 library(tidyverse)
 library(dplyr)
 library(arrow)
@@ -23,12 +23,13 @@ cleaned_data <- raw_data %>% filter(numeric_grade > 2.5)
 cleaned_data$mdy <- mdy(cleaned_data$end_date)
 
 # Define the cutoff date (July 21, 2024)
-cutoff_date <- as.Date("2024-07-21")
+cutoff_date <- as.Date("2023-10-01")
+cutoff_date_harris <- as.Date("2024-07-21")
 
 # Fitler trump and Harris
-cleaned_data <- cleaned_data %>%
+cleaned_data <- cleaned_data %>% filter(mdy>cutoff_date) %>%
   filter((candidate_name == "Donald Trump") | 
-           (candidate_name == "Kamala Harris" & mdy > cutoff_date))
+           (candidate_name == "Kamala Harris" & mdy > cutoff_date_harris))
 
 # Clean raw dataset, remove columns with many missing values and keep the columns we want to make analysis on
 cleaned_data <- cleaned_data %>% dplyr::select(pollster_rating_name, methodology, numeric_grade, start_date,
@@ -64,6 +65,13 @@ cleaned_data <- cleaned_data %>%
 # Revise the name of column 
 cleaned_data <- cleaned_data %>%
   rename(percent = pct)
+
+# Create the counting down column to the final election date
+final_election <- as.Date("11/5/24", format="%m/%d/%y")
+
+# Create the column
+cleaned_data <- cleaned_data %>% 
+  mutate(days_until_election = as.numeric(difftime(final_election, end_date, units = "days")))
 
 # Delete NA
 cleaned_data <- na.omit(cleaned_data)

### 2024-10-25 scripts/06-model_data.R

@@ -14,13 +14,11 @@
 library(tidyverse)
 library(dplyr)
 library(rstanarm)
-library(bayesplot)
 library(ggplot2)
 library(caret)
 library(modelsummary)
 library(arrow)
 library(rsample)
-library(splines)
 
 
 #### Read data ####
@@ -29,57 +27,36 @@ analysis_data <- read_parquet("data/02-analysis_data/cleaned_US_voting.parquet")
 analysis_data <- analysis_data |>
   filter(candidate_name == "Donald Trump") 
 
-# Build up model
-regression_model <- lm(percent ~ numeric_grade + sample_size + state + transparency_score + end_date, 
-                      data = analysis_data)
+# Count occurrences of each state in the test data
+#state_counts <- table(analysis_data$state)
 
-#### Save model ####
-# Save the model 
-saveRDS(regression_model, file = "models/regression_model.rds")
+# Identify states that appear only once
+#single_occurrence_states <- names(state_counts[state_counts == 1])
 
+# Print the states that appear only once
+#print(single_occurrence_states)
 
-
+# Filter out states that appear only once in analysis_data_test
+#analysis_data<- analysis_data %>%
+  #filter(!state %in% single_occurrence_states)
 
 ### Model data ####
-#Build up Logistic Regression Model
-# For reproducibility
 set.seed(853)
 
-# Group by more detailed factors
-analysis_data <- analysis_data %>%
-  group_by(state, pollster_rating_name, methodology, sample_size, population_group) %>%
-  summarise(
-    Trump_percent = mean(percent[candidate_name == "Donald Trump"], na.rm = TRUE),
-    Harris_percent = mean(percent[candidate_name == "Kamala Harris"], na.rm = TRUE)
-  )
+# Perform a stratified split based on the 'state' variable to ensure all levels are present in both sets
+split <- initial_split(data=analysis_data, prop = 0.8, strata = state)
 
-# Create a binary outcome for prediction: 1 if Trump is predicted to win, 0 if Harris
-analysis_data <- analysis_data %>%
-  mutate(trump_win = ifelse(Trump_percent > Harris_percent, 1, 0))
-
-analysis_data <- na.omit(analysis_data)
-# Split the data into training (70%) and testing (30%) sets
-split <- initial_split(analysis_data, prop = 0.7)
-analysis_train_data <- training(split)
-analysis_test_data <- testing(split)
+# Create training and testing sets
+analysis_data_train <- training(split)
[…]

### 2024-10-25 paper/paper.qmd
Update model diagnosis section.

--- 2024-10-24 paper/paper.qmd
@@
 toc: true
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The study predicting the 2024 U.S.
+presidential election is important as it provides the predicted outcomes for the US election.
+Analysis is based on state-by-state electoral votes, and these outcomes can influence campaign strategies and shape public discourse.
+The results indicate Kamala Harris will win by over 270 votes in this election cycle."
 format: pdf
@@
 
-#install.packages("tidymodels")
-#install.packages("usmap")
+# Install the required packages
+#install.packages(c("tidyverse", "ggplot2", "rstanarm", "knitr", "usmap", "arrow"))
 library(tidyverse)
@@
 library(usmap)
+library(arrow)
 
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+@sec-data expains the data we used to build up the prediction mode.
 
@@
   theme_minimal()
+
 ```
@@
 The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\
-* The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
+- The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
 A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.\
-* The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
-* The state-level effects account for regional differences in Trump’s support.
+- The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
+- The state-level effects account for regional differences in Trump’s support.
 Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.
@@
 ## Model Justification
-@tbl-summary shows the summary table for the model. And then evaluate it on the test set. It appears as though the model is having difficulty identifying Trump supporters.
+@tbl-summary shows the summary table for the model.
+And then evaluate it on the test set.
+It appears as though the model is having difficulty identifying Trump supporters.
+The reson why the multiple regression is applied is because.....
+
 ```{r}
-#| echno: False
+#| echno: false
 #| label: tbl-summary
@@
 # Display the first 10 rows of the coefficients table using kable, formatted to 4 decimal places
-kable(head(coefficients_table, 10), digits = 4)
-```
-
-### VIF Evaluation
-@tbl-vif displays that
-
-```{r}
-#| echno: false
-#| label: tbl-vif
-#| tbl-cap: VIF shows a reasonable output.
-#| echo: false
-#| warning: false
-#| message: false
-
-library(car)
-kable(vif(regression_model))
+kable(head(coefficients_table, 10), digits = 2)
 ```
@@
 
+# Read the test data from the .parquet file
+analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
+analysis_data_train<- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
+# Filter out states in the test data that don't exist in the training data
+
+analysis_data_test <- analysis_data_test %>%
+ filter(state %in% unique(analysis_data_train$state))
+
 # Define electoral votes for each state
@@
   electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
-                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
-)
+                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3))
 
 # Apply the regression model to predict Trump's percentage in each state
-analysis_data$predicted_percent_trump <- predict(regression_model, newdata = analysis_data)
+analysis_data_test$predicted_percent_trump <- predict(regression_model, newdata = analysis_data_test)
 
 # Summarize Trump's predicted percentage for each state
-total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data, FUN = mean)
+total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data_test, FUN = mean)
 
@@
 harris_electoral_votes <- sum(state_predictions$harris_electoral_votes)
-
-# Create a table showing the prediction results
-library(knitr)
 
@@
 #| message: false
+
+# Replace NA values in the 'winner' column with 'Trump'
+#state_predictions$winner[is.na(state_predictions$winner)] <- "Trump"
 
@@
 ```{r}
-#| echno: false
-#| label: fig-diagnosis-1
+#| echo: false
+#| label: fig-diagnosis-3
 #| tbl-cap: Linear Regression Assumptions hold
-#| echo: false
 #| warning: false
 #| message: false
+#| fig.width: 10
+#| fig.height: 8
 
@@
 
-## Multicolinearity Check
+## Calculate Mean Squared Error (MSE) on test data
+```{r}
+#| echo: false
+#| label: fig-diagnosis-1
+#| tbl-cap: Calculate Mean Squared Error (MSE) on test data
+#| warning: false
+#| message: false
+
+predicted_values <- predict(regression_model, newdata = analysis_data_test)
+actual_values <- analysis_data_test$percent
+
+mse <- mean((predicted_values - actual_values)^2)
+print(mse)
+```
+
+```{r}
+
+library(caret)
+set.seed(856)
+train_control <- trainControl(method = "cv", number = 10)
+cv_model <- train(percent ~ numeric_grade + sample_size + state + transparency_score + end_date,
+                  data = analysis_data_train,
+                  method = "lm",
+                  trControl = train_control)
+
+print(cv_model$results)
+
+```
+
+```{r}
+baseline_prediction <- mean(analysis_data_train$percent)
+baseline_mse <- mean((analysis_data_test$percent - baseline_prediction)^2)
+print(baseline_mse)
+```
+
+```{r}
+# Calculate R-squared on test data
+rss <- sum((predicted_values - actual_values)^2)  # Residual Sum of Squares
+tss <- sum((actual_values - mean(actual_values))^2)  # Total Sum of Squares
+
+r_squared <- 1 - (rss/tss)
+print(r_squared)
+```
+
+```{r}
+# Create a correlation matrix to check for collinearity
+cor_matrix <- cor(analysis_data_train[, c("numeric_grade", "sample_size", "transparency_score")], use = "complete.obs")
+print(cor_matrix)
+```
+```{r}
+# Check for sparse levels in 'state'
+state_counts <- table(analysis_data_train$state)
+print(state_counts)
+```
 

### 2024-10-25 paper/paper.qmd
Add reference bib.

@@
 ```
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-\newpage
 
@@
 ```{r}
-
+#| echo: false
 library(caret)
@@
 ```{r}
+#| echo: false
 baseline_prediction <- mean(analysis_data_train$percent)
@@
 ```{r}
+#| echo: false
 # Calculate R-squared on test data
@@
 ```{r}
+#| echo: false
 # Create a correlation matrix to check for collinearity
@@
 ```
+
 ```{r}
+#| echo: false
 # Check for sparse levels in 'state'
@@
 @citeR
-Thanks to Open AI [@openai2024chatgpt] and ChatGPT 4.0 is used to write the analysis of the paper.
+Thanks to Open AI and ChatGPT 4.0 is used to write the analysis of the paper.
+
+@fivethirty provides the data. @tidyverse, @ggplot, @knitr
 

### 2024-10-31 paper/paper.qmd
Add the Historical Lean of the Missing State

@@
 
-The dataset for this analysis is sourced from FiveThirtyEight, which rigorously collects and aggregates polling data from a variety of firms to reflect public opinion.
-To ensure the integrity of the data, only polls that adhere to specific criteria are included in the dataset.
-Each poll must provide essential information, such as the pollster’s name, survey dates, sample sizes, and methodological details (e.g., polling medium, voter files, weighting criteria).
-Polls that are deemed nonscientific, that blend data from multiple sources, or that are conducted by hobbyists are excluded.
+The dataset used in this analysis originates from FiveThirtyEight, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately.
+To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset.
+Specifically, each poll must disclose crucial information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details.
+These details encompass the polling medium (e.g., phone, online), use of verified voter files, demographic weighting criteria, and any adjustments applied to reflect a representative sample.
 
-Once a poll meets these stringent standards, it is incorporated into the database, enabling it to inform polling averages, forecasts, and political coverage.
-This careful selection process ensures that the dataset accurately captures and reflects the nuances of public sentiment and behavior.
+Polls are rigorously verified, and those that do not meet these requirements are excluded from the dataset.
+For instance, polls categorized as nonscientific, those that merge data from multiple unrelated sources, and those conducted by hobbyists or unverified entities are filtered out to prevent data quality compromise.
+
+Once deemed credible, polls are incorporated into the FiveThirtyEight database.
+These polls then contribute to polling averages, forecast models, and political coverage, which depend heavily on the quality and reliability of public opinion data.
+This meticulous selection process ensures that the dataset captures a comprehensive and nuanced view of public sentiment, providing an accurate reflection of behavioral trends and preferences over time.
 
@@
             "District of Columbia"),
-  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
-                      3, 10, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3))
+  electoral_votes = c(9, 3, 11, 6, 54, 10, 7, 3, 30, 16, 4, 4, 20, 11, 6, 6, 8, 8, 4, 10, 11, 15, 10, 6, 10, 
+                      4, 5, 6, 4, 14, 5, 28, 16, 3, 17, 7, 6, 19, 4, 9, 3, 11, 40, 6, 3, 13, 12, 5, 10, 3, 3))
 
@@
 
-# Print the results for the total electoral votes
-print(paste("Trump Electoral Votes:", trump_electoral_votes))
-print(paste("Harris Electoral Votes:", harris_electoral_votes))
+```
+
+```{r}
+#| echno: false
+#| label: tbl-missing
+#| tbl-cap: Missing States with Predicted Winner Based on Historical Lean
+#| echo: false
+#| warning: false
+#| message: false
+# Create the data frame with missing states, electoral votes, and predicted winner based on historical lean
+missing_states <- data.frame(
+  state = c("Alabama", "Alaska", "Arkansas", "Connecticut", "Delaware", "Hawaii", "Idaho", 
+            "Illinois", "Indiana", "Kansas", "Kentucky", "Louisiana", "Mississippi", "North Dakota", 
+            "Oklahoma", "Oregon", "South Carolina", "Tennessee", "Utah", "Washington", 
+            "West Virginia", "Wyoming", "District of Columbia"),
+  Electoral_Votes = c(9, 3, 6, 7, 3, 4, 4, 19, 11, 6, 8, 8, 6, 3, 7, 8, 9, 11, 6, 12, 4, 3, 3),
+  Prediction_Based_on_Historical_Lean = c("Trump", "Trump", "Trump", "Harris", "Harris", 
+                                          "Harris", "Trump", "Harris", "Trump", "Trump", 
+                                          "Trump", "Trump", "Trump", "Trump", "Trump", 
+                                          "Harris", "Trump", "Trump", "Trump", "Harris", 
+                                          "Trump", "Trump", "Harris")
+)
+
+# Display the table with kable
+kable(missing_states, col.names = c("State", "Electoral Votes", "Prediction Based on Historical Lean"))
+
 ```
@@
 #| message: false
+state_predictions <- merge(state_predictions, missing_states, by = "state", all = TRUE)
 
-# Replace NA values in the 'winner' column with 'Trump'
-#state_predictions$winner[is.na(state_predictions$winner)] <- "Trump"
+state_predictions <- state_predictions %>%
+  mutate(
+    trump_electoral_votes = case_when(
+      is.na(Prediction_Based_on_Historical_Lean) ~ trump_electoral_votes,  # Keep original if NA
+      Prediction_Based_on_Historical_Lean == "Trump" ~ Electoral_Votes,    # Assign Electoral_Votes if "Trump"
+      TRUE ~ 0  # Set to 0 otherwise
+    ),
+    harris_electoral_votes = case_when(
+      is.na(Prediction_Based_on_Historical_Lean) ~ harris_electoral_votes,  # Keep original if NA
+      Prediction_Based_on_Historical_Lean == "Harris" ~ Electoral_Votes,    # Assign Electoral_Votes if "Harris"
+      TRUE ~ 0  # Set to 0 otherwise
+    )
+  )
 
-# "red" for Trump and "blue" for Harris
+# Replace NA values in the 'winner' column with historical lean predictions for missing states
+state_predictions$winner <- ifelse(
+  is.na(state_predictions$winner),
+  state_predictions$Prediction_Based_on_Historical_Lean,
+  state_predictions$winner
+)
+
+# Assign colors based on the updated 'winner' column
 state_predictions$winner_color <- ifelse(state_predictions$winner == "Trump", "red", "blue")
@@
 plot_usmap(data = state_predictions, values = "winner_color", regions = "states") +
-  scale_fill_manual(values = c("red" = "red", "blue" = "blue"), name = "Predicted Winner", labels = c("Harris", "Trump")) +
+  scale_fill_manual(values = c("red" = "red", "blue" = "blue"), 
+                    name = "Predicted Winner", labels = c("Harris", "Trump")) +
   labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
@@
 However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
+
+```{r}
+#| echno: false
+#| label: fig-statenum
+#| tbl-cap: Numerical Predicted Winner of 2024 US Presidential Election by State
+#| echo: false
+#| warning: false
+#| message: false
+
+trump_total <- sum(state_predictions$trump_electoral_votes, na.rm = TRUE)
+harris_total <- sum(state_predictions$harris_electoral_votes, na.rm = TRUE)
+
+# Create a summary data frame
+summary_df <- data.frame(
+  Candidate = c("Trump", "Harris"),
+  Total_Electoral_Votes = c(trump_total, harris_total)
+)
+
+# Display the summary table in kable format
+cat("\nTotal Electoral Votes:\n")
+kable(summary_df, col.names = c("Candidate", "Total Electoral Votes"), format = "markdown")
+```
 

### 2024-10-31 paper/paper.qmd
Update script

--- 2024-10-25 paper/paper.qmd
@@
 ggplot(analysis_data, aes(x = percent)) +
-  geom_histogram(binwidth = 2, fill = "green", color = "black", alpha = 0.7) +
+  geom_histogram(binwidth = 2, fill = "pink", color = "white", alpha = 0.7) +
   labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
@@
        aes(x = numeric_grade)) + 
-    geom_histogram(binwidth = 0.1, fill = "green", color = "black", alpha = 0.7) + 
+    geom_histogram(binwidth = 0.1, fill = "pink", color = "white", alpha = 0.7) + 
     scale_x_continuous(breaks = seq(2.5, 3.0, by = 0.1)) + 
@@
 ggplot(analysis_data %>% filter(sample_size < 3000), aes(x = sample_size)) +
-  geom_histogram(binwidth = 100, fill = "green", color = "black", alpha = 0.7) +
+  geom_histogram(binwidth = 100, fill = "pink", color = "white", alpha = 0.7) +
   labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
@@
        aes(x = transparency_score)) + 
-  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.7) + 
+  geom_histogram(binwidth = 1, fill = "pink", color = "white", alpha = 0.7) + 
   scale_x_continuous(breaks = 3:10) +
@@
 ggplot(analysis_data, aes(x = as.Date(end_date))) + 
-  geom_line(stat = "count", color = "black", size = 1) + 
+  geom_line(stat = "count", color = "pink", size = 1) + 
   labs(title = "Distribution of End Dates", x = "End Date", y = "Count") + 

### 2024-10-31 scripts/06-model_data.R

@@ -27,19 +27,6 @@ analysis_data <- read_parquet("data/02-analysis_data/cleaned_US_voting.parquet")
 analysis_data <- analysis_data |>
   filter(candidate_name == "Donald Trump") 
 
-# Count occurrences of each state in the test data
-#state_counts <- table(analysis_data$state)
-
-# Identify states that appear only once
-#single_occurrence_states <- names(state_counts[state_counts == 1])
-
-# Print the states that appear only once
-#print(single_occurrence_states)
-
-# Filter out states that appear only once in analysis_data_test
-#analysis_data<- analysis_data %>%
-  #filter(!state %in% single_occurrence_states)
-
 ### Model data ####
 set.seed(853)
 

### 2024-10-31 scripts/06-model_data.R
Model variable is changed.

@@ -39,7 +39,7 @@ analysis_data_test <- testing(split)
 
 
 # Build up model
-regression_model <- lm(percent ~ numeric_grade + sample_size + state + transparency_score + end_date, 
+regression_model <- lm(percent ~ numeric_grade + sample_size + state + transparency_score + days_until_election, 
                       data = analysis_data_train)
 
 #### Save model ####

### 2024-10-31 scripts/00-simulate_data.R
Revise preamble in the simulate script.

@@ -5,7 +5,7 @@
 # Date: 18 October 2024
 # Contact: isabella.zhou@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Get the raw data from the US election pollsters from fivethirtyeight
+# Pre-requisites: Construct the overview of how the dataset should look like.
 # Any other information needed? Make sure you are in the `2024USpresidentialelection` rproj
 
 

### 2024-10-31 paper/paper.qmd
Paper updated.

--- 2024-10-31 paper/paper.qmd
@@
   - Yuxuan Wei
-thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git."
+thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git"
 date: today
@@
 Analysis is based on state-by-state electoral votes, and these outcomes can influence campaign strategies and shape public discourse.
-The results indicate Kamala Harris will win by over 270 votes in this election cycle."
+The result indicates Kamala Harris will win by over 270 votes in this election cycle."
 format: pdf
@@
 # Install the required packages
-#install.packages(c("tidyverse", "ggplot2", "rstanarm", "knitr", "usmap", "arrow"))
+#install.packages(c("tidyverse", "ggplot2", "rstanarm", "knitr", "usmap", "corrplot", "arrow"))
 library(tidyverse)
@@
 library(usmap)
+library(corrplot)
 library(arrow)
-
 analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
@@
 
-@sec-data expains the data we used to build up the prediction mode.
+@sec-data explains the data we used to build up the prediction mode.
+
+@sec-model
+@sec-results
+@sec-discussion
+@sec-appendix
 
@@
 
-## Outcome variables
+## Outcome Variable
 
@@
 
-## Predictor variables
+## Predictor Variables
 
@@
 
-### End Date
+### Days Until Election
 
-The end date indicates when each poll concluded.
-@fig-end-date shows that as the final result of the U.S.
-election approached, more polls were conducted and completed.
-This trend reflects an increased interest in capturing public opinion and predicting electoral outcomes as election day neared, emphasizing the significance of real-time sentiment analysis during this critical period.
+The **days until election** represents the remaining time leading up to the final election day.
+As shown in the figure, the support percentage for Donald Trump fluctuated over time, with a slightly downward trend as the election approached, as indicated by the dashed trend line.
+This suggests that while public opinion varied significantly, there was a decrease in support as election day approached.
+This trend highlights the importance of monitoring real-time polling data, as sentiment may shift in the critical months leading up to a closely contested election.
 
@@
 #| label: fig-end-date
-#| fig-cap: Distribution of End Dates
+#| fig-cap: Trend of Support Percentage for Donald Trump Over Days Until Election.
+Fluctuations in support levels are observed as the election approaches, with a slight downward trend indicated by the dashed curve.
 #| echo: false
@@
 
-ggplot(analysis_data, aes(x = as.Date(end_date))) + 
-  geom_line(stat = "count", color = "black", size = 1) + 
-  labs(title = "Distribution of End Dates", x = "End Date", y = "Count") + 
-  theme_minimal()
-
+ggplot(analysis_data, aes(x = days_until_election, y = percent)) + 
+  geom_line(color = "skyblue", size = 1.2) +  
+  geom_smooth(method = "loess", color = "pink", linetype = "dashed", size = 1) +  
+  labs(x = "Days Until Election", y = "Support Percentage") + 
+  theme_minimal(base_size = 14) +  
+  theme(
+    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),  #
+    axis.title.x = element_text(margin = margin(t = 10)),  
+    axis.title.y = element_text(margin = margin(r = 10)),  
+    axis.text = element_text(color = "#555555"),  
+    panel.grid.minor = element_blank()  )
 ```
 
-# Model
+# Model {#sec-model}
 
-To model Donald Trump’s polling percentages over time, we employed a multiple linear regression framework.
-This approach estimates the relationship between polling percentages and various predictors by fitting a linear equation to the data.
-By analyzing the coefficients, we can quantify the impact of each predictor on Trump’s polling percentages, while also assessing the overall fit of the model and making predictions based on the observed trends.
+To model Donald Trump’s polling percentages over time, we used a multiple linear regression framework, which estimates the relationship between polling percentages and various predictors by fitting a linear equation to the data.
+Analyzing the coefficients allows us to quantify the impact of each predictor on Trump’s polling percentages, while also assessing the overall fit of the model for reliable predictions.
 
-Here we briefly describe the multiple linear regression model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].
+To prevent overfitting, we applied a train-test data split.
+The training data is used to build the model, enabling it to learn patterns and relationships within the data.
+The test data, which the model has not seen before, serves to evaluate its performance on new, unseen data.
+This separation ensures that the model captures patterns that will generalize beyond the training dataset, rather than just memorizing it.
+
+Below, we briefly describe the multiple linear regression model used to examine Trump’s winning probability. Additional details and model diagnostics are provided in [Appendix -@sec-model-details].
 
@@
 - Transparency Score (transparency_score): A measure of how transparent the polling data and methodology are.
-- End Date (end_date): The date the poll was completed, which might capture trends over time.
+- Days Until Election (days_until_election): The left days until the US election.
 
@@
 \text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{transparency\_score}_i \\
-             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{end\_date}_i + \epsilon_i \\
+             &\quad + \beta_3 \cdot \text{sample\_size}_i + \beta_4 \cdot \text{state}_i + \beta_5 \cdot \text{days\_until\_election}_i + \epsilon_i \\
 \epsilon_i &\sim \text{Normal}(0, \sigma^2)
@@
 For example, if the coefficient for Florida is negative, it means Trump polls lower in Florida compared to the reference state.
+The state-level effects account for regional differences in Trump’s support.
+Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.
 - Transparency Score ($\beta_4$): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll.
 A positive coefficient would indicate that polls with higher transparency tend to report higher polling percentages for Trump, whereas a negative coefficient would imply the opposite.
-- End Date ($\beta_5$): The end date is a time-related variable, capturing trends over time.
-A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.
-
-## Interpretation
-
-The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\
-- The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
-A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.\
-- The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
-- The state-level effects account for regional differences in Trump’s support.
-Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.
+- Days Until Election ($\beta_5$): The counting down days is a time-related variable.
+A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
+A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.
 
 ## Model Justification
-@tbl-summary shows the summary table for the model.
-And then evaluate it on the test set.
-It appears as though the model is having difficulty identifying Trump supporters.
-The reson why the multiple regression is applied is because.....
+Based on the model summary shown in @tbl-summary-model, we observe that several state-level coefficients are statistically significant, indicating regional variations in support for Trump.
+Additionally, the coefficients for `transparency_score` and `days_until_election` are both highly significant, suggesting that pollster quality and the timing of the polls have notable effects on Trump’s polling percentages.
+A negative coefficient for `days_until_election` suggests a slight decline in support as the election approaches.
+
+When evaluated on the test set, the model appears to struggle with accurately identifying Trump supporters, possibly due to unobserved factors or limitations in capturing the complexity of voter behavior.
+
+The rationale for applying multiple regression in this context is to control for various influential factors simultaneously—such as time trends (`days_until_election`), pollster quality (`transparency_score`), and regional differences (`state-level effects`).
+This approach allows us to isolate the individual impact of each variable, providing a more detailed understanding of how each factor contributes to Trump’s polling outcomes.
+The full coefficient output is shown in the [Appendix -@sec-model-details]
 
 ```{r}
-#| echno: false
-#| label: tbl-summary
-#| tbl-cap: Regression Model Estimate Summary
 #| echo: false
+#| label: tbl-summary-model
+#| tbl-cap: Regression Model Summary Table
 #| warning: false
@@
 summary<-summary(regression_model)
-
 # Extract the coefficients to form a table
@@
 
-# Display the first 10 rows of the coefficients table using kable, formatted to 4 decimal places
+# Display the first 10 rows of the coefficients table using kable, formatted to 2 decimal places
 kable(head(coefficients_table, 10), digits = 2)
@@
 
-# Results
+# Results {#sec-results}
 
@@
 
-Electoral Vote Count:
-- Trump Electoral Votes: 78
-- Harris Electoral Votes: 416
-These results indicate that based on the current model predictions, Harris is expected to win the 2024 U.S.
-Presidential Election, securing 416 electoral votes, compared to Trump’s 78 electoral votes.
-The election outcome hinges on several battleground states, where the vote margins are predicted to be narrow.
-
-```{r tbl-prediction}
-#| echno: false
+```{r}
+#| echo: false
 #| label: tbl-prediction
 #| tbl-cap: Prediction for Trump and Harris by Electoral College
-#| echo: false
 #| warning: false
@@
 # Filter out states in the test data that don't exist in the training data
-
 analysis_data_test <- analysis_data_test %>%
@@
       digits = 2)
-
 ```
 
+## Predicted Electoral Outcomes by State
+The following table (@tbl-missing) serves as a supplement to the predicted outcomes, filling in the gaps for states where the model couldn’t provide predictions.
+It allows for a complete view of electoral projections by assigning a likely outcome in each missing state based on historical data.
+This approach ensures every state is accounted for in the final electoral vote totals.
+
 ```{r}
-#| echno: false
+#| echo: false
 #| label: tbl-missing
 #| tbl-cap: Missing States with Predicted Winner Based on Historical Lean
-#| echo: false
 #| warning: false
@@
 kable(missing_states, col.names = c("State", "Electoral Votes", "Prediction Based on Historical Lean"))
-
 ```
 
-## Predicted Electoral Outcomes by State
-The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S. Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
+The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S.
+Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
+The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois.
+However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
 
-```{r tbl-prediction}
-#| echno: false
+```{r fig-statemap}
+#| echo: false
 #| label: fig-statemap
 #| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
-#| echo: false
 #| warning: false
 #| message: false
+
 state_predictions <- merge(state_predictions, missing_states, by = "state", all = TRUE)
@@
 ```
-The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois.
-However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
 
+The table below (@tbl-numstate) shows the numerical predicted winner of the 2024 US Presidential Election by state.
+Harris is expected to win the 2024 U.S.
+Presidential Election, securing 387 electoral votes, compared to Trump’s 151 electoral votes.
+The election outcome hinges on several battleground states, where the vote margins are predicted to be narrow.
 ```{r}
-#| echno: false
-#| label: fig-statenum
+#| echo: false
+#| label: tbl-numstate
 #| tbl-cap: Numerical Predicted Winner of 2024 US Presidential Election by State
-#| echo: false
 #| warning: false
@@
 # Display the summary table in kable format
-cat("\nTotal Electoral Votes:\n")
 kable(summary_df, col.names = c("Candidate", "Total Electoral Votes"), format = "markdown")
@@
 
-## What Is Done in This Paper?
-This paper uses a regression model to predict the outcome of the 2024 U.S.
-Presidential Election between Donald Trump and Kamala Harris.
-By analyzing historical voting data, the model forecasts the percentage of votes Trump is expected to receive in each state.
-These predictions are combined with the state's electoral vote allocation to determine the overall winner.
-The findings indicate a significant electoral victory for Harris, projecting 416 electoral votes for her compared to 78 for Trump.
-A geographic map is also presented to visualize state-level outcomes and highlight regional voting trends.
+## Overview of Predictive Modeling for the 2024 U.S. Election
+This paper employs a regression model to forecast the 2024 U.S.
+Presidential Election outcomes between Kamala Harris and Donald Trump.
+By analyzing historical state-level voting data, we estimated Trump’s vote percentages across states and calculated each candidate’s projected electoral votes.
+Our model predicts a significant victory for Harris, who is projected to secure 387 electoral votes compared to Trump’s 151.
+This finding underscores the impact of demographic and geographic factors on the U.S.
+electoral landscape.
+A geographic visualization further emphasizes the anticipated state-by-state outcomes and reveals enduring regional voting patterns.
 
-## What Do We Learn About the World?
-The study highlights the persistence of geographic voting patterns in U.S.
+## Regional Voting Patterns and Their Impact on Electoral Outcomes
+Our analysis demonstrates the persistence of geographic voting patterns in U.S.
 elections.
-Even with changes in candidates, many states follow their historical voting tendencies.
-Republican-leaning states like Alabama and Wyoming are projected to support Trump, while Democratic-leaning states such as California and New York favor Harris.
-This pattern shows the strong influence of regional political loyalties, which continue to shape election outcomes.
+As expected, traditional Democratic strongholds such as California, New York, and Illinois favor Harris, while Republican-dominated states like Alabama and Wyoming show support for Trump.
+These regional preferences align with historical voting behaviors, suggesting that party loyalty and demographic factors continue to shape election results.
 
-## Another Thing We Learn About the World
-The analysis underscores the importance of battleground states in determining the election's outcome.
-States like Florida and Arizona, predicted to lean toward Harris, play a decisive role in the projected electoral victory.
-This illustrates how close contests in a few states can influence the overall election result, emphasizing the significant impact these states have in shaping the presidency.
+The model also highlights the critical role of battleground states, with states such as Florida and Arizona predicted to lean toward Harris.
+The influence of these states, where margins are often narrow, emphasizes the importance of campaign efforts and voter mobilization in these regions.
+The projections illustrate that minor shifts in voter sentiment within these states could decisively impact the overall election outcome.
 
-## What Is Left to Learn or How Should We Proceed in the Future?
-Future research should incorporate more detailed data, including demographic shifts and economic factors that may influence voter preferences.
-It would be valuable to examine how emerging political movements and changes in communication strategies affect elections, particularly in closely contested states.
-Post-election analysis comparing predictions with actual results will also be essential to improving the accuracy of models and understanding how unforeseen events may alter outcomes.
+## Polling and Electoral Uncertainty
+The model’s reliance on historical polling data and state-level predictions reflects certain limitations inherent in election forecasting.
+For example, while the model captures general trends, it does not account for potential turnout variations, third-party candidates, or unexpected political events that might affect voter behavior.
+Furthermore, the use of polling data presents a challenge due to its variability; certain states with less frequent polling data show broader confidence intervals, indicating greater uncertainty in those regions.
 
-## Weaknesses and Next Steps
-While the model offers a useful prediction, it has limitations.
-It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election.
-The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts.
-Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape.
-The logistic regression model is limited by the lack of interaction terms between states, which may obscure regional trends or external factors that influence neighboring states.
-Additionally, the model assumes that polling data accurately reflects voter intentions, but biases or missing data in key regions could affect the predictions.
+This variability suggests that further studies could benefit from integrating real-time data and employing Bayesian methodologies to account for evolving voter preferences.
+Such an approach could improve the accuracy of predictions, especially in regions with historically unpredictable outcomes.
+Future research may also consider factors like demographic shifts and economic conditions, which could significantly influence voter preferences over time.
 
-Future iterations of this model should incorporate voter turnout predictions, demographic variables, and real-time polling updates to better capture the dynamics of voter behavior.
-Including social media sentiment analysis and analyzing cross-state interactions could refine the prediction model, offering more nuanced insights into election forecasts.
+## Implications for Future Electoral Modeling
+The findings from this analysis underscore the need for a nuanced approach to election forecasting.
+While historical voting patterns provide a solid foundation, they may not fully capture the complexities of modern elections, where factors such as social media influence and voter sentiment play increasingly prominent roles.
+Incorporating these additional variables, particularly in battleground states, could refine the model’s predictive power and provide a more comprehensive understanding of the electoral landscape.
+
+For future iterations, we recommend expanding the model to include demographic data, such as age, education level, and income, which could reveal deeper insights into voter behavior.
+Additionally, real-time polling updates could offer a dynamic perspective, allowing the model to adapt to changes in public opinion as the election date approaches.
+Employing these enhancements would improve model reliability, particularly in closely contested states where the margin of error can significantly impact the final prediction.
+
+## Weakness
+Despite the model's strengths, it has limitations that requires further exploration.
+The assumption of linear relationships between predictors may oversimplify complex voter behaviors and social influences.
+The dataset simplifies the potentioanl influecne behind the US election.
+Additionally, the reliance on past data assumes that historical trends will persist, which may not hold true in the rapidly shifting political climate of the U.S.
+To address these issues, future models could benefit from incorporating voter turnout projections and real-time sentiment analysis, potentially drawing data from social media platforms and news sources to gauge public opinion.
+Moreover, a comparative post-election analysis could offer valuable insights, revealing areas where the model succeeded and where it may need refinement.
+This iterative approach would help create a more resilient and adaptable electoral forecasting model.
 
@@
 
-# Appendix {-}
+# Appendix {#sec-appendix}
 
@@
 
-### **Survey Structure**:
+### **Survey Structure**
 
@@
 #| echo: false
-#| label: fig-diagnosis-3
-#| tbl-cap: Linear Regression Assumptions hold
+#| label: fig-diagnosis-1
+#| tbl-cap: Linear regression assumptions hold.
 #| warning: false
@@
 plot(regression_model)
-
 ```
 
-## Calculate Mean Squared Error (MSE) on test data
+## Calculate Mean Squared Error and Mean Absolute Error on Test Data
 ```{r}
 #| echo: false
-#| label: fig-diagnosis-1
+#| label: fig-diagnosis-2
 #| tbl-cap: Calculate Mean Squared Error (MSE) on test data
@@
 
+# Predicted and actual values
 predicted_values <- predict(regression_model, newdata = analysis_data_test)
@@
 
+# Calculate Mean Squared Error (MSE)
 mse <- mean((predicted_values - actual_values)^2)
-print(mse)
+
+# Calculate Mean Absolute Error (MAE)
+mae <- mean(abs(predicted_values - actual_values))
+
+# Calculate R-squared
+ss_total <- sum((actual_values - mean(actual_values))^2)
+ss_residual <- sum((predicted_values - actual_values)^2)
+r_squared <- 1 - (ss_residual / ss_total)
+
+# Combine metrics into a data frame for display
+metrics_df <- data.frame(
+  Metric = c("Mean Squared Error (MSE)", "Mean Absolute Error (MAE)", "R-squared"),
+  Value = c(mse, mae, r_squared))
+
+# Display the metrics table using kable
+kable(metrics_df, caption = "Model Performance Metrics on Test Data")
 ```
 
+## Model Summary
 ```{r}
 #| echo: false
-library(caret)
-set.seed(856)
-train_control <- trainControl(method = "cv", number = 10)
-cv_model <- train(percent ~ numeric_grade + sample_size + state + transparency_score + end_date,
-                  data = analysis_data_train,
-                  method = "lm",
-                  trControl = train_control)
+#| tbl-cap: Complete Model Coefficient Summary Table
+#| warning: false
+#| message: false
 
-print(cv_model$results)
+# Get summary of the regression model
+model_summary <- summary(regression_model)
 
+# Extract and convert the coefficients summary to a data frame
+coefficients_df <- as.data.frame(model_summary$coefficients)
+colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")
+
+# Extract additional statistics
+r_squared <- model_summary$r.squared
+adj_r_squared <- model_summary$adj.r.squared
+f_statistic <- model_summary$fstatistic[1]
+p_value <- pf(f_statistic, model_summary$fstatistic[2], model_summary$fstatistic[3], lower.tail = FALSE)
+residual_se <- model_summary$sigma
+
+# Create a data frame for additional statistics with consistent column names
+additional_stats <- data.frame(
+  Estimate = c(r_squared, adj_r_squared, f_statistic, p_value, residual_se),
+  `Std. Error` = NA,
+  `t value` = NA,
+  `Pr(>|t|)` = NA,
+  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "F-statistic p-value", "Residual Std. Error")
+)
+
+# Ensure column names are identical between data frames
+colnames(additional_stats) <- colnames(coefficients_df)
+
+# Combine the coefficients and additional statistics
+full_summary_df <- rbind(coefficients_df, additional_stats)
+
+# Display the full summary table using kable
+kable(full_summary_df, caption = "Regression Model Summary with Additional Statistics")
 ```
 
+## Multicollinearity Check on the Training Data
 ```{r}
 #| echo: false
-baseline_prediction <- mean(analysis_data_train$percent)
-baseline_mse <- mean((analysis_data_test$percent - baseline_prediction)^2)
-print(baseline_mse)
-```
+#| warning: false
+#| message: false
 
-```{r}
-#| echo: false
-# Calculate R-squared on test data
-rss <- sum((predicted_values - actual_values)^2)  # Residual Sum of Squares
-tss <- sum((actual_values - mean(actual_values))^2)  # Total Sum of Squares
+# Calculate the correlation matrix
+cor_matrix <- cor(analysis_data_train[, c("numeric_grade", "sample_size", "transparency_score", "days_until_election")], use = "complete.obs")
 
-r_squared <- 1 - (rss/tss)
-print(r_squared)
-```
+# Rename the row and column names of the correlation matrix to remove underscores
+colnames(cor_matrix) <- gsub("_", " ", colnames(cor_matrix))
+rownames(cor_matrix) <- gsub("_", " ", rownames(cor_matrix))
 
-```{r}
-#| echo: false
-# Create a correlation matrix to check for collinearity
-cor_matrix <- cor(analysis_data_train[, c("numeric_grade", "sample_size", "transparency_score")], use = "complete.obs")
+# Print the correlation matrix
 print(cor_matrix)
-```
 
-```{r}
-#| echo: false
-# Check for sparse levels in 'state'
-state_counts <- table(analysis_data_train$state)
-print(state_counts)
+# Create a beautiful correlation plot with modified labels
+corrplot(
+  cor_matrix, 
+  method = "color",      # Use color to fill the matrix
+  type = "upper",        # Show only the upper triangle
+  addCoef.col = "black", # Add correlation coefficients in black
+  tl.col = "black",      # Label text color
+  tl.srt = 45,           # Rotate labels
+  number.cex = 0.8,      # Text size for coefficients
+  col = colorRampPalette(c("red", "white", "blue"))(200) # Color gradient
+)
+
 ```

### 2024-10-31 paper/paper.qmd
Typo updated.

@@
 #| label: fig-diagnosis-2
-#| tbl-cap: Calculate Mean Squared Error (MSE) on test data
+#| tbl-cap: Calculate Mean Squared Error (MSE) on Test Data
 #| warning: false
@@
 # Display the metrics table using kable
-kable(metrics_df, caption = "Model Performance Metrics on Test Data")
+kable(metrics_df)
 ```
@@
 # Display the full summary table using kable
-kable(full_summary_df, caption = "Regression Model Summary with Additional Statistics")
+kable(full_summary_df)
 ```
@@
 #| echo: false
+#| fig-cap: Correlation Matrix of "Numeric Grade", "Sample Size", "Transparency Score"and "Days Until Election"
 #| warning: false
@@
 
-# Print the correlation matrix
-print(cor_matrix)
-
 # Create a beautiful correlation plot with modified labels
@@
   cor_matrix, 
-  method = "color",      # Use color to fill the matrix
-  type = "upper",        # Show only the upper triangle
-  addCoef.col = "black", # Add correlation coefficients in black
-  tl.col = "black",      # Label text color
-  tl.srt = 45,           # Rotate labels
-  number.cex = 0.8,      # Text size for coefficients
-  col = colorRampPalette(c("red", "white", "blue"))(200) # Color gradient
-)
+  method = "color",      
+  type = "upper",        
+  addCoef.col = "black", 
+  tl.col = "black",      
+  tl.srt = 45,          
+  number.cex = 0.8,      
+  col = colorRampPalette(c("red", "white", "blue"))(200) )
 

### 2024-10-31 paper/paper.qmd
Modify the format of Appendix A

@@
 @sec-discussion
-@sec-appendix
+@sec-appendixA
+@sec-appendixB
+@sec-model-details
+@sec-acknowledgements
+@sec-references
 
@@
 
-# Appendix {#sec-appendix}
+# Appendix A: Pollster Methodology Overview and Evaluation {#sec-appendixA}
 
-# Pollster Methodology Overview and Evaluation
+## Overview of SurveyUSA
 
-## Overview of SurveyUSA\
 SurveyUSA is a privately held opinion research company that operates nationwide, across all 50 U.S.
@@
 
-## Population, Frame, and Sample\
+## Population, Frame, and Sample
 
@@
 
-## Recruitment\
+## Recruitment
+
 SurveyUSA employs a mixed-method approach to recruitment, including online panels, telephone calls, and a text-to-web method.
@@
 
-## Sampling approach and Trade-offs\
+## Sampling approach and Trade-offs
+
 SurveyUSA uses a blend of probability and non-probability sampling methods.
@@
 
-* **Advantages:**\
+* **Advantages:**
+
 The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population.
@@
 Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
-* **Disadvantages:**\
+* **Disadvantages:**
+
 Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
@@
 
-## Non-response Handling\
+## Non-response Handling
+
 In cases of non-response, SurveyUSA attempts follow-up calls if interviews are interrupted by answering machines or busy signals.
@@
 
-## Questionnaire Evaluation\
+## Questionnaire Evaluation
 
@@
 
-## Summary Evaluation\
+## Summary Evaluation
+
 SurveyUSA’s methodology reflects a balanced approach, leveraging various sampling approach and method to reach a representative sample.
@@
 
-# Appendix B: Idealized Methodology and Survey
+# Appendix B: Idealized Methodology and Survey {#sec-appendixB}
 
@@
 
-# Acknowledgements
+# Acknowledgements {#sec-acknowledgements}
 @citeR
@@
 
-# References
+# References {#sec-references}

### 2024-10-31 paper/paper.qmd
Add Introduction Part, and modify format

@@
 
-Overview paragraph
+The 2024 U.S.
+Presidential Election is set to unfold in a climate of heightened political polarization, economic challenges, and demographic shifts, making it a pivotal event in shaping America's future.
+Predicting the outcome of this election is crucial for gaining insights into potential changes in political leadership and policy directions.
+Polling data has traditionally served as a primary tool for gauging voter sentiment; however, recent election cycles have exposed limitations in polling accuracy due to biases, non-response issues, and variations in poll quality.
+To address these challenges, this study proposes a model that incorporates these factors to enhance the reliability of election forecasts.
 
-Estimand paragraph
+This paper develops a prediction model aimed at forecasting the electoral outcomes between Kamala Harris and Donald Trump in the 2024 election.
+Using a multiple linear regression framework, we analyze aggregated polling data across U.S.
+states, incorporating factors such as poll quality, transparency, sample size, geographic indicators, and poll timing.
+By integrating these variables, our model seeks to provide a nuanced forecast that accounts for regional differences and methodological variations across polls, offering a comprehensive view of the projected support for each candidate.
 
-Results paragraph
+Our findings suggest a competitive election landscape, with Harris showing strong prospects in key battleground states while Trump retains support in traditional Republican strongholds.
+These projections underscore the enduring influence of geographic voting patterns and the impact of polling methodology on electoral forecasting.
+The study provides valuable insights for political analysts, campaign strategists, and the public, contributing to a better understanding of how polling data can be utilized to anticipate electoral outcomes.
 
-Why it matters paragraph
-
-@sec-data explains the data we used to build up the prediction mode.
-
-@sec-model
-@sec-results
-@sec-discussion
-@sec-appendixA
-@sec-appendixB
-@sec-model-details
-@sec-acknowledgements
-@sec-references
+The remainder of this paper is organized as follows: @sec-data describes the dataset and the preprocessing steps involved in preparing data for the model.
+@sec-model explains the modeling approach, including the selection of predictors and the structure of the regression model.
+@sec-results presents the primary findings, highlighting state-by-state predictions and overall electoral projections.
+Section @sec-discussion discusses the implications, limitations, and future directions for this analysis.
+The Appendix section provides supplementary information on methodology, diagnostics, technical details of the model setup, acknowledgments, and references.
 
@@
 
-# Appendix A: Pollster Methodology Overview and Evaluation {#sec-appendixA}
+# Appendix {-}
+
+# Pollster Methodology Overview and Evaluation
 
@@
 
-# Appendix B: Idealized Methodology and Survey {#sec-appendixB}
+# Idealized Methodology and Survey
 
@@
 
-# Acknowledgements {#sec-acknowledgements}
+# Acknowledgements
 @citeR
@@
 
-# References {#sec-references}
+# References

### 2024-10-31 paper/paper.qmd
Update the Title, Abstract, Discussion

@@
 title: "Predicting Kamala Harris's Victory in the 2024 US Election"
-subtitle: "An Investigation into Poll Data Using Multiple Linear Regression"
+subtitle: "Poll Data Predicts Kamala Harris Win with 387 Electoral Votes"
 author: 
@@
 toc: true
-abstract: "The study predicting the 2024 U.S.
-presidential election is important as it provides the predicted outcomes for the US election.
-Analysis is based on state-by-state electoral votes, and these outcomes can influence campaign strategies and shape public discourse.
-The result indicates Kamala Harris will win by over 270 votes in this election cycle."
+abstract: "This study provides a prediction for the 2024 U.S.
+presidential election, presenting potential outcomes based on a state-by-state electoral vote analysis.
+These projections can guide campaign strategies and influence public discourse.
+The results suggest Kamala Harris will secure a win with 387 electoral votes, significantly surpassing the 270 needed for victory.
+In contrast, Donald Trump is predicted to receive 151 electoral votes."
 format: pdf
@@
 #| message: false
-
 ggplot(analysis_data, aes(x = days_until_election, y = percent)) + 
-  geom_line(color = "skyblue", size = 1.2) +  
+    geom_line(color = "skyblue", size = 1) + 
     geom_smooth(method = "loess", color = "pink", linetype = "dashed", size = 1) + 
@@
     theme_minimal(base_size = 14) + 
+    scale_x_reverse() + 
     theme(
-    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),  #
+        plot.title = element_text(face = "bold", size = 16, hjust = 0.5),  
         axis.title.x = element_text(margin = margin(t = 10)), 
@@
         axis.text = element_text(color = "#555555"), 
-    panel.grid.minor = element_blank()  )
+        panel.grid.minor = element_blank()
+    )
+
 ```
@@
 ## Overview of Predictive Modeling for the 2024 U.S. Election
-This paper employs a regression model to forecast the 2024 U.S.
-Presidential Election outcomes between Kamala Harris and Donald Trump.
-By analyzing historical state-level voting data, we estimated Trump’s vote percentages across states and calculated each candidate’s projected electoral votes.
-Our model predicts a significant victory for Harris, who is projected to secure 387 electoral votes compared to Trump’s 151.
+This paper forecasts the 2024 U.S.
+Presidential Election outcomes between Kamala Harris and Donald Trump, presenting a predicted electoral college outcome based on a fitted model.
+By analyzing poll data and historical state-level voting patterns, we estimated Trump’s vote percentages across states and calculated projected electoral votes for each candidate.
+Our model anticipates a significant victory for Harris, who is projected to secure 387 electoral votes compared to Trump’s 151.
 This finding underscores the impact of demographic and geographic factors on the U.S.
 electoral landscape.
+
 A geographic visualization further emphasizes the anticipated state-by-state outcomes and reveals enduring regional voting patterns.
+Key predictors, such as state-level variations and transparency scores, strongly influence polling outcomes for both Donald Trump and Kamala Harris.
+While our model projects a potential Harris victory with a majority of electoral votes, challenges inherent in electoral predictions remain.
+We acknowledge that regional variations, particularly in battleground states like Florida and Arizona, introduce uncertainty that may affect the final outcome.
 
@@
 
+## Weakness
+Despite the model's strengths, it has limitations, which present a critical challenge and requires further exploration.
+The assumption of linear relationships between predictors may oversimplify complex voter behaviors and social influences.
+The dataset simplifies the potentioanl influecne behind the US election.
+
+Moreover, polling averages, though valuable, are subject to biases that may skew results.
+For example, factors like nonresponse bias—where certain demographic groups, such as less civically engaged individuals, are less likely to participate—may influence results more heavily in this election cycle.
+Additionally, reliance on past election data introduces a risk of recency bias, as seen in public expectations shaped by Trump’s unexpected win in 2016 and close finish in 2020.
+Yet, as Nate Silver notes, intuition or prior election outcomes can be misleading, given the unique dynamics of each election.
+Polling errors, such as those seen in 2016 and 2020, further emphasize the need for cautious interpretation of our model’s findings.
+
+@silver2024gut also points out that the voters for Trump are less likely to finish the polls because of “Shy Voters”.
+This may lead to the bias in the survey sample collection.
+The deficiency of education background and sample credibility both influence the prediction.
+
+Additionally, due to limited data available for predicting outcomes in every state, some state projections rely on historical voting patterns, with the assumption that these trends will persist.
+However, this approach may be challenged by the rapidly changing political landscape in the U.S., where evolving demographics and shifting public sentiment could lead to unexpected results.
+
 ## Implications for Future Electoral Modeling
@@
 Employing these enhancements would improve model reliability, particularly in closely contested states where the margin of error can significantly impact the final prediction.
-
-## Weakness
-Despite the model's strengths, it has limitations that requires further exploration.
-The assumption of linear relationships between predictors may oversimplify complex voter behaviors and social influences.
-The dataset simplifies the potentioanl influecne behind the US election.
-Additionally, the reliance on past data assumes that historical trends will persist, which may not hold true in the rapidly shifting political climate of the U.S.
-To address these issues, future models could benefit from incorporating voter turnout projections and real-time sentiment analysis, potentially drawing data from social media platforms and news sources to gauge public opinion.
-Moreover, a comparative post-election analysis could offer valuable insights, revealing areas where the model succeeded and where it may need refinement.
-This iterative approach would help create a more resilient and adaptable electoral forecasting model.
 
@@
 Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
+
 * **Disadvantages:**

### 2024-10-31 paper/paper.qmd
Paper and LLM usage updated.

@@
 # Install the required packages
-#install.packages(c("tidyverse", "ggplot2", "rstanarm", "knitr", "usmap", "corrplot", "arrow"))
+#install.packages(c("tidyverse", "ggplot2", "knitr", "usmap", "corrplot", "arrow"))
 library(tidyverse)
 library(ggplot2)
-library(rstanarm)
 library(knitr)
@@
 - Days Until Election ($\beta_5$): The counting down days is a time-related variable.
-A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time.
-A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.
+A positive and significant coefficient would suggest that Trump’s polling percentage has decreased as the election date approaches, while a negative coefficient would suggest an increase in his polling percent over time.
 
@@
 
-## Overview of Predictive Modeling for the 2024 U.S. Election
-This paper forecasts the 2024 U.S.
-Presidential Election outcomes between Kamala Harris and Donald Trump, presenting a predicted electoral college outcome based on a fitted model.
-By analyzing poll data and historical state-level voting patterns, we estimated Trump’s vote percentages across states and calculated projected electoral votes for each candidate.
-Our model anticipates a significant victory for Harris, who is projected to secure 387 electoral votes compared to Trump’s 151.
-This finding underscores the impact of demographic and geographic factors on the U.S.
-electoral landscape.
+## Key Findings
+This paper presents a forecast for the 2024 U.S.
+Presidential Election between Kamala Harris and Donald Trump, leveraging a linear regression model trained on historical state-level voting data and recent polling information.
+Our model projects a decisive victory for Harris, with an expected 387 electoral votes compared to Trump’s 151, reinforcing the impact of demographic and geographic factors on U.S.
+electoral outcomes.
 
-A geographic visualization further emphasizes the anticipated state-by-state outcomes and reveals enduring regional voting patterns.
-Key predictors, such as state-level variations and transparency scores, strongly influence polling outcomes for both Donald Trump and Kamala Harris.
-While our model projects a potential Harris victory with a majority of electoral votes, challenges inherent in electoral predictions remain.
-We acknowledge that regional variations, particularly in battleground states like Florida and Arizona, introduce uncertainty that may affect the final outcome.
+The analysis reveals that state-specific predictors, such as historical voting patterns and days until election day, are significant influencers of each candidate’s polling outcomes.
+Traditional Democratic strongholds like California and New York strongly favor Harris, while Republican-dominated states such as Alabama and Wyoming align with Trump.
+This distribution reflects enduring geographic voting patterns and underscores the role of regional party loyalty.
+
+Notably, the model also highlights the influence of battleground states, where even slight shifts in voter sentiment could alter the election’s outcome.
+For example, Florida, a key swing state, is predicted to lean narrowly towards Trump with an estimated 50.04% of the vote, emphasizing the potential volatility in these regions.
 
@@
 The influence of these states, where margins are often narrow, emphasizes the importance of campaign efforts and voter mobilization in these regions.
-The projections illustrate that minor shifts in voter sentiment within these states could decisively impact the overall election outcome.
+The projections illustrate that minor shifts in voter sentiment within these states could decisively impact the overall election outcome because of the high number of electoral votes.
 
-## Polling and Electoral Uncertainty
+## Polling and Electoral Uncertainty Beyond the Data
 The model’s reliance on historical polling data and state-level predictions reflects certain limitations inherent in election forecasting.
-For example, while the model captures general trends, it does not account for potential turnout variations, third-party candidates, or unexpected political events that might affect voter behavior.
-Furthermore, the use of polling data presents a challenge due to its variability; certain states with less frequent polling data show broader confidence intervals, indicating greater uncertainty in those regions.
-
-This variability suggests that further studies could benefit from integrating real-time data and employing Bayesian methodologies to account for evolving voter preferences.
-Such an approach could improve the accuracy of predictions, especially in regions with historically unpredictable outcomes.
-Future research may also consider factors like demographic shifts and economic conditions, which could significantly influence voter preferences over time.
+While the model effectively captures overall trends, it cannot account for unforeseen factors, such as shifts in voter turnout, the influence of third-party candidates, or sudden political or social events that could impact voter behavior.
+Additionally, the uneven distribution of survey data across states introduces further uncertainty.Sstates with infrequent polling or underrepresented demographic groups may lead to biased predictions.
+This variation in polling frequency and sample diversity presents a challenge in achieving a fully representative model, and these uncertainties beyond the data are much more complex.
 
 ## Weakness
-Despite the model's strengths, it has limitations, which present a critical challenge and requires further exploration.
-The assumption of linear relationships between predictors may oversimplify complex voter behaviors and social influences.
-The dataset simplifies the potentioanl influecne behind the US election.
+Despite the model estimating the voter's choice trend, it has limitations.
+For instance, assuming linear relationships between predictors may oversimplify complex voter behaviors and other external social influences.
+The dataset simplifies the potential influence behind the US election.
 
-Moreover, polling averages, though valuable, are subject to biases that may skew results.
+Furthermore, polling is susceptible to biases, which can skew results.
 For example, factors like nonresponse bias—where certain demographic groups, such as less civically engaged individuals, are less likely to participate—may influence results more heavily in this election cycle.
 Additionally, reliance on past election data introduces a risk of recency bias, as seen in public expectations shaped by Trump’s unexpected win in 2016 and close finish in 2020.
-Yet, as Nate Silver notes, intuition or prior election outcomes can be misleading, given the unique dynamics of each election.
-Polling errors, such as those seen in 2016 and 2020, further emphasize the need for cautious interpretation of our model’s findings.
+As @silver2024gut notes, intuition or prior election outcomes can be misleading, given the unique dynamics of each election.
+Polling errors, such as those seen in 2016 and 2020, further emphasize the need to carefully interpret our model’s findings.
 
-@silver2024gut also points out that the voters for Trump are less likely to finish the polls because of “Shy Voters”.
-This may lead to the bias in the survey sample collection.
+@silver2024gut also points out that the voters for Trump are less likely to finish the polls because of “Shy Tories”.
+This may lead to bias in the survey sample collection.
 The deficiency of education background and sample credibility both influence the prediction.
 
-Additionally, due to limited data available for predicting outcomes in every state, some state projections rely on historical voting patterns, with the assumption that these trends will persist.
+Due to limited data available for predicting outcomes in every state, some state projections rely on historical voting patterns, with the assumption that these trends will persist.
 However, this approach may be challenged by the rapidly changing political landscape in the U.S., where evolving demographics and shifting public sentiment could lead to unexpected results.
@@
 ## Implications for Future Electoral Modeling
-The findings from this analysis underscore the need for a nuanced approach to election forecasting.
 While historical voting patterns provide a solid foundation, they may not fully capture the complexities of modern elections, where factors such as social media influence and voter sentiment play increasingly prominent roles.
-Incorporating these additional variables, particularly in battleground states, could refine the model’s predictive power and provide a more comprehensive understanding of the electoral landscape.
+Incorporating these additional variables, particularly in swing states, could refine the model’s predictive power and provide a more comprehensive understanding of the electoral landscape.
 
-For future iterations, we recommend expanding the model to include demographic data, such as age, education level, and income, which could reveal deeper insights into voter behavior.
+For future research, expanding the model to include demographic data, such as age, education level, and income could reveal a deeper analysis of voter behavior on a multi-sided scale.
 Additionally, real-time polling updates could offer a dynamic perspective, allowing the model to adapt to changes in public opinion as the election date approaches.
-Employing these enhancements would improve model reliability, particularly in closely contested states where the margin of error can significantly impact the final prediction.
+This variability suggests that further studies could benefit from integrating real-time data and employing Bayesian methodologies to account for evolving voter preferences.
+Such an approach could improve the accuracy of predictions, especially in regions with historically unpredictable outcomes.
+These adjustments could improve model's reliability, particularly in closely contested states where the margin of error can significantly impact the final prediction.
 
@@
 
-In cases of non-response, SurveyUSA attempts follow-up calls if interviews are interrupted by answering machines or busy signals.
-Weighting is applied to adjust for non-response bias, although this doesn't completely eliminate challenges posed by unreachable or unwilling participants.\
+Non-response in survey research is critical to address because it introduces potential bias, impacting the accuracy and representativeness of the results.
+When certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.
+For example, individuals who may be less available—such as those with demanding schedules, or limited access to technology—might be less likely to respond to a poll.
+Meanwhile, people with strong opinions or from specific demographic groups could be overrepresented in the results.
+This imbalance can create biased outcomes, where the poll data disproportionately reflects the views of a more vocal subset rather than an accurate cross-section of the entire population.\
+To mitigate non-response, SurveyUSA employs follow-up calls when interviews are interrupted by answering machines or busy signals.
+This extra effort helps reach individuals who may have been initially unavailable or hesitant, thereby improving the sample’s representativeness.
+Additionally, SurveyUSA applies weighting adjustments to balance demographic or behavioral tendencies that emerge from non-response patterns.
+While weighting can help realign the sample to match population characteristics more closely, it doesn’t fully eliminate the issue, as some individuals or groups may still remain unreachable or unwilling to participate.\
 
@@
 
+\newpage
+
 # Model details {#sec-model-details}
@@
 
-## Calculate Mean Squared Error and Mean Absolute Error on Test Data
+## Mean Squared Error and Mean Absolute Error on Test Data
 ```{r}
@@
 
-# Combine metrics into a data frame for display
+# Combine metrics into a data frame for display, rounding to 2 decimals
 metrics_df <- data.frame(
   Metric = c("Mean Squared Error (MSE)", "Mean Absolute Error (MAE)", "R-squared"),
-  Value = c(mse, mae, r_squared))
-
-# Display the metrics table using kable
+  Value = round(c(mse, mae, r_squared), 2)
+)
 kable(metrics_df)
@@
 
-# Create a data frame for additional statistics with consistent column names
+# Create a data frame for additional statistics with consistent column names and rounded to 2 decimals
 additional_stats <- data.frame(
-  Estimate = c(r_squared, adj_r_squared, f_statistic, p_value, residual_se),
+  Estimate = round(c(r_squared, adj_r_squared, f_statistic, p_value, residual_se), 2),
   `Std. Error` = NA,
@@
 colnames(additional_stats) <- colnames(coefficients_df)
+
+# Round coefficients to 2 decimal places in coefficients_df
+coefficients_df <- coefficients_df %>%
+  mutate(across(where(is.numeric), ~ round(., 2)))
 
@@
 #| echo: false
-#| fig-cap: Correlation Matrix of "Numeric Grade", "Sample Size", "Transparency Score"and "Days Until Election"
+#| fig-cap: Correlation Matrix of `Numeric Grade`, `Sample Size`, `Transparency Score` and `Days Until Election`
 #| warning: false
@@
 
-@fivethirty provides the data. @tidyverse, @ggplot, @knitr
+@fivethirty provides the data. @tidyverse, @ggplot2, @knitr
+This project was made possible by a variety of R packages that provided essential tools and functionality.
+We thank the @tidyverse and @ggplot2 teams for their extensive suite of tools for data manipulation and visualization, which were instrumental in data cleaning and graphing.
+We also acknowledge @usmap for its support in creating U.S.
+geographic visualizations, and @corrplot for facilitating clear, informative correlation plots.
+Finally, @arrow was crucial for efficient data storage and handling with Parquet files, ensuring data integrity throughout the project.
+We are grateful to the developers and maintainers of these packages for their contributions to open-source software, which greatly enhanced the scope and depth of our analysis.
 

### 2024-11-01 paper/paper.qmd
Add references in Appendix B and update Reference bib

@@
 ## Objective and Overview
-The goal of this survey methodology is to accurately forecast the outcome of the U.S.
-presidential election by collecting high-quality, representative data from a diverse set of respondents across the country.
-With a budget of \$100,000, this methodology incorporates sophisticated sampling techniques, robust respondent recruitment strategies, and rigorous data validation protocols.
-The approach is designed to maximize accuracy, reduce bias, and account for various demographic, geographic, and political factors that influence voting behavior.
+The primary goal of this survey methodology is to forecast the outcome of the U.S.
+presidential election by collecting high-quality, representative data from a diverse cross-section of American voters.
+Given a budget of $100,000, this methodology leverages sophisticated sampling techniques, effective respondent recruitment strategies, and robust data validation protocols to ensure maximum accuracy and minimal bias.
+This approach is designed to account for demographic, geographic, and political factors that can influence voting behavior, thereby enhancing the reliability of predictions [@fivethirty; @pewresearch].
 
 ## Core Objectives
-* Obtain a representative sample of the U.S. electorate.
-* Ensure data quality through rigorous validation.
-* Leverage statistical modeling and poll aggregation for an accurate prediction.
+* Obtain a representative sample of the U.S. electorate, with demographic diversity mirroring national voting patterns.
+* Ensure data quality through rigorous validation processes, including screening and cross-verification.
+* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling [@silver_nytimes].
 
 ## Sampling Strategy
-The sampling strategy is designed to ensure that the survey reaches a broad, representative section of the voting population.
-To achieve this, we will use **stratified random sampling** combined with **quota sampling** for key demographics.
-This ensures that each important subgroup within the population is adequately represented.
+Our sampling strategy combines **stratified random sampling** with **quota sampling** to ensure broad representation across key demographics.
+This method has been shown to improve the accuracy of electoral predictions by reducing demographic and geographic sampling bias [@fivethirty].
 
@@
 * **Geographic Region**: Northeast, Midwest, South, West
+
+This stratification aligns with best practices in survey sampling, allowing for improved accuracy and generalizability in election forecasting [@pewresearch].
 
@@
 ## Recruitment Strategy
-To maximize respondent diversity and ensure accurate sampling, the survey will employ **multi-channel recruitment**:
+Recruitment is executed through  **multi-channel outreach**, combining digital advertisements, email outreach, and partnerships with civic organizations.
+This diverse recruitment strategy helps to capture a representative sample and has been identified as a best practice in survey methodologies [@pewresearch].
 
@@
 
+These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @silver_nytimes].
+
 ## Poll Aggregation and Data Analysis
 ### Poll Aggregation
-This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach.
+This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@silver_nytimes].
 
@@
 The survey will be implemented via **Google Forms**, which offers a cost-effective platform for data collection.
-You can access the survey at the following link: [Google Form Survey](https://forms.gle/XxtMTMc45d6VzNuy8)
+You can access the survey at the following link: [Google Form Survey](https://forms.gle/sAxVuk3n9gV8e2odA)
 

### 2024-11-01 paper/paper.qmd
Update the caption for graphs and citation for Appendix A

@@
 
+## Estimand
+
 # Data {#sec-data}
@@
 
-This study uses R packages [@citeR] to clean and analyz the dataset , including libraries from tidyverse [], ggplot2[].
+This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2[@ggplot2], knitr[@knitr],usmap[@usmap], corrplot[@corrplot], and arrow [@arrow].
 
@@
 
-The outcome variable of interest for this research is the percentage, representing the level of public support for Donald Trump.
-The distribution in @fig-pct indicates that most observations cluster around a support percentage of approximately 48%, suggesting moderate backing from the electorate.
-Additionally, a smaller proportion of polls show support exceeding 55%, indicating that while Trump has a core base, many voters remain either indifferent or opposed to him.
+The outcome variable of interest for this research is the percentage representing the level of public support for Donald Trump.
+The distribution is shown in @fig-pct, where the x-axis represents the support percentage, ranging from approximately 20% to 70%, and the y-axis displays the count of poll surveys reporting each support level.
+The distribution reveals that most observations cluster around a support percentage of approximately 48%, indicating a substantial level of backing from the electorate.
+Additionally, a smaller proportion of polls show support exceeding 55%, suggesting that while Trump has a core base, many voters remain either indifferent or opposed to him.
+This visualization provides insight into both the concentration and variability of support within the surveyed population.
 
@@
 #| label: fig-pct
-#| fig-cap: Distribution of Support (percent) for Donald Trump
+#| fig-cap: Distribution of Support for Donald Trump in Percentage Across Poll Survey Responses
 #| echo: false
@@
 ggplot(analysis_data, aes(x = percent)) +
-  geom_histogram(binwidth = 2, fill = "green", color = "black", alpha = 0.7) +
-  labs(title = "Distribution of Support (percent) for Donald Trump", x = "Support Percentage (percent)", y = "Count") +
+  geom_histogram(binwidth = 2, fill = "skyblue", color = "black", alpha = 0.7) +
+  labs(x = "Percentage of Respondents Supporting Donald Trump (%)", 
+       y = "Count of Poll Surveys") +
   theme_minimal()
@@
 A grade of 0 indicates a low-quality poll, while a grade of 3 signifies a high-quality pollster.
-After filtering for pollsters with a numeric grade higher than 2.5, we identified a total of 30 distinct pollsters, with half of them scoring between 2.6 and 2.8, as shown in @fig-numeric-grade .
+After filtering for pollsters with a numeric grade higher than 2.5, we identified a total of 30 distinct pollsters.
+The distribution shows that grades cluster around 2.6, 2.8, and 2.9, with fewer polls receiving grades of 2.7 and 3.0, as shown in @fig-numeric-grade .
 
@@
 #| label: fig-numeric-grade
-#| fig-cap: Distribution of Numeric Grades (2.6 to 3.0)
+#| fig-cap: Distribution of Numeric Grades Across Polls (2.6 to 3.0)
 #| echo: false
@@
        aes(x = numeric_grade)) + 
-    geom_histogram(binwidth = 0.1, fill = "green", color = "black", alpha = 0.7) + 
+    geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black", alpha = 0.7) + 
     scale_x_continuous(breaks = seq(2.5, 3.0, by = 0.1)) + 
     scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) + 
-    labs(title = "Distribution of Numeric Grades (2.6 to 3.0)", 
-         x = "Numeric Grade", 
-         y = "Count of Distinct Polls") + 
+    labs(x = "Numeric Grade for Poll Quality", 
+         y = "Count of Distinct Pollsters Receiving Each Grade") + 
     theme_minimal()
@@
 #| label: fig-sample-size
-#| fig-cap: Distribution of Sample Size
+#| fig-cap: Distribution of Sample Sizes Across Poll Surveys
 #| echo: false
@@
 ggplot(analysis_data %>% filter(sample_size < 3000), aes(x = sample_size)) +
-  geom_histogram(binwidth = 100, fill = "green", color = "black", alpha = 0.7) +
-  labs(title = "Distribution of Sample Size", x = "Sample Size", y = "Count") +
+  geom_histogram(binwidth = 100, fill = "skyblue", color = "black", alpha = 0.7) +
+  labs(x = "Sample Size of Poll (Number of Respondents)",
+       y = "Count of Distinct Polls with Each Sample Size") +
   theme_minimal()
@@
 #| label: fig-transparency-score
-#| fig-cap: Distribution of Transparency Score
+#| fig-cap: Distribution of Transparency Scores Across Polls
 #| echo: false
@@
        aes(x = transparency_score)) + 
-  geom_histogram(binwidth = 1, fill = "green", color = "black", alpha = 0.7) + 
+  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) + 
   scale_x_continuous(breaks = 3:10) +
   scale_y_continuous(breaks = seq(0, max(summary_data$count), by = 1)) +  
-  labs(title = "Distribution of Transparency Score", x = "Transparency Score", y = "Count of Distinct Polls") + 
+  labs(x = "Transparency Score of Poll", 
+       y = "Count of Distinct Pollsters with Each Transparency Score") + 
   theme_minimal()
@@
 
-The **days until election** represents the remaining time leading up to the final election day.
-As shown in the figure, the support percentage for Donald Trump fluctuated over time, with a slightly downward trend as the election approached, as indicated by the dashed trend line.
-This suggests that while public opinion varied significantly, there was a decrease in support as election day approached.
+The days until election represents the remaining time leading up to the final election day.
+This variable is calculated by finding the difference between the end date of each poll survey and the final election date, which is November 5, 2024.
+
+As shown in the @fig-end-date, the support percentage for Donald Trump fluctuated over time, with a slight upward trend as the election approached, indicated by the dashed trend line.
+This suggests that public opinion varied throughout the period, and Trump’s support percentage experienced an increase as election day drew closer.
+However, it still remained below 50%.
 This trend highlights the importance of monitoring real-time polling data, as sentiment may shift in the critical months leading up to a closely contested election.
@@
 #| label: fig-end-date
-#| fig-cap: Trend of Support Percentage for Donald Trump Over Days Until Election.
-Fluctuations in support levels are observed as the election approaches, with a slight downward trend indicated by the dashed curve.
+#| fig-cap: Trend of Support Percentage for Donald Trump Over Days Until Election
 #| echo: false
@@
     geom_line(color = "skyblue", size = 1) + 
-    geom_smooth(method = "loess", color = "pink", linetype = "dashed", size = 1) + 
+    geom_smooth(method = "loess", color = "red", linetype = "dashed", size = 1) + 
     labs(x = "Days Until Election", y = "Support Percentage") + 
@@
 
+## Model Selection
 To model Donald Trump’s polling percentages over time, we used a multiple linear regression framework, which estimates the relationship between polling percentages and various predictors by fitting a linear equation to the data.
@@
 #| label: tbl-summary-model
-#| tbl-cap: Regression Model Summary Table
+#| tbl-cap: Regression Model Summary Table（Display the first 10 rows）
 #| warning: false
@@
 # Extract the coefficients to form a table
-coefficients_table <- summary$coefficients
+coefficients_table <- summary$coefficients[, 1:3]
 
@@
 ## Predicted Electoral Outcomes by State
-The following table (@tbl-missing) serves as a supplement to the predicted outcomes, filling in the gaps for states where the model couldn’t provide predictions.
+The table in the [Appendix -@tbl-missing-states] serves as a supplement to the predicted electoral outcomes by state, filling in the gaps for states where the model couldn’t provide predictions.
 It allows for a complete view of electoral projections by assigning a likely outcome in each missing state based on historical data.
@@
 
-```{r}
+The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S.
+Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
+The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois.
+However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
+
+```{r fig-statemap}
 #| echo: false
-#| label: tbl-missing
-#| tbl-cap: Missing States with Predicted Winner Based on Historical Lean
+#| label: fig-statemap
+#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
 #| warning: false
 #| message: false
+
 # Create the data frame with missing states, electoral votes, and predicted winner based on historical lean
@@
 
-# Display the table with kable
-kable(missing_states, col.names = c("State", "Electoral Votes", "Prediction Based on Historical Lean"))
-```
-
-The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S.
-Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
-The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois.
-However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
-
-```{r fig-statemap}
-#| echo: false
-#| label: fig-statemap
-#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
-#| warning: false
-#| message: false
-
+# Ensure column names match in the original dataset before merging
 state_predictions <- merge(state_predictions, missing_states, by = "state", all = TRUE)
 
+# Update trump_electoral_votes and harris_electoral_votes columns based on historical lean
 state_predictions <- state_predictions %>%
@@
 Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels.
-The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms.
+The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms[@surveyusa_website].
 
@@
 SurveyUSA employs a mixed-method approach to recruitment, including online panels, telephone calls, and a text-to-web method.
-Some respondents are recruited through Random Digit Dialing (RDD) using telephone samples purchased from Aristotle, while others, who do not use home telephones, are invited to complete the survey on an electronic device such as a phone or tablet.
-Respondents from non-probability online panels are selected randomly by Cint/Lucid Holdings LLC.\
+Some respondents are recruited through Random Digit Dialing (RDD) using telephone samples purchased from Aristotle.
+RDD allows them to generate phone numbers at random, helping avoid biases that can result from using pre-existing contact lists.
+For those who do not use home telephones, SurveyUSA invite them to complete the survey on an electronic device such as a phone or tablet.
+Respondents from non-probability online panels are selected randomly by Cint Lucid Holdings LLC [@surveyusa_methodology].\
 
@@
 Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population.
-Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects.\
+Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects.[@surveyusa_methodology]\
 
-* **Advantages:**
-
-The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population.
+* **Advantages:** The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population.
 Furthermore, reweighting the data according to U.S.
@@
 
-* **Disadvantages:**
-
-Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
+* **Disadvantages:** Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
 Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.\
@@
 
-Non-response in survey research is critical to address because it introduces potential bias, impacting the accuracy and representativeness of the results.
-When certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.
-For example, individuals who may be less available—such as those with demanding schedules, or limited access to technology—might be less likely to respond to a poll.
+Non-response in survey research is critical to address because it introduces potential bias, impacting the accuracy and representativeness of the results.As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
 Meanwhile, people with strong opinions or from specific demographic groups could be overrepresented in the results.
 This imbalance can create biased outcomes, where the poll data disproportionately reflects the views of a more vocal subset rather than an accurate cross-section of the entire population.\
+
 To mitigate non-response, SurveyUSA employs follow-up calls when interviews are interrupted by answering machines or busy signals.
-This extra effort helps reach individuals who may have been initially unavailable or hesitant, thereby improving the sample’s representativeness.
+This additional effort helps reach individuals who may have been initially unavailable or hesitant, thereby improving the sample’s representativeness.
+This method aligns with one of the practical strategies discussed by @groves2012nonresponse to reduce non-response.
+However, SurveyUSA need to be caution that excessive or overly persistent follow-ups can lead to respondent discomfort, raise ethical concerns, and introduce potential biases if respondents feel obligated or pressured to participate.
+
 Additionally, SurveyUSA applies weighting adjustments to balance demographic or behavioral tendencies that emerge from non-response patterns.
-While weighting can help realign the sample to match population characteristics more closely, it doesn’t fully eliminate the issue, as some individuals or groups may still remain unreachable or unwilling to participate.\
+As discussed by @peytchev2013consequences, while weighting can help realign the sample to more closely match population characteristics, it doesn’t fully eliminate the issue, as certain individuals or groups may remain unreachable or unwilling to participate, especially in cases where key variables are missing.
+
+Other approaches that SurveyUSA could consider include imputation, as discussed in paper published by @bethlehem2010selection.
+This method estimates missing responses based on available data, helping to fill gaps and reduce bias in cases of partial non-response.
 
@@
 
+## Missing States with Predicted Winner Based on Historical Lean
+```{r}
+#| echo: false
+#| label: tbl-missing-states
+#| tbl-cap: Missing States with Predicted Winner Based on Historical Lean
+#| warning: false
+#| message: false
+
+# Display the table with kable
+kable(missing_states, 
+      col.names = c("State", "Electoral Votes", "Prediction Based on Historical Lean"),
+      align = "c")  # Center align all columns
+
+```
+
 \newpage

### 2024-11-01 paper/paper.qmd
Update summary table.

@@
 #| message: false
-
 # Get summary of the regression model
@@
 coefficients_df <- as.data.frame(model_summary$coefficients)
-colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")
+
+# Set column names for coefficients_df
+colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value")[1:ncol(coefficients_df)]
 
@@
 f_statistic <- model_summary$fstatistic[1]
-p_value <- pf(f_statistic, model_summary$fstatistic[2], model_summary$fstatistic[3], lower.tail = FALSE)
 residual_se <- model_summary$sigma
@@
 additional_stats <- data.frame(
-  Estimate = round(c(r_squared, adj_r_squared, f_statistic, p_value, residual_se), 2),
+  Estimate = round(c(r_squared, adj_r_squared, f_statistic, residual_se), 2),
   `Std. Error` = NA,
   `t value` = NA,
-  `Pr(>|t|)` = NA,
-  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "F-statistic p-value", "Residual Std. Error")
+  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "Residual Std. Error")
 )
@@
 # Ensure column names are identical between data frames
-colnames(additional_stats) <- colnames(coefficients_df)
+additional_stats <- additional_stats[, colnames(coefficients_df), drop = FALSE]
+
+# Load dplyr
+library(dplyr)
 
@@
 # Display the full summary table using kable
+library(knitr)
 kable(full_summary_df)
@@
 #| echo: false
-#| fig-cap: Correlation Matrix of `Numeric Grade`, `Sample Size`, `Transparency Score` and `Days Until Election`
+#| fig-cap: Correlation Matrix of Numeric Grade, Sample Size, Transparency Score and `Days Until Election`
 #| warning: false
@@
       col.names = c("State", "Electoral Votes", "Prediction Based on Historical Lean"),
-      align = "c")  # Center align all columns
+      align = "c")
 
@@
 # Acknowledgements
-@citeR
-Thanks to Open AI and ChatGPT 4.0 is used to write the analysis of the paper.
 
-@fivethirty provides the data. @tidyverse, @ggplot2, @knitr
-This project was made possible by a variety of R packages that provided essential tools and functionality.
-We thank the @tidyverse and @ggplot2 teams for their extensive suite of tools for data manipulation and visualization, which were instrumental in data cleaning and graphing.
+Thanks to Open AI and ChatGPT 4.0 is used to write the paper.
+This project utilized R @citeR and a variety of R packages that provided essential tools and functionality.
+We thank the @tidyverse, @ggplot2 and @knitr teams for their extensive suite of tools for data manipulation and visualization, which were instrumental in data cleaning and graphing.
 We also acknowledge @usmap for its support in creating U.S.
 geographic visualizations, and @corrplot for facilitating clear, informative correlation plots.
-Finally, @arrow was crucial for efficient data storage and handling with Parquet files, ensuring data integrity throughout the project.
-We are grateful to the developers and maintainers of these packages for their contributions to open-source software, which greatly enhanced the scope and depth of our analysis.
+Finally, @arrow was crucial for efficient data storage and handling with Parquet files.
+We are grateful to the developers and maintainers of these packages for their contributions to open-source software.
 

### 2024-11-01 paper/paper.qmd
Modify reference

@@
 * Ensure data quality through rigorous validation processes, including screening and cross-verification.
-* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling [@silver_nytimes].
+* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling
 
@@
 
-These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @silver_nytimes].
+These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @pew_survey_methodology].
 
@@
 ### Poll Aggregation
-This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@silver_nytimes].
+This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@pew_survey_methodology].
 

### 2024-11-01 paper/paper.qmd
Update estimand part.

--- 2024-11-01 paper/paper.qmd
@@
 ## Estimand
+In this analysis, the estimand is the true effect of polling factors on the projected support for Trump and Harris in the 2024 U.S.
+election.
+Specifically, this effect encompasses how variables like poll quality, transparency, sample size, and timing influence predicted vote percentages for Kamala Harris and Donald Trump across states.
+This build-up of estimand ensures consistency by clarifying that our target effect is the overall impact of these factors on candidates’ state-by-state electoral prospects.
+The estimand guides the model design and interpretation to achieve our goal of predicting the election outcome.
 
@@
 #| message: false
+
 # Get summary of the regression model
@@
 coefficients_df <- as.data.frame(model_summary$coefficients)
-
-# Set column names for coefficients_df
-colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value")[1:ncol(coefficients_df)]
+colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")
 
@@
 additional_stats <- data.frame(
-  Estimate = round(c(r_squared, adj_r_squared, f_statistic, residual_se), 2),
+  Estimate = round(c(r_squared, adj_r_squared, f_statistic, p_value, residual_se), 2),
   `Std. Error` = NA,
   `t value` = NA,
-  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "Residual Std. Error")
+  `Pr(>|t|)` = NA,
+  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "F-statistic p-value", "Residual Std. Error")
 )
@@
 # Ensure column names are identical between data frames
-additional_stats <- additional_stats[, colnames(coefficients_df), drop = FALSE]
-
-# Load dplyr
-library(dplyr)
+colnames(additional_stats) <- colnames(coefficients_df)
 
@@
 # Display the full summary table using kable
-library(knitr)
-kable(full_summary_df)
+kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])
 ```

### 2024-11-01 paper/paper.qmd
Rendered paper updated.

@@
 f_statistic <- model_summary$fstatistic[1]
+p_value <- pf(f_statistic, model_summary$fstatistic[2], model_summary$fstatistic[3], lower.tail = FALSE)
 residual_se <- model_summary$sigma
@@
 
+# Load necessary library
+library(dplyr)
+
 # Round coefficients to 2 decimal places in coefficients_df
@@
 
-# Display the full summary table using kable
+# Display the full summary table using kable, excluding "F-statistic p-value" row
+library(knitr)
 kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])

### 2024-11-01 paper/paper.qmd
Some small revisions and add llm usages

@@
 
-This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2[@ggplot2], knitr[@knitr],usmap[@usmap], corrplot[@corrplot], and arrow [@arrow].
+This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2[@ggplot2], knitr[@knitr],usmap[@usmap], corrplot[@corrplot], arrow [@arrow].
 
@@
 
-The dataset used in this analysis originates from FiveThirtyEight, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately.
+The dataset used in this analysis originates from @fivethirty, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately.
 To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset.
@@
 The distribution is shown in @fig-pct, where the x-axis represents the support percentage, ranging from approximately 20% to 70%, and the y-axis displays the count of poll surveys reporting each support level.
+The red dashed line at the 50% mark acts as a benchmark, indicating the threshold needed for majority support.
+
 The distribution reveals that most observations cluster around a support percentage of approximately 48%, indicating a substantial level of backing from the electorate.
@@
 #| label: fig-pct
-#| fig-cap: Distribution of Support for Donald Trump in Percentage Across Poll Survey Responses
+#| fig-cap: Distribution of Support for Donald Trump in Percentage Across Poll Survey Responses.
+The red dashed line at the 50% mark serves as a reference point, highlighting the threshold for majority support.
 #| echo: false
@@
   geom_histogram(binwidth = 2, fill = "skyblue", color = "black", alpha = 0.7) +
+  geom_vline(xintercept = 50, linetype = "dashed", color = "red") +
   labs(x = "Percentage of Respondents Supporting Donald Trump (%)",
@@
 #| label: fig-end-date
-#| fig-cap: Trend of Support Percentage for Donald Trump Over Days Until Election
+#| fig-cap: Trend of Support Percentage for Donald Trump Over Days Until Election.
+The red dashed line indicates the average support rate for Donald Trump at that point in time.
+Renew the data to the October 24.2024
 #| echo: false
@@
 Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population.
-Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects.[@surveyusa_methodology]\
+Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects[@surveyusa_methodology].\
 
@@
 ## Model Summary
+
 ```{r}
@@
 
-# Load necessary library
-library(dplyr)
-
 # Round coefficients to 2 decimal places in coefficients_df
@@
 kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])
+
+# Display the full summary table using kable
+kable(full_summary_df)
+
 ```
@@
 Thanks to Open AI and ChatGPT 4.0 is used to write the paper.
-This project utilized R @citeR and a variety of R packages that provided essential tools and functionality.
+This project utilized @citeR and a variety of R packages that provided essential tools and functionality.
 We thank the @tidyverse, @ggplot2 and @knitr teams for their extensive suite of tools for data manipulation and visualization, which were instrumental in data cleaning and graphing.

### 2024-11-01 paper/paper.qmd
Modify Prose over the paper

@@
 The 2024 U.S.
-Presidential Election is set to unfold in a climate of heightened political polarization, economic challenges, and demographic shifts, making it a pivotal event in shaping America's future.
-Predicting the outcome of this election is crucial for gaining insights into potential changes in political leadership and policy directions.
-Polling data has traditionally served as a primary tool for gauging voter sentiment; however, recent election cycles have exposed limitations in polling accuracy due to biases, non-response issues, and variations in poll quality.
-To address these challenges, this study proposes a model that incorporates these factors to enhance the reliability of election forecasts.
-
-This paper develops a prediction model aimed at forecasting the electoral outcomes between Kamala Harris and Donald Trump in the 2024 election.
+Presidential Election will occur in a context of intensified political polarization, economic challenges, and demographic shifts, positioning it as a significant event in shaping America's future.
+Accurately forecasting this election’s outcome is essential for understanding potential shifts in political leadership and policy direction.
+Polling data has traditionally been a primary tool for measuring voter sentiment; however, recent election cycles have revealed limitations in polling accuracy due to biases, non-response, and variations in poll quality.
+This study proposes a model that addresses these issues to improve the reliability of election forecasts.
+
+This paper develops a predictive model to forecast the electoral outcomes between Kamala Harris and Donald Trump in the 2024 election.
 Using a multiple linear regression framework, we analyze aggregated polling data across U.S.
 states, incorporating factors such as poll quality, transparency, sample size, geographic indicators, and poll timing.
-By integrating these variables, our model seeks to provide a nuanced forecast that accounts for regional differences and methodological variations across polls, offering a comprehensive view of the projected support for each candidate.
-
-Our findings suggest a competitive election landscape, with Harris showing strong prospects in key battleground states while Trump retains support in traditional Republican strongholds.
-These projections underscore the enduring influence of geographic voting patterns and the impact of polling methodology on electoral forecasting.
-The study provides valuable insights for political analysts, campaign strategists, and the public, contributing to a better understanding of how polling data can be utilized to anticipate electoral outcomes.
-
-The remainder of this paper is organized as follows: @sec-data describes the dataset and the preprocessing steps involved in preparing data for the model.
-@sec-model explains the modeling approach, including the selection of predictors and the structure of the regression model.
-@sec-results presents the primary findings, highlighting state-by-state predictions and overall electoral projections.
-Section @sec-discussion discusses the implications, limitations, and future directions for this analysis.
-The Appendix section provides supplementary information on methodology, diagnostics, technical details of the model setup, acknowledgments, and references.
+By integrating these variables, the model aims to produce a detailed forecast that accounts for regional differences and methodological variations, offering a thorough view of projected support for each candidate.
+
+The findings indicate a competitive election landscape, with Harris showing strong prospects in key battleground states, while Trump retains support in traditional Republican strongholds.
+These projections highlight the persistent influence of geographic voting patterns and the importance of polling methodology in electoral forecasting.
+This study offers valuable information for political analysts, campaign strategists, and the public, enhancing the understanding of how polling data can inform electoral outcome predictions.
+
+The remainder of this paper is organized as follows: @sec-data describes the dataset and the preprocessing steps for model preparation.
+@sec-model explains the modeling approach, including predictor selection and the regression model structure.
+@sec-results presents the primary findings, detailing state-by-state predictions and overall electoral projections.
+@sec-discussion discusses the implications, limitations, and potential directions for future research.
+The Appendix provides supplementary information on methodology, diagnostics, technical details of the model setup, acknowledgments, and references.
 
@@
 To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset.
-Specifically, each poll must disclose crucial information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details.
+Specifically, each poll must disclose important information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details.
 These details encompass the polling medium (e.g., phone, online), use of verified voter files, demographic weighting criteria, and any adjustments applied to reflect a representative sample.
@@
 
-Once deemed credible, polls are incorporated into the FiveThirtyEight database.
-These polls then contribute to polling averages, forecast models, and political coverage, which depend heavily on the quality and reliability of public opinion data.
-This meticulous selection process ensures that the dataset captures a comprehensive and nuanced view of public sentiment, providing an accurate reflection of behavioral trends and preferences over time.
+Once verified as credible, polls are incorporated into the FiveThirtyEight database.
+These polls then contribute to polling averages, forecast models, and political analysis, all of which rely on high-quality, reliable public opinion data.
+This careful selection process ensures that the dataset reflects a thorough and detailed view of public sentiment, accurately capturing behavioral trends and preferences over time.
 
@@
 
-The distribution reveals that most observations cluster around a support percentage of approximately 48%, indicating a substantial level of backing from the electorate.
-Additionally, a smaller proportion of polls show support exceeding 55%, suggesting that while Trump has a core base, many voters remain either indifferent or opposed to him.
-This visualization provides insight into both the concentration and variability of support within the surveyed population.
+The distribution shows that most observations cluster around a support level of approximately 48%, indicating significant backing from the electorate.
+A smaller portion of polls report support above 55%, suggesting that while Trump has a core base, many voters remain either undecided or opposed.
+This visualization highlights both the concentration and variability of support within the surveyed population.
 
@@
 
-The sample size indicates the number of respondents in each poll.
-The distribution in @fig-sample-size exhibits a right-skewed shape, suggesting that there are more observations with smaller sample sizes compared to larger ones.
-The peak of the distribution is around 1,000, indicating that this is the most common sample size used in the polls.
-Overall, the sample size data highlights that each poll contains a sufficient number of respondents to provide reliable insights.
+The sample size represents the number of respondents in each poll.
+The distribution in @fig-sample-size is right-skewed, indicating a higher frequency of polls with smaller sample sizes.
+The peak occurs around 1,000 respondents, marking this as the most common sample size among the polls.
+Overall, the data suggests that each poll includes enough respondents to yield reliable information.
 
@@
 However, it still remained below 50%.
-This trend highlights the importance of monitoring real-time polling data, as sentiment may shift in the critical months leading up to a closely contested election.
+This trend highlights the importance of monitoring real-time polling data, as sentiment may shift in these months leading up to a closely contested election.
 
@@
 - California: Trump is predicted to receive 34.39% of the vote, resulting in a victory for Harris, who takes California's 55 electoral votes.
-- Florida: The model predicts a close race, with Trump at 48.89% of the vote, resulting in a Harris win in this critical battleground state.
+- Florida: The model predicts a close race, with Trump at 48.89% of the vote, resulting in a Harris win in this battleground state.
 
@@
 ## Predicted Electoral Outcomes by State
-The table in the [Appendix -@tbl-missing-states] serves as a supplement to the predicted electoral outcomes by state, filling in the gaps for states where the model couldn’t provide predictions.
-It allows for a complete view of electoral projections by assigning a likely outcome in each missing state based on historical data.
-This approach ensures every state is accounted for in the final electoral vote totals.
+The table in the [Appendix -@tbl-missing-states] supplements the predicted electoral outcomes by providing likely results for states where the model could not generate predictions.
+Using historical data to estimate outcomes for these missing states ensures a complete view of electoral projections and accounts for every state in the final electoral vote totals.
 
@@
 
-The analysis reveals that state-specific predictors, such as historical voting patterns and days until election day, are significant influencers of each candidate’s polling outcomes.
-Traditional Democratic strongholds like California and New York strongly favor Harris, while Republican-dominated states such as Alabama and Wyoming align with Trump.
-This distribution reflects enduring geographic voting patterns and underscores the role of regional party loyalty.
+The analysis shows that state-specific factors, such as historical voting patterns and days until election day, significantly influence each candidate’s polling outcomes.
+Traditional Democratic strongholds like California and New York favor Harris, while Republican-leaning states such as Alabama and Wyoming align with Trump.
+This distribution reflects persistent geographic voting patterns and highlights the impact of regional party loyalty.
 
@@
 
-The model also highlights the critical role of battleground states, with states such as Florida and Arizona predicted to lean toward Harris.
+The model also highlights the significant role of battleground states, with states such as Florida and Arizona predicted to lean toward Harris.
 The influence of these states, where margins are often narrow, emphasizes the importance of campaign efforts and voter mobilization in these regions.
@@
 
-Due to limited data available for predicting outcomes in every state, some state projections rely on historical voting patterns, with the assumption that these trends will persist.
-However, this approach may be challenged by the rapidly changing political landscape in the U.S., where evolving demographics and shifting public sentiment could lead to unexpected results.
+With limited data for predicting outcomes in every state, some projections are based on historical voting patterns, assuming these trends will continue.
+However, this approach may be affected by the changing political landscape in the U.S., where evolving demographics and shifting public sentiment could lead to unexpected results.
 
@@
 
-Non-response in survey research is critical to address because it introduces potential bias, impacting the accuracy and representativeness of the results.As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
+Non-response in survey research is important to address because it introduces potential bias, impacting the accuracy and representativeness of the results.As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
 Meanwhile, people with strong opinions or from specific demographic groups could be overrepresented in the results.
@@
 
-Other approaches that SurveyUSA could consider include imputation, as discussed in paper published by @bethlehem2010selection.
-This method estimates missing responses based on available data, helping to fill gaps and reduce bias in cases of partial non-response.
+Other approaches that SurveyUSA could consider include imputation, as discussed in the work by @bethlehem2010selection.
+This method estimates missing responses based on existing data, helping to address gaps and reduce bias in cases of partial non-response.
 
@@
 * **Negative Aspects:**
-Static options for party affiliation and ideology may fail to capture the nuances of respondents’ political beliefs. These rigid categories could oversimplify complex political identities.\
+Static options for party affiliation and ideology may overlook the subtleties of respondents' political beliefs. These fixed categories risk oversimplifying complex political identities.\
 
@@
 ## Objective and Overview
-The primary goal of this survey methodology is to forecast the outcome of the U.S.
-presidential election by collecting high-quality, representative data from a diverse cross-section of American voters.
-Given a budget of $100,000, this methodology leverages sophisticated sampling techniques, effective respondent recruitment strategies, and robust data validation protocols to ensure maximum accuracy and minimal bias.
+The primary goal of this survey methodology is to forecast the U.S.
+presidential election outcome by collecting representative data from a diverse cross-section of American voters.
+With a $100,000 budget, this methodology employs sampling techniques, effective recruitment strategies, and data validation protocols to ensure accuracy and minimize bias.
 This approach is designed to account for demographic, geographic, and political factors that can influence voting behavior, thereby enhancing the reliability of predictions [@fivethirty; @pewresearch].
@@
 * Obtain a representative sample of the U.S. electorate, with demographic diversity mirroring national voting patterns.
-* Ensure data quality through rigorous validation processes, including screening and cross-verification.
+* Ensure data quality through validation processes, including screening and cross-verification.
 * Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling
@@
 Our sampling strategy combines **stratified random sampling** with **quota sampling** to ensure broad representation across key demographics.
-This method has been shown to improve the accuracy of electoral predictions by reducing demographic and geographic sampling bias [@fivethirty].
+This method improves electoral prediction accuracy by reducing demographic and geographic sampling bias [@fivethirty].
 
@@
 Recruitment is executed through  **multi-channel outreach**, combining digital advertisements, email outreach, and partnerships with civic organizations.
-This diverse recruitment strategy helps to capture a representative sample and has been identified as a best practice in survey methodologies [@pewresearch].
+This recruitment strategy helps capture a representative sample and aligns with best practices in survey methodologies [@pewresearch].
 
@@
 ## Data Validation and Quality Assurance
-Maintaining data integrity and ensuring high-quality responses are critical to the accuracy of the election forecast.
+Maintaining data integrity and ensuring high-quality responses are important to the accuracy of the election forecast.
 Several measures will be put in place to validate responses and reduce noise in the dataset.
@@
 
-These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @pew_survey_methodology].
+These practices align with data integrity and quality control standards in electoral polling [@fivethirty; @pew_survey_methodology].
 
@@
 ### Poll Aggregation
-This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@pew_survey_methodology].
+This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) using a **poll-of-polls** approach to strengthen the forecast [@pew_survey_methodology].
 
@@
 
-Thank you for taking part in this survey aimed at predicting the outcome of the 2024 US Presidential election. Your insights are valuable to our research.
+Thank you for taking part in this survey aimed at predicting the outcome of the 2024 US Presidential election. Your voices are valuable to our research.
 
@@
 geographic visualizations, and @corrplot for facilitating clear, informative correlation plots.
-Finally, @arrow was crucial for efficient data storage and handling with Parquet files.
+Finally, @arrow was vital for efficient data storage and handling with Parquet files.
 We are grateful to the developers and maintainers of these packages for their contributions to open-source software.

### 2024-11-02 paper/paper.qmd
Modify Reference

@@
 
-This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2[@ggplot2], knitr[@knitr],usmap[@usmap], corrplot[@corrplot], arrow [@arrow].
+This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr],usmap [@usmap], corrplot [@corrplot], arrow [@arrow].
 
@@
 Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels.
-The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms[@surveyusa_website].
+The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms [@surveyusa_website].
 
@@
 Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population.
-Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects[@surveyusa_methodology].\
+Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects [@surveyusa_methodology].\
 

### 2024-11-02 paper/paper.qmd
Modify Idealized methodology

@@
 The primary goal of this survey methodology is to forecast the U.S.
-presidential election outcome by collecting representative data from a diverse cross-section of American voters.
-With a $100,000 budget, this methodology employs sampling techniques, effective recruitment strategies, and data validation protocols to ensure accuracy and minimize bias.
+presidential election outcome by collecting representative data from a diverse cross-section of American voters (the target population).
+The target population refers to the entire group about which we want to make predictions—in this case, eligible U.S.
+voters across all demographics.
+With a $100,000 budget, this methodology employs probability sampling techniques, effective recruitment strategies, and data validation protocols to ensure accuracy and minimize bias.
+Probability sampling ensures that every individual in the target population has a known, non-zero chance of selection, making the results statistically valid and generalizable to the broader population.
 This approach is designed to account for demographic, geographic, and political factors that can influence voting behavior, thereby enhancing the reliability of predictions [@fivethirty; @pewresearch].
@@
 ## Core Objectives
-* Obtain a representative sample of the U.S. electorate, with demographic diversity mirroring national voting patterns.
-* Ensure data quality through validation processes, including screening and cross-verification.
-* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling
+* Obtain a probability sample that represents the U.S.
+electorate, with demographic diversity reflecting national voting patterns.
+This helps ensure that conclusions drawn from the sample are applicable to the target population.
+* Ensure data quality through validation processes, including screening and cross-verification, to address potential errors and improve the accuracy of the data.
+* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling.
 
 ## Sampling Strategy
-Our sampling strategy combines **stratified random sampling** with **quota sampling** to ensure broad representation across key demographics.
-This method improves electoral prediction accuracy by reducing demographic and geographic sampling bias [@fivethirty].
+Our sampling strategy combines **stratified** random sampling with **quota sampling** to ensure broad representation across key demographics.
+Stratified random sampling involves dividing the target population into subgroups (strata) based on demographic characteristics, then randomly sampling from each stratum.
+This technique enhances the representativeness of the sample and improves prediction accuracy by reducing demographic and geographic sampling bias [@fivethirty].
 
@@
 
-This stratification aligns with best practices in survey sampling, allowing for improved accuracy and generalizability in election forecasting [@pewresearch].
+This stratification aligns with best practices in survey sampling, allowing for improved accuracy and generalizability in election forecasting by ensuring that subgroups are proportionately represented [@pewresearch].
 
@@
 A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1\% at a 95\% confidence level.
-This sample size will allow for detailed subgroup analysis (e.g., by state, demographic group), yielding statistically robust predictions.
+This sample size allows for detailed subgroup analysis (e.g., by state or demographic group), yielding statistically robust predictions that represent the target population.
 
@@
 Post-stratification weights will be applied to adjust for any oversampling or undersampling of specific demographic groups.
-For example, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.
+For instance, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.
+This weighting ensures that the final sample aligns closely with the demographic makeup of the target population.
 
@@
 Recruitment is executed through **multi-channel outreach**, combining digital advertisements, email outreach, and partnerships with civic organizations.
-This recruitment strategy helps capture a representative sample and aligns with best practices in survey methodologies [@pewresearch].
+This strategy is designed to capture a probability sample and follows best practices in survey methodologies to minimize non-response bias—errors that occur when certain groups in the target population are less likely to respond to the survey.
+Non-response matters because it can distort the results if certain demographics are underrepresented in the final data [@pewresearch].
 
@@
 * **Email Outreach**: If permissible, voter registration databases will be accessed to send email invitations to registered voters.
-* **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities will further boost respondent diversity.
-* **Incentives**: Each participant will be entered into a lottery with a chance to win a \$100 gift card to encourage participation.
+* **Partnerships with Civic Organizations**: Partnering with non-profits and civic organizations that engage diverse communities will help improve respondent diversity and reduce non-response bias.
+* **Incentives**: Each participant will be entered into a lottery with a chance to win a $100 gift card to encourage participation and mitigate non-response.
 
 ## Data Validation and Quality Assurance
-Maintaining data integrity and ensuring high-quality responses are important to the accuracy of the election forecast.
-Several measures will be put in place to validate responses and reduce noise in the dataset.
+Maintaining data integrity and ensuring high-quality responses are essential to the accuracy of the election forecast.
+Several measures will be implemented to validate responses and reduce noise in the dataset.
 
@@
 * **Email/Phone Verification**: Respondents will verify their email or phone number to ensure authenticity and prevent duplicate submissions.
-* **Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question. Responses completed suspiciously quickly will be flagged for review.
+* **Time on Task Monitoring**: The survey platform will monitor the time respondents spend on each question. Responses completed unusually quickly will be flagged for review.
 * **Voter Registration Cross-Check**: If feasible, respondents will be cross-referenced with voter registration records to ensure eligibility.
@@
 
-These practices align with data integrity and quality control standards in electoral polling [@fivethirty; @pew_survey_methodology].
+These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @pew_survey_methodology].
 
@@
 ### Poll Aggregation
-This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) using a **poll-of-polls** approach to strengthen the forecast [@pew_survey_methodology].
+This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) using a poll-of-polls approach to strengthen the forecast [@pew_survey_methodology].
 
@@
 **Bayesian hierarchical models** will account for variability across different states, demographics, and regions.
-This will allow for modeling the popular vote and potentially translating it into **Electoral College predictions**.
+This approach allows us to model the popular vote and potentially translate it into **Electoral College predictions**.
 

### 2024-11-02 paper/paper.qmd
Modify Estimand

@@
 
-## Estimand
-In this analysis, the estimand is the true effect of polling factors on the projected support for Trump and Harris in the 2024 U.S.
+In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S.
 election.
-Specifically, this effect encompasses how variables like poll quality, transparency, sample size, and timing influence predicted vote percentages for Kamala Harris and Donald Trump across states.
-This build-up of estimand ensures consistency by clarifying that our target effect is the overall impact of these factors on candidates’ state-by-state electoral prospects.
-The estimand guides the model design and interpretation to achieve our goal of predicting the election outcome.
+Specifically, it reflects how variables such as poll quality, transparency, sample size, and timing influence the predicted vote percentages for Kamala Harris and Donald Trump across states.
+Defining the estimand clearly ensures consistency in the analysis by guiding model design and interpretation, preventing unintended shifts in focus due to minor methodological changes.
 

### 2024-11-02 paper/paper.qmd
Modify Measurement part

@@
 
-The dataset used in this analysis originates from @fivethirty, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately.
-To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset.
-Specifically, each poll must disclose important information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details.
-These details encompass the polling medium (e.g., phone, online), use of verified voter files, demographic weighting criteria, and any adjustments applied to reflect a representative sample.
-
-Polls are rigorously verified, and those that do not meet these requirements are excluded from the dataset.
-For instance, polls categorized as nonscientific, those that merge data from multiple unrelated sources, and those conducted by hobbyists or unverified entities are filtered out to prevent data quality compromise.
-
-Once verified as credible, polls are incorporated into the FiveThirtyEight database.
-These polls then contribute to polling averages, forecast models, and political analysis, all of which rely on high-quality, reliable public opinion data.
-This careful selection process ensures that the dataset reflects a thorough and detailed view of public sentiment, accurately capturing behavioral trends and preferences over time.
+In this analysis, the goal is to convert individual polling data, which reflects voter sentiment before Election Day, into an estimate of the overall electoral support for each candidate.
+This process involves systematically capturing public opinion about voting intentions and translating it into structured data that can reliably forecast electoral college outcomes.
+
+The dataset originates from @fivethirty, a trusted source known for its rigorous standards in polling data collection.
+Only polls meeting specific quality criteria are included, ensuring that data represents a broad cross-section of likely voters across the U.S.
+Each poll must disclose essential details, including the pollster’s name, survey dates, sample size, and methodological information.
+This transparency in methodology includes aspects like the polling medium (phone, online), use of voter files, demographic weighting, and any adjustments made to reflect a representative sample.
+These steps help ensure that the recorded data accurately captures respondents' voting intentions.
+
+Once these polls pass quality checks, they are integrated into the FiveThirtyEight database, where they contribute to aggregated polling averages and forecast models.
+Poll results are recorded as percentages reflecting the level of support for each candidate, essentially quantifying voter sentiment.
+However, moving from these individual opinions to a reliable state-by-state and national forecast requires addressing inherent challenges, such as demographic imbalances and geographic biases.
+To mitigate these, demographic weights are applied, aligning sample composition with actual population distributions.
+
+The measurement approach also includes recency adjustments to account for the time since each poll was conducted, as opinions can shift rapidly closer to Election Day.
+This approach, combined with selective inclusion criteria, ensures that the dataset reflects a consistent and structured view of voter sentiment across various demographic and regional groups, bridging the gap between initial polling data and final election predictions.
 

### 2024-11-02 paper/paper.qmd
Revise title, subtitle, abstract, measurement.

--- 2024-11-02 paper/paper.qmd
@@
 ---
-title: "Predicting Kamala Harris's Victory in the 2024 US Election"
-subtitle: "Poll Data Predicts Kamala Harris Win with 387 Electoral Votes"
+title: "Forecasting the 2024 U.S. Presidential Election"
+subtitle: "Predicting Kamala Harris’s Path to Victory: A Poll-Based Projection Under Electoral Uncertainty"
 author: 
@@
 toc: true
-abstract: "This study provides a prediction for the 2024 U.S.
-presidential election, presenting potential outcomes based on a state-by-state electoral vote analysis.
+abstract: "This study provides a predictive analysis of the 2024 U.S.
+presidential election, presenting potential outcomes through a state-by-state evaluation of electoral votes.
 These projections can guide campaign strategies and influence public discourse.
-The results suggest Kamala Harris will secure a win with 387 electoral votes, significantly surpassing the 270 needed for victory.
+The results suggest Kamala Harris will secure a win with 387 electoral votes, significantly surpassing the 270 needed for victory and indicating a landslide.
 In contrast, Donald Trump is predicted to receive 151 electoral votes."
@@
 
+## Estimand
 In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S.
@@
 
+###
+
 # Data {#sec-data}
@@
 
-## Data Measurement and Considerations
-
-The dataset used in this analysis originates from @fivethirty, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately.
-To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset.
-Specifically, each poll must disclose important information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details.
-These details encompass the polling medium (e.g., phone, online), use of verified voter files, demographic weighting criteria, and any adjustments applied to reflect a representative sample.
-
-Polls are rigorously verified, and those that do not meet these requirements are excluded from the dataset.
-For instance, polls categorized as nonscientific, those that merge data from multiple unrelated sources, and those conducted by hobbyists or unverified entities are filtered out to prevent data quality compromise.
-
-Once verified as credible, polls are incorporated into the FiveThirtyEight database.
-These polls then contribute to polling averages, forecast models, and political analysis, all of which rely on high-quality, reliable public opinion data.
-This careful selection process ensures that the dataset reflects a thorough and detailed view of public sentiment, accurately capturing behavioral trends and preferences over time.
+## Measurement and Considerations
+
+The goal of measurement here is to translate individual voter opinions into a reliable estimate of electoral college outcomes.
+This analysis aims to systematically capture public sentiment through polling data and convert it into a structured forecast of electoral support for each candidate.
+
+- Data Source and Quality Assurance: The dataset is sourced from @fivethirty, a trusted platform recognized for its stringent standards in polling data quality.
+Only polls meeting high-quality criteria are included to ensure broad representation of likely U.S.
+voters.
+Each poll provides essential details, including the pollster’s identity, survey dates, sample size, and methodological transparency.
+These methods include data collection medium (e.g., phone, online), use of voter files, demographic weighting, and adjustments to create a representative sample.
+While these standards help capture respondents’ voting intentions accurately, it’s important to note that these criteria rely on historical benchmarks, potentially overlooking recent methodological shifts or emerging biases.
+- Temporal Limitations and Data Recency: Polling data captures discrete snapshots of voter sentiment rather than continuous updates.
+Consequently, the analysis reflects voter intentions only at specific moments, which may not capture rapid opinion shifts, particularly as Election Day approaches.
+To mitigate this limitation, recency adjustments are applied to account for the time elapsed since each poll was conducted, helping to ensure that the data remains reflective of current voter sentiment.
+- Participation and Response Bias: Despite the rigorous methodology, certain biases in survey participation are difficult to avoid.
+Self-selection bias (where individuals choose whether to participate) and social desirability bias (where respondents may adjust their responses to be more socially acceptable) can affect data accuracy.
+These biases may introduce discrepancies between expressed opinions and actual voting behavior, potentially influencing forecast reliability.
+- Regional Sampling Imbalances: The frequency of polling varies significantly by state, with battleground states receiving more frequent attention than states considered “safe.” This uneven distribution can lead to imbalances in regional representation, which might skew state-level and, by extension, national forecasts.
+Such discrepancies highlight the challenge of producing a uniformly accurate forecast across all regions.
 

### 2024-11-02 paper/paper.qmd
Revise the Prose, Caption, Graphs, Pollster methodology overview

@@
 
-This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr],usmap [@usmap], corrplot [@corrplot], arrow [@arrow].
+This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], usmap [@usmap], corrplot [@corrplot], arrow [@arrow].
 
@@
 The outcome variable of interest for this research is the percentage representing the level of public support for Donald Trump.
-The distribution is shown in @fig-pct, where the x-axis represents the support percentage, ranging from approximately 20% to 70%, and the y-axis displays the count of poll surveys reporting each support level.
+The distribution is shown in @fig-pct, where support percentage for Donald Trump ranges from approximately 20% to 70%.
 The red dashed line at the 50% mark acts as a benchmark, indicating the threshold needed for majority support.
@@
 A smaller portion of polls report support above 55%, suggesting that while Trump has a core base, many voters remain either undecided or opposed.
-This visualization highlights both the concentration and variability of support within the surveyed population.
+@fig-pct highlights both the concentration and variability of support for Donald Trump within the surveyed population.
 
@@
 The highest possible score is 10, while the lowest is 0.
-The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that this is the most common score.
-This suggests that among the selected pollsters, there is a predominance of high transparency scores.
+The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that nine the most common transparency score.
+@fig-transparency-score suggests that among the selected pollsters, there is a predominance of high transparency scores.
 
@@
   labs(x = "Transparency Score of Poll", 
-       y = "Count of Distinct Pollsters with Each Transparency Score") + 
+       y = "Count of Distinct Pollsters\nwith Each Transparency Score") + 
   theme_minimal()
@@
 
-As shown in the @fig-end-date, the support percentage for Donald Trump fluctuated over time, with a slight upward trend as the election approached, indicated by the dashed trend line.
-This suggests that public opinion varied throughout the period, and Trump’s support percentage experienced an increase as election day drew closer.
-However, it still remained below 50%.
-This trend highlights the importance of monitoring real-time polling data, as sentiment may shift in these months leading up to a closely contested election.
+As shown in the @fig-end-date, at the beginning, fewer pollsters are conducting surveys, as indicated by the sparse dots on the graph.
+As election day approaches, the number of polls increases, reflected by the denser clustering of dots.
+Additionally, the support percentage for Donald Trump fluctuated over time, with a slight upward trend as election day drew closer, as shown by the red dashed trend line.
+This pattern suggests that public opinion shifted throughout the period, with Trump’s support percentage gradually rising, though it remained below 50%.
+This trend highlights the importance of monitoring real-time polling data, as voter sentiment can shift significantly in the months leading up to a closely contested election.
 
@@
 #| label: fig-end-date
-#| fig-cap: Trend of Support Percentage for Donald Trump Over Days Until Election.
-The red dashed line indicates the average support rate for Donald Trump at that point in time.
-Renew the data to the October 24.2024
+#| fig-cap: Trend of Support Percentage for Donald Trump Over Time Leading Up to the 2024 Election Day.
+The red dashed line represents the smoothed trend of average support for Donald Trump at each point in time, showing fluctuations and a gradual increase in support as the election day approaches.Renew the data to the October 24.2024
 #| echo: false
@@
 ggplot(analysis_data, aes(x = days_until_election, y = percent)) + 
-    geom_line(color = "skyblue", size = 1) + 
+    geom_point(color = "skyblue", size = 1) +  # Smaller dots
     geom_smooth(method = "loess", color = "red", linetype = "dashed", size = 1) + 
-    labs(x = "Days Until Election", y = "Support Percentage") + 
+    labs(
+        x = "Days Remaining Until Election Day", 
+        y = "Support Percentage for Donald Trump (%)"
+    ) + 
     theme_minimal(base_size = 14) + 
@@
 #| label: tbl-summary-model
-#| tbl-cap: Regression Model Summary Table（Display the first 10 rows）
+#| tbl-cap: Regression Model Summary Table (Display the first 10 rows)
 #| warning: false
@@
 #| label: tbl-prediction
-#| tbl-cap: Prediction for Trump and Harris by Electoral College
+#| tbl-cap: Prediction Outcomes for the 2024 U.S.
+Presidential Election by State.
+Showing the predicted percentage of votes for Donald Trump, the number of electoral votes each state holds, and the expected winning candidate (either Kamala Harris or Donald Trump)
 #| warning: false
@@
 The table in the [Appendix -@tbl-missing-states] supplements the predicted electoral outcomes by providing likely results for states where the model could not generate predictions.
-Using historical data to estimate outcomes for these missing states ensures a complete view of electoral projections and accounts for every state in the final electoral vote totals.
-
-The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S.
+Using historical data and winner information to estimate outcomes for these missing states ensures a complete view of electoral projections and accounts for every state in the final electoral vote totals.
+
+@fig-statemap shows the predicted winner for each state in the 2024 U.S.
 Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
-The predicted outcome in the regression model reflects the geographic voting patterns, with Trump winning in traditionally Republican-leaning states like Alabama, Missouri, and Wyoming, while Harris dominates in Democratic strongholds such as California, New York, and Illinois.
-However, key battleground states such as Florida and Arizona are predicted to favor Harris, potentially determining the overall election outcome.
+The color distribution across the country highlights regional preferences, with Harris winning most of the West Coast, Northeast, and parts of the Midwest, while Trump is favored in much of the South and Mountain West regions.
+Swing states, including Pennsylvania, Michigan, and Wisconsin, are currently projected to lean blue, suggesting a shift toward Harris in these critical battleground areas.
+@fig-statemap serves as a snapshot of the anticipated electoral landscape, indicating where each candidate may focus campaign efforts leading up to election day.
 
@@
 #| label: fig-statemap
-#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
+#| fig-cap: Predicted Winner of the 2024 U.S. Presidential Election by State (Based on Polling Data and Historical Trends)
 #| warning: false
@@
                     name = "Predicted Winner", labels = c("Harris", "Trump")) +
-  labs(title = "Predicted Winner of the 2024 U.S. Presidential Election by State") +
   theme(legend.position = "right")
-
-```
-
-The table below (@tbl-numstate) shows the numerical predicted winner of the 2024 US Presidential Election by state.
+```
+
+@tbl-numstate shows the numerical predicted winner of the 2024 US Presidential Election by state.
 Harris is expected to win the 2024 U.S.
@@
 #| label: tbl-numstate
-#| tbl-cap: Numerical Predicted Winner of 2024 US Presidential Election by State
+#| tbl-cap: Numerical Projected Electoral Vote Count for the 2024 U.S. Presidential Election (Based on Polling Data and Historical Trends). 
 #| warning: false
@@
 summary_df <- data.frame(
-  Candidate = c("Trump", "Harris"),
+  Candidate = c("Donald Trump", "Kamala Harris"),
   Total_Electoral_Votes = c(trump_total, harris_total)
@@
 While the model effectively captures overall trends, it cannot account for unforeseen factors, such as shifts in voter turnout, the influence of third-party candidates, or sudden political or social events that could impact voter behavior.
-Additionally, the uneven distribution of survey data across states introduces further uncertainty.Sstates with infrequent polling or underrepresented demographic groups may lead to biased predictions.
+Additionally, the uneven distribution of survey data across states introduces further uncertainty.
+States with infrequent polling or underrepresented demographic groups may lead to biased predictions.
 This variation in polling frequency and sample diversity presents a challenge in achieving a fully representative model, and these uncertainties beyond the data are much more complex.
@@
 
-* Target Population: U.S. citizens eligible to vote in the 2024 presidential election.\
-* Sample Frame:  U.S. households with either home telephones or access to devices such as phones or tablets. \
-* Sample Size: Sample sizes vary across different polls.
+To address research questions, collecting data from every case in the target population is often impractical.
+Defining an appropriate target population, sampling frame, and sample size is essential to ensure accurate representation and feasible data collection , according to @taherdoost2016sampling.
+This is especially crucial in polling, where precise results rely on selecting a sample that reflects the broader population.
+Without clear definitions, polls risk producing biased or inaccurate outcomes.
+
+A target population is a complete set of individuals sharing specific characteristics, but identifying the precise target population can be challenging [@banerjee2010statistics].
+For the poll conducted by SurveyUSA, the target population consists of U.S.
+citizens eligible to vote in the 2024 presidential election, whether nationwide or within specific geographic areas.
+
+The sampling frame is the list of actual cases from which the sample is drawn [@taherdoost2016sampling].
+In SurveyUSA’s methodology, the sampling frame consists of U.S.
+households with access to devices such as home telephones, mobile phones, or tablets.
+When using voter-list (RBS) samples to contact landline phones, SurveyUSA sources these samples from Aristotle.
+For non-probability samples, online adult panelists are randomly chosen from Cint.
+For respondents without a home telephone, SurveyUSA purchases samples from Cint or from Aristotle of Washington, D.C.
+Aristotle specializes in providing data and identity verification services for campaigns and public affairs [@aristotle_website], while Cint is a global provider of digital insights gathering, connecting researchers with a diverse online panel for survey sampling needs [@cint_website].
+The selection of the sampling frame must be representative of the population to ensure that the sample reflects the full diversity and characteristics of the target group.
+A well-defined, representative sampling frame enhances the validity and reliability of research findings by avoiding overrepresentation or underrepresentation of specific groups [@taherdoost2016sampling].
+
+A sample is a subset of individuals or cases selected from the target population or sample frame to make inferences about that population [@fowler2013survey].
+In the context of polls conducted by SurveyUSA, the sample refers to the survey respondents.
+Sample sizes vary across different SurveyUSA polls.
 For the 2024 U.S.
-presidential election cycle, SurveyUSA conducted 49 polls, with sample sizes ranging from 507 to 2,330 for registered voters or likely voters.
-The average sample size for these polls is approximately 1,045 households.\
+presidential election cycle, SurveyUSA conducted 49 polls with sample sizes ranging from 507 to 2,330 registered or likely voters.
+The average sample size for these polls is approximately 1,045 households.
 
@@
 
-SurveyUSA employs a mixed-method approach to recruitment, including online panels, telephone calls, and a text-to-web method.
-Some respondents are recruited through Random Digit Dialing (RDD) using telephone samples purchased from Aristotle.
-RDD allows them to generate phone numbers at random, helping avoid biases that can result from using pre-existing contact lists.
-For those who do not use home telephones, SurveyUSA invite them to complete the survey on an electronic device such as a phone or tablet.
-Respondents from non-probability online panels are selected randomly by Cint Lucid Holdings LLC [@surveyusa_methodology].\
+SurveyUSA employs a mixed-method approach to recruitment, designed to reach a diverse and representative sample by incorporating online panels, telephone calls, and a text-to-web method.
+Some respondents are recruited using Random Digit Dialing (RDD) with telephone samples purchased from Aristotle.
+RDD generates phone numbers randomly, allowing SurveyUSA to reach both listed and unlisted numbers, thereby reducing bias associated with pre-existing contact lists.
+This technique is valuable for recruiting a broad demographic across various age groups, regions, and socioeconomic backgrounds for polls, such as voter preference surveys.
+
+For respondents without home telephones, SurveyUSA sends text-to-web invitations, enabling participants to complete surveys on electronic devices like smartphones or tablets.
+This approach broadens accessibility and inclusivity across diverse demographic groups.
+
+Additionally, respondents from non-probability online panels are randomly selected by Cint, which recruits individuals who have pre-registered for surveys, allowing for the quick generation of a large, diverse respondent pool [@surveyusa_methodology].
+This mixed approach allows SurveyUSA to obtain a more comprehensive and representative sample, ultimately enhancing the reliability and accuracy of survey results.
 
 ## Sampling approach and Trade-offs
+
+Selecting an appropriate sampling technique can help researchers to obtain reliable research results.
+In general, sampling techniques fall into two categories: probability (random) sampling and non-probability (non-random) sampling.
+Probability sampling includes methods such as simple random sampling, stratified random sampling, cluster sampling, systematic sampling, and multi-stage sampling.
+In contrast, non-probability sampling encompasses techniques like quota sampling, snowball sampling, judgment sampling, and convenience sampling.
 
@@
 
-Non-response in survey research is important to address because it introduces potential bias, impacting the accuracy and representativeness of the results.As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
+Non-response in survey research is important to address because it introduces potential bias, impacting the accuracy and representativeness of the results.As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.
+For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
 Meanwhile, people with strong opinions or from specific demographic groups could be overrepresented in the results.
-This imbalance can create biased outcomes, where the poll data disproportionately reflects the views of a more vocal subset rather than an accurate cross-section of the entire population.\
+As a result of non-response, the findings may misinform decision-makers, leading to conclusions that don’t truly represent the diverse views of the entire population.
+Addressing non-response is thus essential for producing balanced, reliable survey results that can genuinely inform policies, programs, and public opinion.\
 
@@
 Stratified random sampling involves dividing the target population into subgroups (strata) based on demographic characteristics, then randomly sampling from each stratum.
-This technique enhances the representativeness of the sample and improves prediction accuracy by reducing demographic and geographic sampling bias [@fivethirty].
+This technique enhances the representativeness of the sample and improves prediction accuracy by includes all important subpopulation [@taherdoost2016sampling] and reducing demographic and geographic sampling bias [@fivethirty].
+
+Quota Sampling complements this by setting specific quotas to ensure each subgroup meets minimum representation levels within the sample, based on key demographic categories.
+While not truly random, quota sampling helps ensure that important demographics are represented even when probability sampling is challenging or costly.
 
@@
 This stratification aligns with best practices in survey sampling, allowing for improved accuracy and generalizability in election forecasting by ensuring that subgroups are proportionately represented [@pewresearch].
+However, in stratified sampling, selecting relevant stratification variables can be challenging, and it is neither feasible nor cost-effective to stratify across numerous variables simultaneously.
+For quota sampling, there is a risk of selection bias, and it does not guarantee the randomness, which may impact the sample’s representativeness.
 

### 2024-11-02 paper/paper.qmd
Add more details in Model section

@@
 
-Below, we briefly describe the multiple linear regression model used to examine Trump’s winning probability. Additional details and model diagnostics are provided in [Appendix -@sec-model-details].
+One alternative model considered is logistic regression, commonly used for binary outcomes to predict the probability of an event occurring versus not occurring.
+While logistic regression is effective for classification tasks, it is not suitable here, as the goal of this paper is to predict a continuous percentage of voters likely to vote for Donald Trump.
+Logistic regression restricts outputs to probabilities between 0 and 1, which does not align with the requirements of this analysis.
+Therefore, a multiple linear regression framework is selected for this paper.
 
 ## Multiple Linear Regression Model Overview
-The model now predicts Trump’s polling percentage (percent) using the following predictors:
+Key assumptions for Multiple linear regression:
+
+- Linearity: The relationship between the independent variables (predictors) and the dependent variable(Percentage of Respondents Supporting Donald Trump) is linear. 
+- Independence: The outcome of one observation(respondents) should not influence another
+- Homoscedasticity: The variance of the residuals (errors) is constant across all levels of the independent variables.
+- Normality of Residuals: The residuals (errors) of the model are normally distributed.
+- No Multicollinearity: Independent variables should not be highly correlated with each other. Multicollinearity will make some predictors appear insignificant when they might actually have an effect.
+
+Additional details and model diagnostics are provided in [Appendix -@sec-model-details].
+
+The model predicts Trump’s polling percentage (percent) using the following predictors:
 
@@
 #| label: tbl-summary-model
-#| tbl-cap: Regression Model Summary Table (Display the first 10 rows)
-#| warning: false
-#| message: false
-
-regression_model<-readRDS(here::here("models/regression_model.rds"))
-summary<-summary(regression_model)
-# Extract the coefficients to form a table
-coefficients_table <- summary$coefficients[, 1:3]
-
-# Display the first 10 rows of the coefficients table using kable, formatted to 2 decimal places
-kable(head(coefficients_table, 10), digits = 2)
+#| tbl-cap: Regression Model Summary Table.
+This table displays the top 10 predictors with the largest absolute coefficients, along with Transparency Score and Days Until Election.
+The standard errors represent the variability in the coefficient estimates, while the t-values indicate the strength and significance of each predictor’s relationship with the outcome variable.
+#| warning: false
+#| message: false
+
+# Load the regression model
+regression_model <- readRDS(here::here("models/regression_model.rds"))
+summary <- summary(regression_model)
+
+# Extract the coefficients and form a table with estimates, standard errors, and t-values
+coefficients_table <- as.data.frame(summary$coefficients[, 1:3])
+
+# Select the top 10 rows with the largest absolute coefficients
+coefficients_table$Predictor <- rownames(coefficients_table)
+coefficients_table <- coefficients_table[order(abs(coefficients_table$Estimate), decreasing = TRUE), ]
+top_10_table <- head(coefficients_table, 10)
+
+# Ensure that transparency_score and days_until_election are included in the table
+required_predictors <- c("transparency_score", "days_until_election")
+additional_predictors <- coefficients_table[coefficients_table$Predictor %in% required_predictors, ]
+
+# Combine the top 10 table with the required predictors, ensuring no duplicates
+final_table <- unique(rbind(top_10_table, additional_predictors))
+
+# Rename specific predictors
+final_table$Predictor <- as.character(final_table$Predictor)
+final_table$Predictor[final_table$Predictor == "transparency_score"] <- "Transparency Score"
+final_table$Predictor[final_table$Predictor == "days_until_election"] <- "Days Until Election"
+
+# Set row names to the updated Predictor names and remove the Predictor column
+row.names(final_table) <- final_table$Predictor
+final_table <- final_table[, -ncol(final_table)]  # Remove Predictor column
+
+# Rename the columns
+colnames(final_table) <- c("Coefficient", "Standard Error", "t-Statistic")
+
+# Display the table
+kable(final_table, digits = 2)
+
 ```
@@
 # Create the table using kable
-kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
-      col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
-      digits = 2)
+kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")],        col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),digits = 2) 
 ```
@@
 ## Weakness
-Despite the model estimating the voter's choice trend, it has limitations.
-For instance, assuming linear relationships between predictors may oversimplify complex voter behaviors and other external social influences.
-The dataset simplifies the potential influence behind the US election.
+Despite the model’s ability to estimate voter choice trends, it has several limitations.
+For instance, assuming linear relationships between predictors restricts its capacity to capture more complex, non-linear relationships, potentially oversimplifying external social influences.
+The dataset itself may also oversimplify the range of factors affecting the U.S.
+election, limiting the model’s ability to account for all relevant influences.
+Additionally, outliers and influential points can disproportionately impact the regression model, potentially distorting results and leading to misleading conclusions.
 
@@
 
-# Display the full summary table using kable
-kable(full_summary_df)
+```
+```{r}
+#| echo: false
+#| tbl-cap: Coefficient Estimates with 95% Confidence Intervals for Predictors. Predictors with positive coefficients are shown in blue, while predictors with negative coefficients are shown in red. 
+#| warning: false
+#| message: false
+
+# Convert the model summary to a tidy format for easier plotting
+tidy_model <- broom::tidy(regression_model, conf.int = TRUE, conf.level = 0.95) %>%
+  filter(term != "(Intercept)")
+
+# Plot the coefficients with confidence intervals, excluding the intercept
+ggplot(tidy_model, aes(x = estimate, y = reorder(term, estimate))) +
+  geom_point(aes(color = estimate > 0), size = 1.2) +
+  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), color = "grey", height = 0.3) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
+  scale_color_manual(
+    values = c("red", "blue"),
+    labels = c("Negative Coefficient", "Positive Coefficient"),
+    name = ""  # This removes the default "estimate > 0" label
+  ) +
+  labs(x = "Coefficient Value", y = "Predictors") +
+  theme_minimal(base_size = 12) +
+  theme(
+    axis.text.y = element_text(size = 3),
+    axis.title.x = element_text(size = 14),
+    axis.title.y = element_text(size = 14),
+    plot.title = element_text(size = 16, face = "bold"),
+    legend.position = "top"
+  ) +
+  guides(color = guide_legend(reverse = TRUE))
 

### 2024-11-03 paper/paper.qmd
Update intro.

@@
 title: "Forecasting the 2024 U.S. Presidential Election"
-subtitle: "Predicting Kamala Harris’s Path to Victory: A Poll-Based Projection Under Electoral Uncertainty"
+subtitle: "Kamala Harris’s Path to Victory: A Poll-Based Prediction Under Electoral Uncertainty"
 author: 
@@
 The 2024 U.S.
-Presidential Election will occur in a context of intensified political polarization, economic challenges, and demographic shifts, positioning it as a significant event in shaping America's future.
-Accurately forecasting this election’s outcome is essential for understanding potential shifts in political leadership and policy direction.
-Polling data has traditionally been a primary tool for measuring voter sentiment; however, recent election cycles have revealed limitations in polling accuracy due to biases, non-response, and variations in poll quality.
-This study proposes a model that addresses these issues to improve the reliability of election forecasts.
-
-This paper develops a predictive model to forecast the electoral outcomes between Kamala Harris and Donald Trump in the 2024 election.
-Using a multiple linear regression framework, we analyze aggregated polling data across U.S.
-states, incorporating factors such as poll quality, transparency, sample size, geographic indicators, and poll timing.
-By integrating these variables, the model aims to produce a detailed forecast that accounts for regional differences and methodological variations, offering a thorough view of projected support for each candidate.
-
-The findings indicate a competitive election landscape, with Harris showing strong prospects in key battleground states, while Trump retains support in traditional Republican strongholds.
-These projections highlight the persistent influence of geographic voting patterns and the importance of polling methodology in electoral forecasting.
-This study offers valuable information for political analysts, campaign strategists, and the public, enhancing the understanding of how polling data can inform electoral outcome predictions.
-
-The remainder of this paper is organized as follows: @sec-data describes the dataset and the preprocessing steps for model preparation.
+Presidential Election, which will come to an end on Nov 4, 2024, draws the worldwide attention.
+Especially after Joe Biden dropped out, this cycle’s election is full of more uncertainties.
+Predicting the electoral result is crucial and meaningful for understanding potential shifts in voter behavior, with significant implications for future leadership and policy directions in the United States.
+Forecasting the election’s outcome becomes essential and meaningful for understanding potential shifts in the voters’ behavior.
+To make the prediction feasible, polling data becomes a primary tool for measuring voters’ sentiment and their expectations.
+This paper focuses on forecasting the electoral outcomes between Kamala Harris and Donald Trump in the 2024 cycle.
+Using the multiple linear regression model build on the polling data from @fivethirty, we construct an analysis by incorporating factors such as poll quality, transparency, sample size, state preference, and poll timing.
+By integrating these variables, the model produces a detailed forecast that accounts for regional differences and methodological variations, offering a thorough view of projected support for each candidate.
+The result indicates a competitive election landscape, with Harris showing strong prospects in key swing states, while Trump retains support in traditional Republican states.
+These findings demonstrate how the persistent influence of geographic voting patterns and the importance of polling methodology would influence the electoral votes.
+This paper offers valuable analysis for political analysts, campaign strategists, and the public, enhancing the understanding of how polling data can inform electoral outcome predictions.
+However, recent election cycles have also revealed limitations in polling accuracy due to biases, non-response errors, and variations in poll quality.
+This study proposes a feasible model that addresses these issues to improve the reliability of election forecasts, and the uncertainty beyond the data has also been acknowledged in this paper.
+The paper is organized as follows: @sec-data describes the dataset and the processing steps for model preparation.
 @sec-model explains the modeling approach, including predictor selection and the regression model structure.
 @sec-results presents the primary findings, detailing state-by-state predictions and overall electoral projections.
-@sec-discussion discusses the implications, limitations, and potential directions for future research.
-The Appendix provides supplementary information on methodology, diagnostics, technical details of the model setup, acknowledgments, and references.
-
-## Estimand
+@sec-discussion discusses the key findings, regional voting patterns, polling uncertainty and weakness.
+The @sec-Appendix1 provides the evaluation of the survey USA and @sec-Appendix2 discusses about the idealized methodology on survey.
+Besides, model diagnostics and summary are also attached in @sec-model.
+
 In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S.
@@
 Defining the estimand clearly ensures consistency in the analysis by guiding model design and interpretation, preventing unintended shifts in focus due to minor methodological changes.
-
-###
 
@@
 
-# Appendix {-}
-
-# Pollster Methodology Overview and Evaluation
+# Pollster Methodology Overview and Evaluation {#sec-Appendix1}
 
@@
 
-# Idealized Methodology and Survey
+# Idealized Methodology and Survey {#sec-Appendix2}
 
@@
 
-# Model details {#sec-model-details}
+# Model details {#sec-model}
 

### 2024-11-03 paper/paper.qmd
Typo.
Wrong election date, updated.

@@
 The 2024 U.S.
-Presidential Election, which will come to an end on Nov 4, 2024, draws the worldwide attention.
+Presidential Election, which will come to an end on Nov 5, 2024, draws the worldwide attention.
 Especially after Joe Biden dropped out, this cycle’s election is full of more uncertainties.
@@
 The paper is organized as follows: @sec-data describes the dataset and the processing steps for model preparation.
-@sec-model explains the modeling approach, including predictor selection and the regression model structure.
+@sec-modelsetup explains the modeling approach, including predictor selection and the regression model structure.
 @sec-results presents the primary findings, detailing state-by-state predictions and overall electoral projections.
@@
 
-# Model {#sec-model}
+# Model {#sec-modelsetup}
 

### 2024-11-03 paper/paper.qmd
Update intro and figure in model summary.

@@
 To make the prediction feasible, polling data becomes a primary tool for measuring voters’ sentiment and their expectations.
+
 This paper focuses on forecasting the electoral outcomes between Kamala Harris and Donald Trump in the 2024 cycle.
@@
 The result indicates a competitive election landscape, with Harris showing strong prospects in key swing states, while Trump retains support in traditional Republican states.
-These findings demonstrate how the persistent influence of geographic voting patterns and the importance of polling methodology would influence the electoral votes.
+These findings demonstrate how the persistent influence of geographic voting patterns and the polling characteristics would influence the electoral votes.
+
 This paper offers valuable analysis for political analysts, campaign strategists, and the public, enhancing the understanding of how polling data can inform electoral outcome predictions.
@@
 
-In this analysis, the estimand is the true effect of polling factors on projected support for Trump and Harris in the 2024 U.S.
-election.
-Specifically, it reflects how variables such as poll quality, transparency, sample size, and timing influence the predicted vote percentages for Kamala Harris and Donald Trump across states.
-Defining the estimand clearly ensures consistency in the analysis by guiding model design and interpretation, preventing unintended shifts in focus due to minor methodological changes.
+The estimand in this paper represents the actual influence of certain polling factors on the forecasted support for Kamala Harris and Donald Trump in the 2024 election.
+Specifically, it examines how factors like poll quality, transparency, sample size, and timing impact voting percentages for each candidate across different states.
+Defining this estimand here provides a consistent foundation for the analysis, ensuring that the model accurately reflects the relationship between these polling characteristics and candidate support while minimizing potential distortions from methodological differences.
 
@@
 ```
-```{r}
+```{r, fig.width=10, fig.height=8}
 #| echo: false
@@
   labs(x = "Coefficient Value", y = "Predictors") +
-  theme_minimal(base_size = 12) +
+  theme_minimal(base_size = 14) +
   theme(
-    axis.text.y = element_text(size = 3),
+    axis.text.y = element_text(size = 10),
     axis.title.x = element_text(size = 14),

### 2024-11-03 paper/paper.qmd
Revise references, llm usages

@@
 By integrating these variables, the model produces a detailed forecast that accounts for regional differences and methodological variations, offering a thorough view of projected support for each candidate.
-The result indicates a competitive election landscape, with Harris showing strong prospects in key swing states, while Trump retains support in traditional Republican states.
-These findings demonstrate how the persistent influence of geographic voting patterns and the polling characteristics would influence the electoral votes.
+The results indicate a decisive victory for Harris, who is projected to secure approximately 387 electoral votes, showcasing strong performance in key swing states and surpassing the required 270 votes by a wide margin.
+In contrast, Trump is predicted to receive 151 electoral votes, retaining support primarily within traditional Republican strongholds.
+These findings underscore Harris's substantial lead and emphasize the ongoing impact of geographic voting patterns and polling characteristics on electoral outcomes.
 
@@
 @sec-discussion discusses the key findings, regional voting patterns, polling uncertainty and weakness.
-The @sec-Appendix1 provides the evaluation of the survey USA and @sec-Appendix2 discusses about the idealized methodology on survey.
+The @sec-Appendix1 provides n evaluation of the SurveyUSA polls and @sec-Appendix2 discusses about the idealized methodology on survey.
 Besides, model diagnostics and summary are also attached in @sec-model.
@@
 Specifically, it examines how factors like poll quality, transparency, sample size, and timing impact voting percentages for each candidate across different states.
+However, the true estimand remains unknown, as we can only approximate it using available polling data and model assumptions.
 Defining this estimand here provides a consistent foundation for the analysis, ensuring that the model accurately reflects the relationship between these polling characteristics and candidate support while minimizing potential distortions from methodological differences.
@@
 The distribution is shown in @fig-pct, where support percentage for Donald Trump ranges from approximately 20% to 70%.
-The red dashed line at the 50% mark acts as a benchmark, indicating the threshold needed for majority support.
+The red dashed line at the 50% mark acts as a benchmark, indicating the threshold needed for majority support for winning.
 
@@
 
-The numeric grade reflects the quality of the pollster, with FiveThirtyEight defining a scale from 0 to 3.
+The numeric grade reflects the quality of the pollster, with @fivethirty defining a scale from 0 to 3.
 A grade of 0 indicates a low-quality poll, while a grade of 3 signifies a high-quality pollster.
@@
 The highest possible score is 10, while the lowest is 0.
-The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that nine the most common transparency score.
+The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that nine is the most common transparency score.
 @fig-transparency-score suggests that among the selected pollsters, there is a predominance of high transparency scores.
@@
 #| fig-cap: Trend of Support Percentage for Donald Trump Over Time Leading Up to the 2024 Election Day.
-The red dashed line represents the smoothed trend of average support for Donald Trump at each point in time, showing fluctuations and a gradual increase in support as the election day approaches.Renew the data to the October 24.2024
+The red dashed line represents the smoothed trend of average support for Donald Trump at each point in time, showing fluctuations and a gradual increase in support as the election day approaches.
+Renew the data to the October 24, 2024.
 #| echo: false
@@
 
-Additional details and model diagnostics are provided in [Appendix -@sec-model-details].
+Additional details and model diagnostics are provided in @sec-model.
 
@@
 This approach allows us to isolate the individual impact of each variable, providing a more detailed understanding of how each factor contributes to Trump’s polling outcomes.
-The full coefficient output is shown in the [Appendix -@sec-model-details]
+The full coefficient output is shown in the @sec-model
 
@@
 For instance:
-- Alabama: Trump is predicted to win 53% of the vote, securing all 9 electoral votes.
+
+- South Dakota: Trump is predicted to win 57.17% of the vote, securing all 3 electoral votes for Trump.
 - California: Trump is predicted to receive 34.39% of the vote, resulting in a victory for Harris, who takes California's 55 electoral votes.
-- Florida: The model predicts a close race, with Trump at 48.89% of the vote, resulting in a Harris win in this battleground state.
+- Florida: The model predicts a close race, with Trump at 50.04% of the vote, resulting in a Trump win in this battleground state.
 
@@
 ## Predicted Electoral Outcomes by State
-The table in the [Appendix -@tbl-missing-states] supplements the predicted electoral outcomes by providing likely results for states where the model could not generate predictions.
+The table in the @tbl-missing-states supplements the predicted electoral outcomes by providing likely results for states where the model could not generate predictions.
 Using historical data and winner information to estimate outcomes for these missing states ensures a complete view of electoral projections and accounts for every state in the final electoral vote totals.
@@
 Harris is expected to win the 2024 U.S.
-Presidential Election, securing 387 electoral votes, compared to Trump’s 151 electoral votes.
+Presidential Election, securing 387 electoral votes in total, compared to Trump’s 151 electoral votes.
 The election outcome hinges on several battleground states, where the vote margins are predicted to be narrow.
@@
 The analysis shows that state-specific factors, such as historical voting patterns and days until election day, significantly influence each candidate’s polling outcomes.
-Traditional Democratic strongholds like California and New York favor Harris, while Republican-leaning states such as Alabama and Wyoming align with Trump.
+Traditional Democratic strongholds like California and New York favor Harris, while Republican-leaning states such as South Dakota and Missouri align with Trump.
 This distribution reflects persistent geographic voting patterns and highlights the impact of regional party loyalty.
@@
 elections.
-As expected, traditional Democratic strongholds such as California, New York, and Illinois favor Harris, while Republican-dominated states like Alabama and Wyoming show support for Trump.
+As expected, traditional Democratic strongholds such as California, New York, and Massachusetts favor Harris, while Republican-dominated states like South Dakota and Missouri show support for Trump.
 These regional preferences align with historical voting behaviors, suggesting that party loyalty and demographic factors continue to shape election results.
 
-The model also highlights the significant role of battleground states, with states such as Florida and Arizona predicted to lean toward Harris.
+For instance, Florida, with its 30 electoral votes, is projected to lean toward Trump, with 50.04% of voters supporting him.
+In contrast, Arizona, with its 11 electoral votes, is expected to lean toward Harris, as 47.64% of voters are predicted to support Trump.
 The influence of these states, where margins are often narrow, emphasizes the importance of campaign efforts and voter mobilization in these regions.
@@
 
-# Pollster Methodology Overview and Evaluation {#sec-Appendix1}
+# Appendix: Pollster Methodology Overview and Evaluation {#sec-Appendix1}
 
@@
 Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
-
 * **Disadvantages:** Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
-Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.\
+Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.
 
@@
 
-Non-response in survey research is important to address because it introduces potential bias, impacting the accuracy and representativeness of the results.As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.
+Addressing non-response in survey research is essential because it introduces potential bias, particularly non-response bias, which can impact the accuracy and representativeness of the results.
+As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.
 For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
@@
 As a result of non-response, the findings may misinform decision-makers, leading to conclusions that don’t truly represent the diverse views of the entire population.
-Addressing non-response is thus essential for producing balanced, reliable survey results that can genuinely inform policies, programs, and public opinion.\
+Addressing non-response is thus essential for producing balanced, reliable survey results that can genuinely inform policies, programs, and public opinion.
 
@@
 * **Negative Aspects:**
-Static options for party affiliation and ideology may overlook the subtleties of respondents' political beliefs. These fixed categories risk oversimplifying complex political identities.\
+Static options for party affiliation and ideology may overlook the subtleties of respondents' political beliefs. These fixed categories risk oversimplifying complex political identities.
 
@@
 
-# Idealized Methodology and Survey {#sec-Appendix2}
+# Appendix: Idealized Methodology and Survey {#sec-Appendix2}
 
@@
 ### Sample Size
-A total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1\% at a 95\% confidence level.
+Sample size is a critical factor in research design, as it influences the accuracy, reliability, and generalizability of study results.
+As mentioned by @cohen2013statistical, in statistical analysis, a larger sample size generally provides a more accurate reflection of the population characteristics, reducing the potential for sampling error.
+
+Thus, for the idealized methodology, a total of **10,000 respondents** will be surveyed, providing a margin of error of approximately ±1\% at a 95\% confidence level.
 This sample size allows for detailed subgroup analysis (e.g., by state or demographic group), yielding statistically robust predictions that represent the target population.
@@
 ### Weighting
-Post-stratification weights will be applied to adjust for any oversampling or undersampling of specific demographic groups.
-For instance, younger voters or underrepresented minorities will be weighted to reflect their true proportions in the voting population.
-This weighting ensures that the final sample aligns closely with the demographic makeup of the target population.
+As discussed by @kalton2003weighting, weighting adjustments are frequently applied in surveys to address non- response and non-coverage, helping weighted sample estimates align with known population values.
+Thus, in this idealized methodology, post-stratification weights will be used to adjust for any oversampling or undersampling of specific demographic groups.
+For example, younger voters or underrepresented minorities will be weighted to reflect their actual proportions in the voting population.
+This adjustment ensures that the final sample closely mirrors the demographic composition of the target population, enhancing the accuracy and representativeness of the results.
 
@@
 Non-response matters because it can distort the results if certain demographics are underrepresented in the final data [@pewresearch].
+Moreover, utilizing multiple methods can reduce costs, speed up response collection, and improve response rates [@dillman2014internet].
 
@@
 
-# Model details {#sec-model}
+# Appendix: Model details {#sec-model}
 

### 2024-11-03 paper/paper.qmd
Delete the long table and finalize the paper.

@@
 
-```{r}
-#| echo: false
-#| tbl-cap: Complete Model Coefficient Summary Table
-#| warning: false
-#| message: false
-
-# Get summary of the regression model
-model_summary <- summary(regression_model)
-
-# Extract and convert the coefficients summary to a data frame
-coefficients_df <- as.data.frame(model_summary$coefficients)
-colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")
-
-# Extract additional statistics
-r_squared <- model_summary$r.squared
-adj_r_squared <- model_summary$adj.r.squared
-f_statistic <- model_summary$fstatistic[1]
-p_value <- pf(f_statistic, model_summary$fstatistic[2], model_summary$fstatistic[3], lower.tail = FALSE)
-residual_se <- model_summary$sigma
-
-# Create a data frame for additional statistics with consistent column names and rounded to 2 decimals
-additional_stats <- data.frame(
-  Estimate = round(c(r_squared, adj_r_squared, f_statistic, p_value, residual_se), 2),
-  `Std. Error` = NA,
-  `t value` = NA,
-  `Pr(>|t|)` = NA,
-  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "F-statistic p-value", "Residual Std. Error")
-)
-
-# Ensure column names are identical between data frames
-colnames(additional_stats) <- colnames(coefficients_df)
-
-# Round coefficients to 2 decimal places in coefficients_df
-coefficients_df <- coefficients_df %>%
-  mutate(across(where(is.numeric), ~ round(., 2)))
-
-# Combine the coefficients and additional statistics
-full_summary_df <- rbind(coefficients_df, additional_stats)
-
-# Display the full summary table using kable, excluding "F-statistic p-value" row
-library(knitr)
-kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])
-
-```
-```{r, fig.width=10, fig.height=8}
+```{r, fig.width=12, fig.height=10}
 #| echo: false
@@
   labs(x = "Coefficient Value", y = "Predictors") +
-  theme_minimal(base_size = 14) +
+  theme_minimal(base_size = 16) +
   theme(
-    axis.text.y = element_text(size = 10),
-    axis.title.x = element_text(size = 14),
-    axis.title.y = element_text(size = 14),
+    axis.text.y = element_text(size = 12),
+    axis.title.x = element_text(size = 16),
+    axis.title.y = element_text(size = 16),
     plot.title = element_text(size = 16, face = "bold"),
-    legend.position = "top"
-  ) +
+    legend.position = "top", size= 20) +
   guides(color = guide_legend(reverse = TRUE))

### 2024-11-04 paper/paper.qmd
Revise the Appendix and Measurement

@@
 This study proposes a feasible model that addresses these issues to improve the reliability of election forecasts, and the uncertainty beyond the data has also been acknowledged in this paper.
+
 The paper is organized as follows: @sec-data describes the dataset and the processing steps for model preparation.
@@
 
-The goal of measurement here is to translate individual voter opinions into a reliable estimate of electoral college outcomes.
-This analysis aims to systematically capture public sentiment through polling data and convert it into a structured forecast of electoral support for each candidate.
-
-- Data Source and Quality Assurance: The dataset is sourced from @fivethirty, a trusted platform recognized for its stringent standards in polling data quality.
-Only polls meeting high-quality criteria are included to ensure broad representation of likely U.S.
+The goal of measurement is to distill individual voter opinions into a reliable estimate of Electoral College outcomes, transforming raw polling data into a clear forecast of each candidate’s support.
+
+To capture public sentiment, surveys ask questions like, “If the election were held today, who would you vote for?” Responses are summarized by pollsters as a percentage of support for each candidate, creating a structured outcome variable that reflects aggregate support.
+
+- Data Source and Quality Assurance: The dataset is sourced from @fivethirty, a trusted platform recognized for its stringent standards in polling data qualityOnly high-quality polls are included to ensure broad representation of likely U.S.
 voters.
-Each poll provides essential details, including the pollster’s identity, survey dates, sample size, and methodological transparency.
-These methods include data collection medium (e.g., phone, online), use of voter files, demographic weighting, and adjustments to create a representative sample.
-While these standards help capture respondents’ voting intentions accurately, it’s important to note that these criteria rely on historical benchmarks, potentially overlooking recent methodological shifts or emerging biases.
+Each poll includes essential details, such as pollster identity, survey dates, sample size, and methodology, all documented in the dataset.
+While these standards effectively capture respondents' voting intentions, they are based on historical benchmarks that may not fully account for recent methodological shifts or emerging biases.
+Additionally, the dataset provides a numeric grade, transparency score, and pollster rating, calculated by @fivethirty using their internal criteria and scoring mechanisms.
 - Temporal Limitations and Data Recency: Polling data captures discrete snapshots of voter sentiment rather than continuous updates.
@@
 #| label: tbl-prediction
-#| tbl-cap: Prediction Outcomes for the 2024 U.S.
-Presidential Election by State.
-Showing the predicted percentage of votes for Donald Trump, the number of electoral votes each state holds, and the expected winning candidate (either Kamala Harris or Donald Trump)
+#| tbl-cap: 2024 U.S.
+Presidential Election Predictions by State.
+Projected vote percentages for Donald Trump, each state’s electoral votes, and the expected winning candidate (Kamala Harris or Donald Trump).
 #| warning: false
@@
 #| label: tbl-numstate
-#| tbl-cap: Numerical Projected Electoral Vote Count for the 2024 U.S. Presidential Election (Based on Polling Data and Historical Trends). 
+#| tbl-cap: Projected Electoral Vote Count for the 2024 U.S. Presidential Election. With 538 total electoral votes, a candidate needs 270 to win.
 #| warning: false
@@
 Probability sampling includes methods such as simple random sampling, stratified random sampling, cluster sampling, systematic sampling, and multi-stage sampling.
-In contrast, non-probability sampling encompasses techniques like quota sampling, snowball sampling, judgment sampling, and convenience sampling.
-
-SurveyUSA uses a blend of probability and non-probability sampling methods.
-Some respondents are drawn from non-probability online panels, while others are recruited using probability-based telephone sampling.
+In contrast, non-probability sampling encompasses techniques like quota sampling, snowball sampling, judgment sampling, and convenience sampling [@fowler2013survey].
+
+SurveyUSA utilizes both probability and non-probability sampling methods, sourcing respondents from non-probability online panels and probability-based telephone sampling [@surveyusa_methodology].
+SurveyUSA employs simple random sampling, a method in which each individual in the population has an equal chance of selection, by randomly selecting phone numbers [@noor2022simple].
+In contrast, the online panel represents convenience sampling, a non-probability method in which self-selected participants voluntarily join the panel and are readily available for surveys [@fowler2013survey].
 Responses are weighted based on the latest U.S.
@@
 
-* **Advantages:** The diverse sampling approach not only ensures a broad range of opinions is captured but also complements probability-based sampling, which accurately reflects the overall population.
-Furthermore, reweighting the data according to U.S.
+* **Advantages:** The mixed approach offers several benefits.
+Simple random sampling ensures representativeness by giving all individuals an equal selection chance, a key feature that ensures representativeness and minimizes selection bias.
+Randomization helping to offset confounding effects from both known and unknown factors [@noor2022simple].
+Convenience sampling through online panels further enhances data collection by making it faster and more cost-effective [@sedgwick2013convenience].
+Additionally, reweighting the data according to U.S.
 Census demographics strengthens the credibility of the results by ensuring demographic accuracy.
-Additionally, rotating questions and answer choices helps mitigate bias, further improving the reliability of the data.
-Finally, the use of online surveys offers a cost-effective solution for efficient data collection.\
-* **Disadvantages:** Phone-based data collection tends to be time-consuming and can be affected by interviewer effects during telephone interviews.
-Additionally, challenges like non-response issues, such as busy signals or refusals to participate, can hinder the effectiveness of the data collection process.
+Rotating questions and answer choices helps mitigate bias, improving data reliability.\
+* **Disadvantages:** Simple random sampling can be problematic for heterogeneous or dispersed populations [@noor2022simple].
+Using phone-based data collection is time-consuming, as it requires contacting many individuals to reach an adequate response rate.
+Non-response issues, including busy signals, refusals, or hang-ups, are common in phone surveys.
+This can create non-response bias, where the views of non-participants differ from those of participants, compromising representativeness.
+The interviewer effect is another concern as respondents may adjust their answers in the presence of a live interviewer [@noor2022simple].
+In addition, convenience sampling also presents challenges, primarily by introducing motivation bias.
+Participants’ willingness to join may depend on their interest in the survey topic, or dissatisfaction they want to voice, potentially skewing the sample’s representativeness [@sedgwick2013convenience].
 
@@
 
-Addressing non-response in survey research is essential because it introduces potential bias, particularly non-response bias, which can impact the accuracy and representativeness of the results.
-As mentioned by @groves2012nonresponse, when certain groups are underrepresented due to non-response, it can skew findings, making them less reflective of the actual population.
+Addressing non-response in survey research is essential, as it occurs when selected participants do not participate or complete the survey, leading to non-response bias [@groves2012nonresponse].
+This bias can compromise accuracy and representativeness by disrupting the information balance needed for the research question, particularly when certain groups are underrepresented, skewing findings away from the actual population [@sedgwick2013convenience].
 For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
@@
 
-Quota Sampling complements this by setting specific quotas to ensure each subgroup meets minimum representation levels within the sample, based on key demographic categories.
+Quota Sampling complements this by setting specific quotas to ensure each subgroup meets minimum representation levels within the sample, based on key demographic categories [@moser1952quota].
 While not truly random, quota sampling helps ensure that important demographics are represented even when probability sampling is challenging or costly.
@@
 #| label: fig-diagnosis-1
-#| tbl-cap: Linear regression assumptions hold.
+#| fig-cap: Linear regression assumptions hold.
 #| warning: false
@@
 #| fig.width: 10
-#| fig.height: 8
+#| fig.height: 7
 
@@
 ```
-
+\newpage
 ## Model Summary
@@
 #| echo: false
-#| tbl-cap: Coefficient Estimates with 95% Confidence Intervals for Predictors. Predictors with positive coefficients are shown in blue, while predictors with negative coefficients are shown in red. 
+#| label: fig-model-summary
+#| fig-cap: Coefficient Estimates with 95% Confidence Intervals for Predictors. Predictors with positive coefficients are shown in blue, while predictors with negative coefficients are shown in red. 
 #| warning: false
@@
 ggplot(tidy_model, aes(x = estimate, y = reorder(term, estimate))) +
-  geom_point(aes(color = estimate > 0), size = 1.2) +
+  geom_point(aes(color = estimate > 0), size = 3) +
   geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), color = "grey", height = 0.3) +
@@
 #| echo: false
-#| fig-cap: Correlation Matrix of Numeric Grade, Sample Size, Transparency Score and `Days Until Election`
+#| fig-cap: Correlation Matrix of Numeric Grade, Sample Size, Transparency Score and Days Until Election
 #| warning: false

### 2024-11-04 paper/paper.qmd
Modify Measurement part

@@
 
-The goal of measurement is to distill individual voter opinions into a reliable estimate of Electoral College outcomes, transforming raw polling data into a clear forecast of each candidate’s support.
-
-To capture public sentiment, surveys ask questions like, “If the election were held today, who would you vote for?” Responses are summarized by pollsters as a percentage of support for each candidate, creating a structured outcome variable that reflects aggregate support.
-
-- Data Source and Quality Assurance: The dataset is sourced from @fivethirty, a trusted platform recognized for its stringent standards in polling data qualityOnly high-quality polls are included to ensure broad representation of likely U.S.
-voters.
-Each poll includes essential details, such as pollster identity, survey dates, sample size, and methodology, all documented in the dataset.
-While these standards effectively capture respondents' voting intentions, they are based on historical benchmarks that may not fully account for recent methodological shifts or emerging biases.
-Additionally, the dataset provides a numeric grade, transparency score, and pollster rating, calculated by @fivethirty using their internal criteria and scoring mechanisms.
-- Temporal Limitations and Data Recency: Polling data captures discrete snapshots of voter sentiment rather than continuous updates.
-Consequently, the analysis reflects voter intentions only at specific moments, which may not capture rapid opinion shifts, particularly as Election Day approaches.
-To mitigate this limitation, recency adjustments are applied to account for the time elapsed since each poll was conducted, helping to ensure that the data remains reflective of current voter sentiment.
-- Participation and Response Bias: Despite the rigorous methodology, certain biases in survey participation are difficult to avoid.
-Self-selection bias (where individuals choose whether to participate) and social desirability bias (where respondents may adjust their responses to be more socially acceptable) can affect data accuracy.
+The goal of measurement is to distill individual voter opinions into a reliable estimate of Electoral College outcomes, transforming raw polling data into a forecast of each candidate’s support.
+
+To capture public sentiment, surveys ask questions like, “If the election were held today, who would you vote for?” Pollsters summarize responses as percentages of support for each candidate, creating a structured outcome variable that reflects aggregate support.
+
+- **Data Source and Quality Assurance**: The dataset is sourced from @fivethirty, a trusted platform recognized for its high standards in polling data quality.
+Only polls that meet specific criteria are included to ensure broad representation of likely U.S.
+Each poll documents essential details, including the pollster's identity, survey dates, sample size, and methodology.
+While these standards effectively capture respondents' voting intentions, they are based on historical benchmarks that may not fully adjust for recent changes in polling methods.
+The dataset also provides a numeric grade, transparency score, and pollster rating, calculated by @fivethirty using their internal criteria.
+- **Temporal Limitations and Data Recency**: Polling data captures discrete snapshots of voter sentiment rather than continuous updates.
+Consequently, the analysis reflects intentions at particular times, which may not account for rapid shifts in opinion closer to Election Day.
+To address this, recency adjustments are applied to account for the time elapsed since each poll was conducted, helping to ensure the data remains reflective of current voter sentiment.
+- **Participation and Response Bias**: Despite the rigorous methodology, certain biases in survey participation are difficult to avoid.
+Self-selection bias (where individuals choose whether to participate) and social desirability bias (where respondents may adjust their responses to appear socially acceptable) can affect data accuracy.
 These biases may introduce discrepancies between expressed opinions and actual voting behavior, potentially influencing forecast reliability.
-- Regional Sampling Imbalances: The frequency of polling varies significantly by state, with battleground states receiving more frequent attention than states considered “safe.” This uneven distribution can lead to imbalances in regional representation, which might skew state-level and, by extension, national forecasts.
+- **Regional Sampling Imbalances**: The frequency of polling varies significantly by state, with battleground states receiving more frequent attention than states considered “safe.” This uneven distribution can lead to imbalances in regional representation, which may skew state-level and national forecasts.
 Such discrepancies highlight the challenge of producing a uniformly accurate forecast across all regions.

### 2024-11-04 paper/paper.qmd
Modify Appendix part

@@
 presidential election cycle, SurveyUSA conducted 49 polls with sample sizes ranging from 507 to 2,330 registered or likely voters.
-The average sample size for these polls is approximately 1,045 households.
+The average sample size for these polls is approximately 1,045 households.Selecting a representative sample size helps ensure the survey results can be generalized to the target population while maintaining statistical precision [@fowler2013survey].
 

### 2024-11-04 paper/paper.qmd
Modify Prose over the paper

--- 2024-11-04 paper/paper.qmd
@@
 The 2024 U.S.
-Presidential Election, which will come to an end on Nov 5, 2024, draws the worldwide attention.
+Presidential Election, which will come to an end on Nov 5, 2024, draws worldwide attention.
 Especially after Joe Biden dropped out, this cycle’s election is full of more uncertainties.
@@
 @sec-discussion discusses the key findings, regional voting patterns, polling uncertainty and weakness.
-The @sec-Appendix1 provides n evaluation of the SurveyUSA polls and @sec-Appendix2 discusses about the idealized methodology on survey.
+The @sec-Appendix1 provides n evaluation of the SurveyUSA polls and @sec-Appendix2 discusses about the idealized methodology of the survey.
 Besides, model diagnostics and summary are also attached in @sec-model.
@@
 
-This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], usmap [@usmap], corrplot [@corrplot], arrow [@arrow].
+This study uses R packages [@citeR] to clean and analyze the dataset, including libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], usmap [@usmap], corrplot [@corrplot], arrow [@arrow].
 
@@
 - **Data Source and Quality Assurance**: The dataset is sourced from @fivethirty, a trusted platform recognized for its high standards in polling data quality.
-Only polls that meet specific criteria are included to ensure broad representation of likely U.S.
+Only polls that meet specific criteria are included to ensure a broad representation of likely U.S.
 Each poll documents essential details, including the pollster's identity, survey dates, sample size, and methodology.
@@
 The outcome variable of interest for this research is the percentage representing the level of public support for Donald Trump.
-The distribution is shown in @fig-pct, where support percentage for Donald Trump ranges from approximately 20% to 70%.
+The distribution is shown in @fig-pct, where the support percentage for Donald Trump ranges from approximately 20% to 70%.
 The red dashed line at the 50% mark acts as a benchmark, indicating the threshold needed for majority support for winning.
@@
 The highest possible score is 10, while the lowest is 0.
-The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that nine is the most common transparency score.
+The distribution of Transparency Scores for the filtered pollsters shows a peak around 9 as presented in @fig-transparency-score, indicating that 9 is the most common transparency score.
 @fig-transparency-score suggests that among the selected pollsters, there is a predominance of high transparency scores.
@@
 
-The days until election represents the remaining time leading up to the final election day.
+The days until tge election represent the remaining time leading up to the final election day.
 This variable is calculated by finding the difference between the end date of each poll survey and the final election date, which is November 5, 2024.
@@
 - Days Until Election ($\beta_5$): The counting down days is a time-related variable.
-A positive and significant coefficient would suggest that Trump’s polling percentage has decreased as the election date approaches, while a negative coefficient would suggest an increase in his polling percent over time.
+A positive and significant coefficient would suggest that Trump’s polling percentage has decreased as the election date approaches, while a negative coefficient would suggest an increase in his polling percentage over time.
 
@@
 Such an approach could improve the accuracy of predictions, especially in regions with historically unpredictable outcomes.
-These adjustments could improve model's reliability, particularly in closely contested states where the margin of error can significantly impact the final prediction.
+These adjustments could improve the model's reliability, particularly in closely contested states where the margin of error can significantly impact the final prediction.
 
@@
 To address research questions, collecting data from every case in the target population is often impractical.
-Defining an appropriate target population, sampling frame, and sample size is essential to ensure accurate representation and feasible data collection , according to @taherdoost2016sampling.
+Defining an appropriate target population, sampling frame, and sample size is essential to ensure accurate representation and feasible data collection, according to @taherdoost2016sampling.
 This is especially crucial in polling, where precise results rely on selecting a sample that reflects the broader population.
@@
 The average sample size for these polls is approximately 1,045 households.
+Selecting a representative sample size helps ensure the survey results can be generalized to the target population while maintaining statistical precision [@fowler2013survey].
 
@@
 SurveyUSA employs a mixed-method approach to recruitment, designed to reach a diverse and representative sample by incorporating online panels, telephone calls, and a text-to-web method.
-Some respondents are recruited using Random Digit Dialing (RDD) with telephone samples purchased from Aristotle.
+Some respondents were recruited using Random Digit Dialing (RDD) with telephone samples purchased from Aristotle.
 RDD generates phone numbers randomly, allowing SurveyUSA to reach both listed and unlisted numbers, thereby reducing bias associated with pre-existing contact lists.
@@
 Simple random sampling ensures representativeness by giving all individuals an equal selection chance, a key feature that ensures representativeness and minimizes selection bias.
-Randomization helping to offset confounding effects from both known and unknown factors [@noor2022simple].
+Randomization helps to offset confounding effects from both known and unknown factors [@noor2022simple].
 Convenience sampling through online panels further enhances data collection by making it faster and more cost-effective [@sedgwick2013convenience].
@@
 This bias can compromise accuracy and representativeness by disrupting the information balance needed for the research question, particularly when certain groups are underrepresented, skewing findings away from the actual population [@sedgwick2013convenience].
-For example, individuals who with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
+For example, individuals with demanding schedules, lower income or limited access to technology might be less likely to respond to a poll.
 Meanwhile, people with strong opinions or from specific demographic groups could be overrepresented in the results.
@@
 
-SurveyUSA’s methodology reflects a balanced approach, leveraging various sampling approach and method to reach a representative sample.
+SurveyUSA’s methodology reflects a balanced approach, leveraging various sampling approaches and methods to reach a representative sample.
 While its blend of probability and non-probability methods has strengths, such as cost-effectiveness and broad reach, it faces challenges related to telephone interview logistics, potential interviewer bias, and the limitations of fixed questionnaire options.
@@
 Our sampling strategy combines **stratified** random sampling with **quota sampling** to ensure broad representation across key demographics.
-Stratified random sampling involves dividing the target population into subgroups (strata) based on demographic characteristics, then randomly sampling from each stratum.
-This technique enhances the representativeness of the sample and improves prediction accuracy by includes all important subpopulation [@taherdoost2016sampling] and reducing demographic and geographic sampling bias [@fivethirty].
+Stratified random sampling involves dividing the target population into subgroups (strata) based on demographic characteristics, and then randomly sampling from each stratum.
+This technique enhances the representativeness of the sample and improves prediction accuracy by including all important subpopulations [@taherdoost2016sampling] and reducing demographic and geographic sampling bias [@fivethirty].
 
@@
 However, in stratified sampling, selecting relevant stratification variables can be challenging, and it is neither feasible nor cost-effective to stratify across numerous variables simultaneously.
-For quota sampling, there is a risk of selection bias, and it does not guarantee the randomness, which may impact the sample’s representativeness.
+For quota sampling, there is a risk of selection bias, and it does not guarantee randomness, which may impact the sample’s representativeness.
 
@@
 ### Weighting
-As discussed by @kalton2003weighting, weighting adjustments are frequently applied in surveys to address non- response and non-coverage, helping weighted sample estimates align with known population values.
+As discussed by @kalton2003weighting, weighting adjustments are frequently applied in surveys to address non-response and non-coverage, helping weighted sample estimates align with known population values.
 Thus, in this idealized methodology, post-stratification weights will be used to adjust for any oversampling or undersampling of specific demographic groups.
@@
 "Thank you for completing this survey. Your response has been recorded.
-If you have any questions about this survey or would like to be informed about the results, please contact at [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca)."
+If you have any questions about this survey or would like to be informed about the results, please contact [shaw.wei@mail.utoronto.ca](mailto:shaw.wei@mail.utoronto.ca)."
 
